### 2021-03-19 Evening-Huddle-Stats.Rmd
Create RMarkdown file and render file to visualize vaccination stats.

---
title: "MSHS COVID-19 Vaccinations"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: TRUE
---

##### Summary as of `r paste(format(Sys.Date(), "%m/%d/%y"), "3:40PM")`

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Install and load packages}
# Code for updating data analysis for afternoon huddle

#Install and load necessary packages --------------------
#install.packages("readraw_dfl")
#install.packages("writeraw_dfl")
#install.packages("ggplot2")
#install.packages("lubridate")
#install.packages("dplyr")
#install.packages("reshape2")
#install.packages("svDialogs")
#install.packages("stringr")
#install.packages("formattable")
#install.packages("ggpubr")
#install.packages("zipcodeR")
#install.packages("tidyr")
#install.packages("janitor")
#install.packages("knitr")
#install.packages("rmarkdown")
#install.packages("kableExtra")

#Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(janitor)
library(knitr)
library(rmarkdown)
library(kableExtra)
```

```{r Import reference data, set variables, and import raw data, include = FALSE}

# Set working directory and select raw data ----------------------------
rm(list = ls())

# Determine path for working directory
if ("Presidents" %in% list.files("J://")) {
  user_directory <- paste0("J:/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
} else {
  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
}

# Set path for file selection
user_path <- paste0(user_directory, "\\*.*")

# Determine whether or not to update an existing repo
update_repo <- TRUE

# Determine whether or not to update an existing repo
initial_run <- FALSE
update_repo <- TRUE

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-03-12.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-03-12.xlsx"),
                           sheet = "Pod Mappings Simple")

# Store today's date
today <- Sys.Date()

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network LI",
               "MSSN")

# Pod type order
pod_type <- c("Employee", "Patient", "All")

# Vaccine manufacturers
mfg <- c("Pfizer", "Moderna", "J&J")

# NY zip codes
ny_zips <- search_state("NY")

# First vaccine date
vacc_start_date <- as.Date("12/15/20", format = "%m/%d/%y")
vacc_start_first_sun <- vacc_start_date - (wday(vacc_start_date) - 1)

# Determine current week of vaccine effort
this_week <- as.numeric(floor((today - vacc_start_first_sun) / 7) + 1)

# Create dataframe with dates and weeks since vaccines started
all_dates <- data.frame("Date" = seq.Date(as.Date("12/15/20",
                                                  format = "%m/%d/%y"),
                                          today + 7,
                                          by = 1))

all_dates <- all_dates %>%
  mutate(VaccWeek = as.numeric(
    floor((Date - vacc_start_first_sun) / 7) + 1))

vacc_week_dates <- all_dates %>%
  group_by(VaccWeek) %>%
  summarize(Dates = 
              paste0(format(min(Date), "%m/%d/%y"),
                     "-",
                     format(max(Date), "%m/%d/%y")))

# Create variable with doses
doses <- c("Dose1", "Dose2", "AllDoses")

# Specify Sinai colors for table
sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2") #,
                  # "#4C4D4C", "#8988dd", "#B2B3B2", "#F887CE")

# Import raw data from Epic
if (update_repo) {
  sched_repo <- readRDS(
    choose.files(default = paste0(user_directory,
                                  "/R_Sched_AM_Repo/*.*"),
                 caption = "Select this morning's schedule repository"))

  raw_df <- read.csv(choose.files(
    default =
      paste0(user_directory, "/Epic 340PM Sched All Status/*.*"),
    caption = "Select this afternoon's Epic schedule"),
    stringsAsFactors = FALSE,
    check.names = FALSE)

  new_sched <- raw_df

  # Remove test patient
  new_sched <- new_sched[new_sched$Patient != "Patient, Test", ]

  # Update data classes from .csv schedule import to match repository structure
  new_sched <- new_sched %>%
    mutate(DOB = as.Date(DOB, format = "%m/%d/%Y"),
           `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
           Date = as.Date(Date, format = "%m/%d/%Y"),
           `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
                                    tz = "", format = "%Y-%m-%d %H:%M %p"),
           `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)))

  # Determine dates in new report
  current_dates <- sort(unique(new_sched$Date))

  # Update schedule repository by removing duplicate dates and adding data
  # from new report
  sched_repo <- sched_repo %>%
    filter(!(Date >= current_dates[1]))
  sched_repo <- rbind(sched_repo, new_sched)

  # Save schedule
  saveRDS(sched_repo, paste0(user_directory, "/R_Sched_PM_Huddle_Repo/",
                             "Epic Sched 340PM ",
                             format(min(sched_repo$Date), "%m%d%y"), " to ",
                             format(max(sched_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

} else {

  sched_repo <- readRDS(
    choose.files(default = paste0(user_directory,
                                  "/R_Sched_AM_Repo/*.*"),
                 caption = "Select this morning's schedule repository"))

}

# Import MSSN data from Tableau
mssn_admin <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select latest MSSN Tableau Administration Data"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

mssn_admin <- mssn_admin[1:nrow(mssn_admin) - 1, ]

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
```

```{r Format Epic schedule data}
# Format and analyze Epic schedule to date for dashboards ---------------------
epic_sched_to_date <- sched_repo

epic_sched_to_date <- epic_sched_to_date %>%
  mutate(
    # Determine whether appointment is for dose 1 or dose 2
    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose1",
                  ifelse(str_detect(Type, "DOSE 2"), "Dose2", NA)),
    # Determine appointment date, year, month, etc.
    ApptDate = date(Date),
    ApptYear = year(Date),
    ApptMonth = month(Date),
    ApptDay = day(Date),
    ApptWeek = week(Date),
    # Clean up department if it is duplicated in that column
    Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
    # Group arrived, completed, and checked out appts as arrived
    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                    "Arr", `Appt Status`),
    # Update appointment status: classify any appts from prior days that are
    # still in scheduled as No Shows
    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", Status),
    # Determine manufacturer based on immunization field
    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
      ifelse(Status2 != "Arr", NA,
             # Assume any visits without immunization record are Pfizer
             ifelse(is.na(Immunizations), "Pfizer",
                    # Any immunizations with Moderna in text classified as
                    # Moderna, otherwise Pfizer
                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                           # Any immunizations with Johnson and Johnson are
                           # classified as J&J
                           ifelse(str_detect(Immunizations,
                                             "Johnson and Johnson"),
                                  "J&J", "Pfizer")))),
    # Determine week number of year
    WeekNum = format(ApptDate, "%U"),
    # Determine appointment day of week
    DOW = weekdays(ApptDate),
    # Determine if patient's zip code is in NYS
    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
    # Determine week number of vaccine efforts
    VaccWeek = as.numeric(floor((ApptDate - vacc_start_first_sun) / 7) + 1))

# Crosswalk sites
epic_sched_to_date <- left_join(epic_sched_to_date, site_mappings,
                                by = c("Department" = "Department"))

# Roll up any Moderna administered at MSB for YWCA to MSH
epic_sched_to_date <- epic_sched_to_date %>%
  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))

# Crosswalk pod type (employee vs patient)
epic_sched_to_date <- left_join(epic_sched_to_date,
                                pod_mappings[, c("Provider", "Pod Type")],
                                by = c("Provider/Resource" = "Provider"))

# Assume any pods without a mapping are patient pods
epic_sched_to_date[is.na(epic_sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  ungroup()

```

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count")

mssn_admin_to_date <- mssn_admin_to_date[, colnames(epic_sched_summary)]
```

```{r Combine data across all sites}

# Bind MSSN data with Epic sites data
daily_sched_summary <- rbind(epic_sched_summary, mssn_admin_to_date)

daily_sched_summary <- daily_sched_summary %>%
  left_join(vacc_week_dates, by = c("VaccWeek" = "VaccWeek"))
```

```{r Create and combine tables with vaccine administration and schedule data}
# Summarize total doses to date through today -------------
admin_to_date <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Summarize administered doses for prior weeks -----------------
prior_weeks_admin <- daily_sched_summary %>%
  filter(VaccWeek < this_week) %>%
  group_by(Site, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize total doses administered and scheduled this week through today -----
this_week_admin_to_date <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate <= today) %>%
  group_by(Site, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize data for this week to date -------------------
this_week_daily_admin <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate < today) %>%
  group_by(Site, Dose, VaccWeek, ApptDate) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, ApptDate),
              names_prefix = "Wk ",
              names_sep = c(": "),
              values_from = AdminDoses,
              names_sort = TRUE)

# Summarize today's arrived and scheduled doses -------------
todays_sched <- daily_sched_summary %>%
  filter(ApptDate == today) %>%
  group_by(Site, Dose, ApptDate, Status2) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  pivot_wider(names_from = Status2,
              values_from = AdminDoses) %>%
  mutate(Total = sum(Arr, Sch, na.rm = TRUE),
         VaccWeek = NULL) %>%
  pivot_longer(cols = c(Arr, Sch, Total),
               names_to = "ApptStatus",
               values_to = "Count") %>%
  pivot_wider(names_from = c(ApptDate, ApptStatus),
              names_prefix = "Today's Sched: ",
              values_from = c(Count))

# Summarize scheduled data for the next 7 days ---------------
next_7days_sched <- daily_sched_summary %>%
  filter(ApptDate %in% seq(from = today + 1, to = today + 7, by = 1)) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(SchedVisits = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = ApptDate,
              values_from = SchedVisits,
              names_sort = TRUE)

# Create a template of all sites, vaccine dates, and doses ---------
site_rep <- data.frame("Site" = sort(rep(all_sites,
                                         length(doses))))

dose_rep <- data.frame("Dose" = rep(doses,
                                    length(all_sites)))

site_dose_rep <- cbind(site_rep, dose_rep)

site_dose_rep <- site_dose_rep %>%
  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
  arrange(Site, Dose)

# Combine all tables
site_data_summary <- 
  left_join(
    left_join(
      left_join(
        left_join(
          left_join(
            left_join(
              #First, join site and dose template with administered doses to date
              site_dose_rep,
              admin_to_date,
              by = c("Site" = "Site", "Dose" = "Dose")),
            # Second, join with administered doses from prior weeks
            prior_weeks_admin,
            by = c("Site" = "Site", "Dose" = "Dose")),
          # Third, join this week's doses administered/scheduled through today
          this_week_admin_to_date,
          by = c("Site" = "Site", "Dose" = "Dose")),
        # Fourth, join this week's daily data through today
        this_week_daily_admin,
        by = c("Site" = "Site", "Dose" = "Dose")),
      # Fifth, join today's arrived and scheduled appts
      todays_sched,
      by = c("Site" = "Site", "Dose" = "Dose")),
    # Last, join scheduled doses for the next 7 days
    next_7days_sched,
    by = c("Site" = "Site", "Dose" = "Dose"))

# Determine system-wide totals for each dose
system_wide_summary <- do.call(
  #Combine list of dataframes into single dataframe
  rbind, lapply(
    # First, split dataframe into list of dataframes by dose type
    site_data_summary %>%
      group_split(Dose),
    # Next, adorn totals for each dataframe
    function (x)
      x %>%
      adorn_totals(where = "row",
                   fill = unique(x$Dose),
                   na.rm = TRUE,
                   name = "MSHS",
                   -Dose)))
```

```{r Custom function for creating kable}

vaccine_admin_summary <- function(x, dose) {
  # Column Names ---------------
  # Determine date ranges for each week
  weekly_dates <- (vacc_week_dates %>%
                   filter(VaccWeek <= this_week) %>%
                   mutate(Title = paste0("Wk ", VaccWeek, ": ", Dates)))$Title

  # Determine dates this week through yesterday
  this_weeks_dates <- format(
  sort(unique(daily_sched_summary %>%
                filter(VaccWeek == this_week &
                         ApptDate < today) %>%
                select(ApptDate))$ApptDate), "%m/%d/%y")

  # Create column names for today's data
  todays_cols <- c(paste(format(today, "%m/%d/%y"), " - Arrived"),
                   paste(format(today, "%m/%d/%y"), " - Later Today"),
                   paste(format(today, "%m/%d/%y"), " - Total"))

  # Create vector with column names
  kable_column_names <- c(colnames(x)[1],
                      "Doses To Date",
                      weekly_dates,
                      this_weeks_dates,
                      todays_cols,
                      format(
                        as.Date(tail(colnames(x), 7), "%Y-%m-%d"), "%m/%d/%y"))

  # Header Names ------------
  # Create header for doses administered each week to date
  weekly_columns_header <- this_week
  names(weekly_columns_header) <- "Adminstered Doses By Week"

  # Create header for this week
  this_week_header <- wday(today) + 2
  names(this_week_header) <- paste("Week", this_week, "To Date")

  # Create header for schedule for next 7 days
  next_7days_header <- 7
  names(next_7days_header) <- "Scheduled Doses Over Next 7 Days"

  # Create vector with header names and length
  kable_headers <- c(" " = 2,
                   weekly_columns_header,
                   this_week_header,
                   next_7days_header)

  kable(x, format = "html", escape = FALSE,
        align = "c", digits = 0,
        col.names = kable_column_names,
        caption = paste0(dose, " Summary")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           2,
                           this_week + 2,
                           ncol(x) - 10,
                           ncol(x) - 7),
                border_right = "thin solid lightgray") %>%
    column_spec(column = c(3:(this_week + 2)),
                background = sinai_colors[2]) %>%
    column_spec(column = c((this_week + 3):(ncol(x) - 7)),
                background = sinai_colors[4]) %>%
    # include_thead =  TRUE) %>%
    column_spec(column = c((ncol(x) - 6):ncol(x)),
                background = sinai_colors[6]) %>%
    # # include_thead =  TRUE) %>%
    # column_spec(column = c(3:5), background = "inherit", color = "inherit") %>%
    # row_spec(row = 0, background = "#221f72", color = "white") %>%
    row_spec(row = nrow(x), background = "lightgrey",
             bold = T, color = "black") %>%
    add_header_above(kable_headers,
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3],
                                    sinai_colors[5]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px")

}

```

#### All Doses<br>
<p></p>
```{r Subset data and create kable for all doses administered}
all_doses <- system_wide_summary %>%
  filter(Dose == "AllDoses") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = all_doses, dose = "All Doses")

```
<p></p>

#### First Doses
<p></p>
```{r Subset data and create kable for first doses administered}
first_doses <- system_wide_summary %>%
  filter(Dose == "Dose1") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = first_doses, dose = "Dose 1")

```

<p></p>
#### Second Doses
<p></p>
```{r Subset data and create kable for second doses administered}
second_doses <- system_wide_summary %>%
  filter(Dose == "Dose2") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = second_doses, dose = "Dose 2")

```

### 2021-03-19 Evening-Huddle-Dashboard.R

@@ -1,0 +1,5 @@
+rmarkdown::render("Evening-Huddle-Stats.Rmd",
+                  output_file = paste0(user_directory,
+                                       "/Daily_PM_Huddle_Output/",
+                                       "MSHS Vaccine Summary ",
+                                       format(Sys.Date(), "%m-%d-%y")))

### 2021-03-22 Evening-Huddle-Stats.Rmd
Change format of evening huddle report markdown from having a table of contents to tabs.

@@
 title: "MSHS COVID-19 Vaccinations"
-output: 
-  html_document:
-    toc: true
-    toc_depth: 4
-    toc_float: TRUE
+output: html_document
 ---
-
-##### Summary as of `r paste(format(Sys.Date(), "%m/%d/%y"), "3:40PM")`
 
@@
 
-#### All Doses<br>
-<p></p>
+#### Administered & Scheduled Vaccines as of `r format(Sys.Date(), "%m/%d/%y")` 3:40PM {.tabset}
+
+##### All Doses
 ```{r Subset data and create kable for all doses administered}
@@
 
-#### First Doses
+##### First Doses
 <p></p>
@@
 <p></p>
-#### Second Doses
+##### Second Doses
 <p></p>

### 2021-03-23 Vaccine Sched Repo w Automated Epic Reporting.R
Add tidyr package for pivot_wider and pivot_longer. Add logic for scheduling errors when future schedules are already marked as arrived. Create templates with dates of interest for schedule breakdowns and inventory cycle analysis to ensure holiday dates are not missing from export. Update code for schedule breakdowns and inventory cycle schedule analysis to use these templates and replace cast with pivot_wider/pivot_longer.

@@ -13,6 +13,7 @@
 # install.packages("kableExtra")
 # install.packages("ggpubr")
 # install.packages("zipcodeR")
+# install.packages("tidyr")
 
 #Analysis for weekend discharge tracking
 library(readxl)
@@ -31,6 +32,7 @@ library(knitr)
 library(kableExtra)
 library(rmarkdown)
 library(zipcodeR)
+library(tidyr)
 
 # Set working directory and select raw data ----------------------------
 rm(list = ls())
@@ -207,20 +209,20 @@ sched_to_date <- sched_to_date %>%
     # Status)),
     # Update appointment status: classify any appts from prior days that are
     # still in scheduled as No Shows
-    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", Status),
+    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
+                     # Correct any appts erroneously marked as arrived early
+                     ifelse(ApptDate >= today & Status == "Arr", "Sch",
+                            Status)),
     # Determine manufacturer based on immunization field
     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
       ifelse(Status2 != "Arr", NA,
-             # Assume any visits without immunization record are Pfizer
-             ifelse(is.na(Immunizations), "Pfizer",
-                    # Any immunizations with Moderna in text classified as
-                    # Moderna, otherwise Pfizer
-                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
-                           # Any immunizations with Johnson and Johnson are
-                           # classified as J&J
-                           ifelse(str_detect(Immunizations,
-                                             "Johnson and Johnson"),
-                                  "J&J", "Pfizer")))),
+             # Any immunizations with Moderna in text classified as Moderna
+             ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
+                    # Any visiting docs or Johnson and Johnson immunizations
+                    # classified as J&J
+                    ifelse(str_detect(Department, "VISITING DOCS") |
+                             str_detect(Immunizations, "Johnson and Johnson"),
+                                        "J&J", "Pfizer"))),
[…]

### 2021-03-23 Evening-Huddle-Stats.Rmd
Update file paths based on new folder names.

@@
     default =
-      paste0(user_directory, "/Epic 340PM Sched All Status/*.*"),
+      paste0(user_directory, "/Epic PM Huddle Sched All Status/*.*"),
     caption = "Select this afternoon's Epic schedule"),

### 2021-03-23 Evening-Huddle-Dashboard.R

@@ -1,5 +1,5 @@
 rmarkdown::render("Evening-Huddle-Stats.Rmd",
                   output_file = paste0(user_directory,
-                                       "/Daily_PM_Huddle_Output/",
+                                       "/Daily PM Huddle Output/",
                                        "MSHS Vaccine Summary ",
                                        format(Sys.Date(), "%m-%d-%y")))

### 2021-03-29 Dose 1 MRN Level Schedule Export.R
Create a code to export patient level schedule details.

@@ -1,0 +1,137 @@
+# Code for importing vaccine schedule repository and exporting patient level data
+
+#Install and load necessary packages --------------------
+# install.packages("readxl")
+# install.packages("writexl")
+# install.packages("ggplot2")
+# install.packages("lubridate")
+# install.packages("dplyr")
+# install.packages("reshape2")
+# install.packages("svDialogs")
+# install.packages("stringr")
+# install.packages("formattable")
+# install.packages("kableExtra")
+# install.packages("ggpubr")
+# install.packages("zipcodeR")
+# install.packages("tidyr")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Import reference data for site and pod mappings
+site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                   "Automation Ref 2021-03-12.xlsx"),
+                            sheet = "Site Mappings")
+pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                  "Automation Ref 2021-03-12.xlsx"),
+                           sheet = "Pod Mappings Simple")
+
+# Store today's date
+today <- Sys.Date()
+
+# Save start and end dates for this analysis
+start_date <- as.Date("3/5/21", format = "%m/%d/%y")
+end_date <- as.Date("4/5/21", format = "%m/%d/%y")
+
+# Status Order
+status <- c("Arr", "Sch", "No Show", "Can", "Left", "Present")
+
+# Import Epic schedule repo
[…]

### 2021-03-30 Evening-Huddle-Stats.Rmd
Continue working on saving and importing data for Tableau.

@@
 ```{r Create and combine tables with vaccine administration and schedule data}
+# Create a template of all sites, vaccine dates, and doses ---------
+site_rep <- data.frame("Site" = sort(rep(all_sites,
+                                         length(doses))))
+
+dose_rep <- data.frame("Dose" = rep(doses,
+                                    length(all_sites)))
+
+site_dose_rep <- cbind(site_rep, dose_rep)
+
+site_dose_rep <- site_dose_rep %>%
+  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
+  arrange(Site, Dose)
+
+# Create template of next 7 days for each site and dose to ensure holidays are included
+next_7days <- seq(from = today + 1, to = today + 7, by = 1)
+
+next_7days_rep <- data.frame("ApptDate" = rep(next_7days,
+                                          length(all_sites)))
+
+site_next_7days_rep <- data.frame("Site" = sort(rep(all_sites,
+                                                    length(next_7days))))
+
+site_next_7days_templ <- cbind(site_next_7days_rep, next_7days_rep)
+
+site_dose_next_7days_templ <- left_join(site_dose_rep,
+                                        site_next_7days_templ,
+                                        by = c("Site" = "Site"))
+
 # Summarize total doses to date through today -------------
@@
 next_7days_sched <- daily_sched_summary %>%
-  filter(ApptDate %in% seq(from = today + 1, to = today + 7, by = 1)) %>%
+  filter(ApptDate %in% next_7days) %>%
   group_by(Site, Dose, ApptDate) %>%
@@
             .groups = "keep") %>%
-  ungroup() %>%
+  ungroup()
+
+next_7days_sched <- left_join(site_dose_next_7days_templ, next_7days_sched,
+                              by = c("Site" = "Site",
+                                     "Dose" = "Dose",
+                                     "ApptDate" = "ApptDate"))
+
+next_7days_sched <- next_7days_sched %>%
   pivot_wider(names_from = ApptDate,
@@
               names_sort = TRUE)
-
-# Create a template of all sites, vaccine dates, and doses ---------
-site_rep <- data.frame("Site" = sort(rep(all_sites,
-                                         length(doses))))
-
-dose_rep <- data.frame("Dose" = rep(doses,
-                                    length(all_sites)))
-
-site_dose_rep <- cbind(site_rep, dose_rep)
-
-site_dose_rep <- site_dose_rep %>%
-  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
-  arrange(Site, Dose)
 

### 2021-03-30 Convert RDS to RData Test Script.R

@@ -2,6 +2,9 @@
 
 rm(list = ls())
 
+library(dplyr)
+library()
+
 # Determine path for working directory
 if ("Presidents" %in% list.files("J://")) {
   user_directory <- paste0("J:/Presidents/HSPI-PM/",
@@ -17,6 +20,86 @@ rds_df <- readRDS(choose.files(default = paste0(user_directory,
                                                 "/R_Sched_AM_Repo/*.*"),
                                caption = "Select schedule repository"))
 
-save(rds_df, file = paste0(user_directory,
+# test_df <- data.frame("ApptNote" = unique(rds_df$`Appt Notes`))
+
+# rds_df <- rds_df %>%
+#   mutate(TestNull = ApptNote == "",
+#          NewNote = gsub("^$|^ $", NA, ApptNote))
+
+rds_df2 <- as.data.frame(rds_df)
+
+rds_df2 <- rds_df2 %>%
+  mutate(ApptNote2 = gsub("^$|^ $", NA, `Appt Notes`))
+
+test_df <- rds_df %>%
+  # filter(`Appt Notes` ==)
+  mutate(`Appt Notes` = ifelse(is.na(`Appt Notes`), "", `Appt Notes`),
+         `Canc Date` = ifelse(is.na(`Canc Date`), "", `Canc Date`),
+         `MyChart Status` = ifelse(is.na(`MyChart Status`), "", `MyChart Status`),
+         Race = ifelse(is.na(Race), "", Race),
+         Immunizations = ifelse(is.na(Immunizations), "", Immunizations),
+         `MOUNT SINAI HEALTH SYSTEM` = ifelse(is.na(`MOUNT SINAI HEALTH SYSTEM`),
+                                              "", `MOUNT SINAI HEALTH SYSTEM`),
+         `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = ifelse(
+           is.na(`PATIENTS LIFE NUMBER OR ORACLE NUMBER`), "",
+           `PATIENTS LIFE NUMBER OR ORACLE NUMBER`),
+         `Level Of Service` = ifelse(is.na(`Level Of Service`), "",
+                                     `Level Of Service`))
+         
+
+# 
+# rds_df2 <- rds_df2 %>%
+#   mutate(`Appt Notes` = NULL)
+# NOt SURE HOW TABLEAU HANDLES NA
+
+save(rds_df2, file = paste0(user_directory,
                            "/RData Exports/",
-                           "RData Test.RData"))
[…]

### 2021-03-30 Evening-Huddle-Dashboard.R

@@ -1,3 +1,13 @@
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
 rmarkdown::render("Evening-Huddle-Stats.Rmd",
                   output_file = paste0(user_directory,
                                        "/Daily PM Huddle Output/",

### 2021-03-30 Evening-Huddle-Dashboard.R
Clear environment variables before running evening huddle dashboard.

@@ -1,3 +1,5 @@
+rm(list = ls())
+
 if ("Presidents" %in% list.files("J://")) {
   user_directory <- paste0("J:/Presidents/HSPI-PM/",
                            "Operations Analytics and Optimization/Projects/",

### 2021-03-31 Dose1 with Lapsed Dose2.R
Create code to find patients who received Dose 1 but never arrived for their Dose 2 visit.

@@ -1,0 +1,217 @@
+# Code for identifying MRNs with lapsed Dose 2 -----------------
+
+#Install and load necessary packages --------------------
+# install.packages("readxl")
+# install.packages("writexl")
+# install.packages("ggplot2")
+# install.packages("lubridate")
+# install.packages("dplyr")
+# install.packages("reshape2")
+# install.packages("svDialogs")
+# install.packages("stringr")
+# install.packages("formattable")
+# install.packages("kableExtra")
+# install.packages("ggpubr")
+# install.packages("zipcodeR")
+# install.packages("tidyr")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(janitor)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Import reference data for site and pod mappings
+site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                   "Automation Ref 2021-03-12.xlsx"),
+                            sheet = "Site Mappings")
+pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                  "Automation Ref 2021-03-12.xlsx"),
+                           sheet = "Pod Mappings Simple")
+
+# Store today's date
+today <- Sys.Date()
+
+# Create dataframe with dates and weeks
+all_dates <- data.frame("Date" = seq.Date(as.Date("1/1/20",
+                                                  format = "%m/%d/%y"),
[…]

### 2021-04-01 Evening-Huddle-Stats.Rmd
Update analysis reference file with MSQ tent location.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-03-12.xlsx"),
+                                   "Automation Ref 2021-04-01.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-03-12.xlsx"),
+                                  "Automation Ref 2021-04-01.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-04-02 Vaccine Sched Repo w Automated Epic Reporting.R
Update reference file.

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-03-12.xlsx"),
+                                   "Automation Ref 2021-04-01.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-03-12.xlsx"),
+                                  "Automation Ref 2021-04-01.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-04-05 Evening-Huddle-Stats.Rmd
Update logic for this week's doses to date to include all dates, even holidays when there may not have been any appts scheduled or arrived.

@@
 
+# Create a template of this week's days for each site and dose to ensure holidays are included
+this_week_prior_days <- all_dates %>%
+  filter(VaccWeek == this_week &
+           Date < today)
+
+colnames(this_week_prior_days) <- c("ApptDate", "VaccWeek")
+
+this_week_prior_days_rep <- bind_rows(replicate(length(all_sites),
+                                              this_week_prior_days,
+                                              simplify = FALSE))
+
+site_this_week_prior_days_rep <- data.frame("Site" = sort(
+  rep(all_sites, nrow(this_week_prior_days))))
+
+site_this_week_prior_days_templ <- cbind(site_this_week_prior_days_rep,
+                                     this_week_prior_days_rep)
+
+site_dose_this_week_prior_days_templ <- left_join(site_dose_rep,
+                                                site_this_week_prior_days_templ,
+                                                by = c("Site" = "Site"))
+
 # Create template of next 7 days for each site and dose to ensure holidays are included
@@
            ApptDate < today) %>%
-  group_by(Site, Dose, VaccWeek, ApptDate) %>%
+  group_by(Site, Dose, ApptDate) %>%
   summarize(AdminDoses = sum(Count, na.rm = TRUE),
             .groups = "keep") %>%
-  ungroup() %>%
+  ungroup()
+
+# Combine with template to ensure holidays are included
+this_week_daily_admin <- left_join(site_dose_this_week_prior_days_templ,
+                                   this_week_daily_admin,
+                                   by = c("Site" = "Site",
+                                          "Dose" = "Dose",
+                                          "ApptDate" = "ApptDate"))
+
+# Pivot wider to get desired format
+this_week_daily_admin <- this_week_daily_admin %>%
   pivot_wider(names_from = c(VaccWeek, ApptDate),
@@
   # Determine dates this week through yesterday
+  # this_weeks_dates <- format(
+  # sort(unique(daily_sched_summary %>%
+  #               filter(VaccWeek == this_week &
+  #                        ApptDate < today) %>%
+  #               select(ApptDate))$ApptDate), "%m/%d/%y")
+
   this_weeks_dates <- format(
-  sort(unique(daily_sched_summary %>%
-                filter(VaccWeek == this_week &
-                         ApptDate < today) %>%
-                select(ApptDate))$ApptDate), "%m/%d/%y")
+    sort(this_week_prior_days %>%
+           select(ApptDate))$ApptDate, "%m/%d/%y")
 

### 2021-04-06 Vaccine Sched Repo w Automated Epic Reporting.R
Add code to create schedule breakdown by manufacturer.

@@ -109,7 +109,6 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 # NY zip codes
 ny_zips <- search_state("NY")
 
-
 # Import raw data from Epic
 if (update_repo) {
   if (initial_run) {
@@ -216,13 +215,16 @@ sched_to_date <- sched_to_date %>%
     # Determine manufacturer based on immunization field
     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
       ifelse(Status2 != "Arr", NA,
-             # Any immunizations with Moderna in text classified as Moderna
-             ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
-                    # Any visiting docs or Johnson and Johnson immunizations
-                    # classified as J&J
-                    ifelse(str_detect(Department, "VISITING DOCS") |
-                             str_detect(Immunizations, "Johnson and Johnson"),
-                                        "J&J", "Pfizer"))),
+             # Any blank immunizations assumed to be Pfizer
+             ifelse(is.na(Immunizations), "Pfizer",
+                    # Any immunizations with Moderna in text classified as Moderna
+                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
+                           # Any visiting docs or Johnson and Johnson
+                           # immunizations classified as J&J
+                           ifelse(str_detect(Department, "VISITING DOCS") |
+                                    str_detect(Immunizations,
+                                               "Johnson and Johnson"),
+                                  "J&J", "Pfizer")))),
     # Determine week number of year
     WeekNum = format(ApptDate, "%U"),
     # Determine appointment day of week
@@ -271,6 +273,7 @@ sched_breakdown <- sched_breakdown[order(sched_breakdown$Dose,
 
 # Create template dataframe of all sites, dose, and pod type combinations to
 # ensure all are included even if there are no scheduled appointments
+# Repeat dose types
 doses_templ <- data.frame(
   "Dose" = rep(c(1:2),
                length(all_sites)))
@@ -278,6 +281,7 @@ doses_templ <- data.frame(
 doses_templ <- doses_templ %>%
   arrange(Dose)
 
+# Repeat pod types
 pods_templ <- data.frame(
[…]

### 2021-04-06 Dose1 with Lapsed Dose2.R
Add total first doses administered column. Export sumamry to excel file.

@@ -98,7 +98,7 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 ny_zips <- search_state("NY")
 
 # Dose 1 cutoff date
-dose1_date <- as.Date("2/28/21", format = "%m/%d/%y")
+dose1_date <- as.Date("2/21/21", format = "%m/%d/%y")
 
 # Import schedule repository
 sched_repo <- readRDS(choose.files(default = paste0(user_directory,
@@ -206,7 +206,9 @@ dose1_mrns_summary <- dose1_mrns %>%
                fill = "-",
                na.rm = TRUE,
                name = "MSHS") %>%
-  mutate(PercentNoArrDose2 = percent(NoArrDose2 / (NoArrDose2 + ArrDose2), 0.1))
+  mutate(AdminDose1 = NoArrDose2 + ArrDose2,
+    PercentNoArrDose2 = percent(NoArrDose2 / AdminDose1, 0.1)) %>%
+  select(Site, AdminDose1, NoArrDose2, ArrDose2, PercentNoArrDose2)
 
 # Create list of MRN without Dose 2
 dose1_mrns_no_dose2 <- dose1_mrns %>%
@@ -214,4 +216,11 @@ dose1_mrns_no_dose2 <- dose1_mrns %>%
 
 random <- dose1_mrns_no_dose2[sample.int(nrow(dose1_mrns_no_dose2), 10), "MRN"]
 
-random_mrns
+write_xlsx(dose1_mrns_summary, path = paste0(
+  user_directory,
+  "/AdHoc/Dose1 without Arr Dose2 Through ",
+  format(dose1_date, "%Y-%m-%d"),
+  ".xlsx"))
+
+
+

### 2021-04-06 Dose1 with Lapsed Dose2.R
Change dose 1 date back to 2/28/21 from 2/21/21

@@ -98,7 +98,7 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 ny_zips <- search_state("NY")
 
 # Dose 1 cutoff date
-dose1_date <- as.Date("2/21/21", format = "%m/%d/%y")
+dose1_date <- as.Date("2/28/21", format = "%m/%d/%y")
 
 # Import schedule repository
 sched_repo <- readRDS(choose.files(default = paste0(user_directory,

### 2021-04-07 Vaccine Sched Repo w Automated Epic Reporting.R
Update reference file.

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-01.xlsx"),
+                                   "Automation Ref 2021-04-07.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-01.xlsx"),
+                                  "Automation Ref 2021-04-07.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-04-07 Dose1 with Lapsed Dose2.R
Update lapsed Dose 2 analysis to only include Dose 1 administered from 2/15-2/28.

@@ -97,8 +97,11 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 # NY zip codes
 ny_zips <- search_state("NY")
 
+# Dose 1 start date
+dose1_start_date <- as.Date("2/15/21", format = "%m/%d/%y")
+
 # Dose 1 cutoff date
-dose1_date <- as.Date("2/28/21", format = "%m/%d/%y")
+dose1_end_date <- as.Date("2/28/21", format = "%m/%d/%y")
 
 # Import schedule repository
 sched_repo <- readRDS(choose.files(default = paste0(user_directory,
@@ -165,7 +168,8 @@ sched_to_date <- left_join(sched_to_date, site_mappings,
 dose1_mrns <- sched_to_date %>%
   filter(Dose == 1 &
            Status2 == "Arr" &
-           ApptDate <= dose1_date) %>%
+           ApptDate >= dose1_start_date &
+           ApptDate <= dose1_end_date) %>%
   select(Site, MRN)
 
 dose1_mrns <- unique(dose1_mrns)
@@ -188,7 +192,8 @@ dose1_mrns <- dose1_mrns %>%
 # Identify MRNs with an administered Dose 2
 dose2_mrns <- sched_to_date %>%
   filter(Dose == 2 &
-           Status2 == "Arr")
+           Status2 == "Arr"  &
+           ApptDate > dose1_start_date)
 
 # Determine if patients with administered Dose 1 also received a Dose 2
 dose1_mrns <- dose1_mrns %>%

### 2021-04-07 Evening-Huddle-Stats.Rmd
Update reference file.
Update reference file for afternoon huddle analysis.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-01.xlsx"),
+                                   "Automation Ref 2021-04-07.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-01.xlsx"),
+                                  "Automation Ref 2021-04-07.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
   this_weeks_dates <- format(
-    sort(this_week_prior_days %>%
-           select(ApptDate))$ApptDate, "%m/%d/%y")
+    sort((this_week_prior_days %>%
+           select(ApptDate))$ApptDate), "%m/%d/%y")
 

### 2021-04-08 Vaccine Sched Repo w Automated Epic Reporting.R
Update reference file.

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-07.xlsx"),
+                                   "Automation Ref 2021-04-08.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-07.xlsx"),
+                                  "Automation Ref 2021-04-08.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-04-14 Evening-Huddle-Stats.Rmd
Update reference file pod mapping to remove MSQ duplicates.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-07.xlsx"),
+                                   "Automation Ref 2021-04-14.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-07.xlsx"),
+                                  "Automation Ref 2021-04-14.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-04-14 Vaccine Sched Repo w Automated Epic Reporting.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-08.xlsx"),
+                                   "Automation Ref 2021-04-14.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-08.xlsx"),
+                                  "Automation Ref 2021-04-14.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -242,7 +242,7 @@ sched_to_date <- sched_to_date %>%
 
 # Crosswalk pod type (employee vs patient)
 sched_to_date <- left_join(sched_to_date,
-                           pod_mappings[, c("Provider", "Pod Type")],
+                           unique(pod_mappings[, c("Provider", "Pod Type")]),
                            by = c("Provider/Resource" = "Provider"))
 
 # Assume any pods without a mapping are patient pods
@@ -252,10 +252,6 @@ sched_to_date[is.na(sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"
 sched_summary <- sched_to_date %>%
   group_by(Site, `Pod Type`, Dose, ApptDate, NYZip, Status2) %>%
   summarize(Count = n())
-
-# # Remove Network LI from sched_to_date now that data has been summarized
-# sched_to_date <- sched_to_date %>%
-#   filter(!(Site %in% "Network LI"))
 
 # Summarize schedule breakdown for next 2 weeks and export --------------------
 # Format data

### 2021-04-16 Evening-Huddle-Stats.Rmd
Update reference files with new Queens department.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-14.xlsx"),
+                                   "Automation Ref 2021-04-15.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-14.xlsx"),
+                                  "Automation Ref 2021-04-15.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-04-16 Vaccine Sched Repo w Automated Epic Reporting.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-14.xlsx"),
+                                   "Automation Ref 2021-04-15.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-14.xlsx"),
+                                  "Automation Ref 2021-04-15.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-04-16 Vaccine Sched Repo w Automated Epic Reporting.R
Add logic for fixing timezones in sched_to_date variable.

@@ -182,6 +182,8 @@ sched_to_date <- sched_repo
 
 sched_to_date <- sched_to_date %>%
   mutate(
+    # Update timezones to EST if imported as UTC
+    `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
     # Determine whether appointment is for dose 1 or dose 2
     Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                   ifelse(str_detect(Type, "DOSE 2"), 2, NA)),

### 2021-04-27 Dose1 with Lapsed Dose2.R
Update analysis to include any first doses up to 3/26/21 and exclude J&J

@@ -98,10 +98,10 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 ny_zips <- search_state("NY")
 
 # Dose 1 start date
-dose1_start_date <- as.Date("2/15/21", format = "%m/%d/%y")
+dose1_start_date <- as.Date("12/15/20", format = "%m/%d/%y")
 
 # Dose 1 cutoff date
-dose1_end_date <- as.Date("2/28/21", format = "%m/%d/%y")
+dose1_end_date <- as.Date("3/26/21", format = "%m/%d/%y")
 
 # Import schedule repository
 sched_repo <- readRDS(choose.files(default = paste0(user_directory,
@@ -169,7 +169,8 @@ dose1_mrns <- sched_to_date %>%
   filter(Dose == 1 &
            Status2 == "Arr" &
            ApptDate >= dose1_start_date &
-           ApptDate <= dose1_end_date) %>%
+           ApptDate <= dose1_end_date &
+           Mfg != "J&J") %>%
   select(Site, MRN)
 
 dose1_mrns <- unique(dose1_mrns)
@@ -224,7 +225,8 @@ random <- dose1_mrns_no_dose2[sample.int(nrow(dose1_mrns_no_dose2), 10), "MRN"]
 write_xlsx(dose1_mrns_summary, path = paste0(
   user_directory,
   "/AdHoc/Dose1 without Arr Dose2 Through ",
-  format(dose1_date, "%Y-%m-%d"),
+  format(dose1_end_date, "%Y-%m-%d"),
+  " Updated ", Sys.Date(),
   ".xlsx"))
 
 

### 2021-04-27 Vaccine Sched Repo w Automated Epic Reporting.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-15.xlsx"),
+                                   "Automation Ref 2021-04-25.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-15.xlsx"),
+                                  "Automation Ref 2021-04-25.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-04-27 Evening-Huddle-Stats.Rmd
Update reference file for afternoon report.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-15.xlsx"),
+                                   "Automation Ref 2021-04-25.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-15.xlsx"),
+                                  "Automation Ref 2021-04-25.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-05-03 Vaccine Sched Repo w Automated Epic Reporting.R
Update analysis reference file.

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-25.xlsx"),
+                                   "Automation Ref 2021-05-03.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-25.xlsx"),
+                                  "Automation Ref 2021-05-03.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-05-03 Evening-Huddle-Stats.Rmd
Update analysis reference file for afternoon/evening huddle dashboard code.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-04-25.xlsx"),
+                                   "Automation Ref 2021-05-03.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-04-25.xlsx"),
+                                  "Automation Ref 2021-05-03.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-05-18 Mimic Historical Arrived and Scheduled Spreadsheet.Rmd
Start working on a script to mimic original daily arrived and scheduled visit analysis using historical repository.

--- 2021-05-03 Evening-Huddle-Stats.Rmd
@@
 # Determine whether or not to update an existing repo
-update_repo <- TRUE
-
-# Determine whether or not to update an existing repo
 initial_run <- FALSE
-update_repo <- TRUE
+update_repo <- FALSE
 
@@
 # Store today's date
-today <- Sys.Date()
+# today <- Sys.Date()
+today <- as.Date("3/31/21", format = "%m/%d/%y")
 
@@
     choose.files(default = paste0(user_directory,
-                                  "/R_Sched_AM_Repo/*.*"),
-                 caption = "Select this morning's schedule repository"))
+                                  "/R_Sched_PM_Huddle_Repo/*.*"),
+                 caption = "Select the desired schedule repository"))
 
@@
 # Import MSSN data from Tableau
-mssn_admin <- read_excel(
+mssn_employee <- read_excel(
   path = choose.files(
     default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
-    caption = "Select latest MSSN Tableau Administration Data"),
+    caption = "Select MSSN Tableau Administration Data for Employees"),
   col_names = TRUE,
@@
 
-mssn_admin <- mssn_admin[1:nrow(mssn_admin) - 1, ]
+mssn_nonemployee <- read_excel(
+  path = choose.files(
+    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
+    caption = "Select MSSN Tableau Administration Data for Non-Employees"),
+  col_names = TRUE,
+  na = c("", NA),
+  skip = 1)
 
-colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
+mssn_employee <- mssn_employee[1:nrow(mssn_employee) - 1, ]
+mssn_nonemployee <- mssn_nonemployee[1:nrow(mssn_nonemployee) - 1, ]
+
+mssn_employee <- mssn_employee %>%
+  mutate(`Pod Type` = "Employee")
+
+mssn_nonemployee <- mssn_nonemployee %>%
+  mutate(`Pod Type` = "Patient")
+
+mssn_admin <- rbind(mssn_employee, mssn_nonemployee)
+
+colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses", "Pod Type")
 ```
@@
   group_by(Site,
+           `Pod Type`,
            Dose,
@@
 ```{r Combine data across all sites}
-
 # Bind MSSN data with Epic sites data
@@
 ```{r Create and combine tables with vaccine administration and schedule data}
-# Create a template of all sites, vaccine dates, and doses ---------
+# Create a template of all sites, vaccine dates, doses, and pod types ---------
 site_rep <- data.frame("Site" = sort(rep(all_sites,
@@
 
-site_dose_rep <- cbind(site_rep, dose_rep)
+site_dose_templ <- cbind(site_rep, dose_rep)
 
-site_dose_rep <- site_dose_rep %>%
+site_dose_templ <- site_dose_templ %>%
   mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
   arrange(Site, Dose)
+
+pod_rep <- data.frame("Pod Type" = rep(pod_type,
+                                       length(all_sites)))
+
+site_pod_rep <- data.frame("Site" = sort(rep(all_sites,
+                                             length(pod_type))))
+
+site_pod_templ <- cbind(site_pod_rep, pod_rep)
+
+site_pod_templ <- site_pod_templ %>%
+  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
+  arrange(Site, Pod.Type)
+
+site_dose_pod_templ <- left_join(site_dose_templ, site_pod_templ,
+                                 by = c("Site" = "Site"))
 
@@
 
-site_dose_this_week_prior_days_templ <- left_join(site_dose_rep,
+site_dose_this_week_prior_days_templ <- left_join(site_dose_pod_templ,
                                                   site_this_week_prior_days_templ,
@@
 
-site_dose_next_7days_templ <- left_join(site_dose_rep,
+site_dose_next_7days_templ <- left_join(site_dose_pod_templ,
                                         site_next_7days_templ,
@@
   filter(ApptDate <= today) %>%
-  group_by(Site, Dose) %>%
+  group_by(Site, `Pod Type`, Dose) %>%
+  summarize(AdminDoses = sum(Count, na.rm = TRUE),
+            .groups = "keep") %>%
+  ungroup()
+
+admin_to_date2 <- daily_sched_summary %>%
+  filter(ApptDate <= today) %>%
+  group_by(Site, `Pod Type`, Dose) %>%
   summarize(AdminDoses = sum(Count, na.rm = TRUE),
@@
   filter(VaccWeek < this_week) %>%
-  group_by(Site, Dose, VaccWeek, Dates) %>%
+  group_by(Site, `Pod Type`, Dose, VaccWeek, Dates) %>%
   summarize(AdminDoses = sum(Count, na.rm = TRUE),
@@
            ApptDate <= today) %>%
-  group_by(Site, Dose, VaccWeek, Dates) %>%
+  group_by(Site, `Pod Type`, Dose, VaccWeek, Dates) %>%
   summarize(AdminDoses = sum(Count, na.rm = TRUE),
@@
            ApptDate < today) %>%
-  group_by(Site, Dose, ApptDate) %>%
+  group_by(Site, `Pod Type`, Dose, ApptDate) %>%
   summarize(AdminDoses = sum(Count, na.rm = TRUE),
@@
                                    by = c("Site" = "Site",
+                                          "Pod.Type" = "Pod Type",
                                           "Dose" = "Dose",

### 2021-05-19 Mimic Historical Arrived and Scheduled Spreadsheet.Rmd
Modify script to summarize doses administered by manufacturer through 3/31/21.

--- 2021-05-03 Evening-Huddle-Stats.Rmd
@@
     choose.files(default = paste0(user_directory,
-                                  "/R_Sched_AM_Repo/*.*"),
-                 caption = "Select this morning's schedule repository"))
+                                  "/R_Sched_PM_Huddle_Repo/*.*"),
+                 caption = "Select the desired schedule repository"))
 
 }
+
+# Import MSSN data from Tableau
+# mssn_employee <- read_excel(
+#   path = choose.files(
+#     default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
+#     caption = "Select MSSN Tableau Administration Data for Employees"),
+#   col_names = TRUE,
+#   na = c("", NA),
+#   skip = 1)
+# 
+# mssn_nonemployee <- read_excel(
+#   path = choose.files(
+#     default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
+#     caption = "Select MSSN Tableau Administration Data for Non-Employees"),
+#   col_names = TRUE,
+#   na = c("", NA),
+#   skip = 1)
+# 
+# mssn_employee <- mssn_employee[1:nrow(mssn_employee) - 1, ]
+# mssn_nonemployee <- mssn_nonemployee[1:nrow(mssn_nonemployee) - 1, ]
+# 
+# mssn_employee <- mssn_employee %>%
+#   mutate(`Pod Type` = "Employee")
+# 
+# mssn_nonemployee <- mssn_nonemployee %>%
+#   mutate(`Pod Type` = "Patient")
+# 
+# mssn_admin <- rbind(mssn_employee, mssn_nonemployee)
 
@@
     default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
-    caption = "Select latest MSSN Tableau Administration Data"),
+    caption = "Select MSSN Tableau Administration Data"),
   col_names = TRUE,
@@
 colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
+
+mssn_admin$Mfg <- "Pfizer"
 ```
@@
 
+# Update data based on site nuances
+epic_sched_to_date <- epic_sched_to_date %>%
+  mutate(
     # Roll up any Moderna administered at MSB for YWCA to MSH
-epic_sched_to_date <- epic_sched_to_date %>%
-  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))
+    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
+    # Update all MSVD visits to J&J
+    Mfg = ifelse(Site %in% c("MSVD"), "J&J", Mfg))
 
@@
 
+# Determine expected manufacturer for scheduled appointments
+dose1_moderna <- epic_sched_to_date %>%
+  filter(Status2 %in% c("Arr") & Mfg == "Moderna" & Dose == "Dose1") %>%
+  select(MRN)
+
+epic_sched_to_date <- epic_sched_to_date %>%
+  mutate(ExpSchMfg = ifelse(Status2 != "Sch", NA,
+                            ifelse(Site == "MSVD", "J&J",
+                                   ifelse(Dose == 'Dose1', "Pfizer",
+                                          ifelse(MRN %in% dose1_moderna$MRN,
+                                                 "Moderna", "Pfizer")))),
+         MfgRollUp = ifelse(is.na(Mfg) & is.na(ExpSchMfg), NA,
+                            ifelse(is.na(ExpSchMfg), Mfg, ExpSchMfg)))
+
 # Summarize schedule data for Epic sites by key stratification
@@
   filter(Status2 %in% c("Arr", "Sch") &
-           ApptDate <= today + 7) %>%
+           ApptDate <= today) %>%
   group_by(Site,
+           MfgRollUp,
            Dose,
@@
 
+test_df <- epic_sched_summary %>%
+  filter(ApptDate <= today) %>%
+  group_by(Site, Dose) %>%
+  summarize(Admin = sum(Count, na.rm = TRUE))
+
 ```
@@
          VaccWeek = as.numeric(
-           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
+           floor((ApptDate - vacc_start_first_sun) / 7 +1)),
+         MfgRollUp = Mfg) %>%
+  filter(ApptDate <= today) %>%
   pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
@@
   left_join(vacc_week_dates, by = c("VaccWeek" = "VaccWeek"))
-```
 
-```{r Create and combine tables with vaccine administration and schedule data}
-# Create a template of all sites, vaccine dates, and doses ---------
-site_rep <- data.frame("Site" = sort(rep(all_sites,
-                                         length(doses))))
+admin_doses_by_mfg <- daily_sched_summary %>%
+  group_by(Site, Dose, MfgRollUp) %>%
+  summarize(AdminDoses = sum(Count, na.rm = TRUE))
 
-dose_rep <- data.frame("Dose" = rep(doses,
-                                    length(all_sites)))
-
-site_dose_rep <- cbind(site_rep, dose_rep)
-
-site_dose_rep <- site_dose_rep %>%
-  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
-  arrange(Site, Dose)
-
-# Create a template of this week's days for each site and dose to ensure holidays are included
-this_week_prior_days <- all_dates %>%
-  filter(VaccWeek == this_week &
-           Date < today)
-
-colnames(this_week_prior_days) <- c("ApptDate", "VaccWeek")
-
-this_week_prior_days_rep <- bind_rows(replicate(length(all_sites),
-                                              this_week_prior_days,
-                                              simplify = FALSE))
-
-site_this_week_prior_days_rep <- data.frame("Site" = sort(
-  rep(all_sites, nrow(this_week_prior_days))))
-
-site_this_week_prior_days_templ <- cbind(site_this_week_prior_days_rep,
-                                     this_week_prior_days_rep)
-
-site_dose_this_week_prior_days_templ <- left_join(site_dose_rep,
-                                                site_this_week_prior_days_templ,
-                                                by = c("Site" = "Site"))
-
-# Create template of next 7 days for each site and dose to ensure holidays are included
-next_7days <- seq(from = today + 1, to = today + 7, by = 1)
-
-next_7days_rep <- data.frame("ApptDate" = rep(next_7days,
-                                          length(all_sites)))
-
-site_next_7days_rep <- data.frame("Site" = sort(rep(all_sites,
-                                                    length(next_7days))))
-
-site_next_7days_templ <- cbind(site_next_7days_rep, next_7days_rep)
-
-site_dose_next_7days_templ <- left_join(site_dose_rep,
-                                        site_next_7days_templ,
-                                        by = c("Site" = "Site"))
-
-# Summarize total doses to date through today -------------
-admin_to_date <- daily_sched_summary %>%
-  filter(ApptDate <= today) %>%
-  group_by(Site, Dose) %>%
-  summarize(AdminDoses = sum(Count, na.rm = TRUE),
-            .groups = "keep") %>%
-  ungroup()
-
-# Summarize administered doses for prior weeks -----------------
-prior_weeks_admin <- daily_sched_summary %>%
-  filter(VaccWeek < this_week) %>%
-  group_by(Site, Dose, VaccWeek, Dates) %>%
-  summarize(AdminDoses = sum(Count, na.rm = TRUE),
-            .groups = "keep") %>%
-  ungroup() %>%
-  pivot_wider(names_from = c(VaccWeek, Dates),
-              names_prefix = "Wk ",
-              names_sep = ": ",
-              values_from = AdminDoses)
-
-# Summarize total doses administered and scheduled this week through today -----
-this_week_admin_to_date <- daily_sched_summary %>%
-  filter(VaccWeek == this_week &
-           ApptDate <= today) %>%
-  group_by(Site, Dose, VaccWeek, Dates) %>%
-  summarize(AdminDoses = sum(Count, na.rm = TRUE),
-            .groups = "keep") %>%
-  ungroup() %>%
-  pivot_wider(names_from = c(VaccWeek, Dates),
-              names_prefix = "Wk ",
-              names_sep = ": ",
-              values_from = AdminDoses)
-
-# Summarize data for this week to date -------------------
-this_week_daily_admin <- daily_sched_summary %>%
-  filter(VaccWeek == this_week &
-           ApptDate < today) %>%
-  group_by(Site, Dose, ApptDate) %>%
-  summarize(AdminDoses = sum(Count, na.rm = TRUE),
-            .groups = "keep") %>%
-  ungroup()
-
-# Combine with template to ensure holidays are included
-this_week_daily_admin <- left_join(site_dose_this_week_prior_days_templ,
-                                   this_week_daily_admin,
-                                   by = c("Site" = "Site",
-                                          "Dose" = "Dose",
-                                          "ApptDate" = "ApptDate"))
-
-# Pivot wider to get desired format
-this_week_daily_admin <- this_week_daily_admin %>%
-  pivot_wider(names_from = c(VaccWeek, ApptDate),
-              names_prefix = "Wk ",
-              names_sep = c(": "),
-              values_from = AdminDoses,
-              names_sort = TRUE)
-
-# Summarize today's arrived and scheduled doses -------------
-todays_sched <- daily_sched_summary %>%
-  filter(ApptDate == today) %>%
-  group_by(Site, Dose, ApptDate, Status2) %>%
-  summarize(AdminDoses = sum(Count, na.rm = TRUE),
-            .groups = "keep") %>%
-  pivot_wider(names_from = Status2,
-              values_from = AdminDoses) %>%
-  mutate(Total = sum(Arr, Sch, na.rm = TRUE),
-         VaccWeek = NULL) %>%
-  pivot_longer(cols = c(Arr, Sch, Total),
-               names_to = "ApptStatus",
-               values_to = "Count") %>%
-  pivot_wider(names_from = c(ApptDate, ApptStatus),
-              names_prefix = "Today's Sched: ",
-              values_from = c(Count))
-
-# Summarize scheduled data for the next 7 days ---------------
-next_7days_sched <- daily_sched_summary %>%
-  filter(ApptDate %in% next_7days) %>%
-  group_by(Site, Dose, ApptDate) %>%
-  summarize(SchedVisits = sum(Count, na.rm = TRUE),
-            .groups = "keep") %>%
-  ungroup()
-
-next_7days_sched <- left_join(site_dose_next_7days_templ, next_7days_sched,
-                              by = c("Site" = "Site",
-                                     "Dose" = "Dose",
-                                     "ApptDate" = "ApptDate"))
-
-next_7days_sched <- next_7days_sched %>%
-  pivot_wider(names_from = ApptDate,
-              values_from = SchedVisits,
-              names_sort = TRUE)
-
-# Combine all tables
-site_data_summary <- 
-  left_join(
-    left_join(
-      left_join(
-        left_join(
-          left_join(
-            left_join(
-              #First, join site and dose template with administered doses to date
-              site_dose_rep,
-              admin_to_date,
-              by = c("Site" = "Site", "Dose" = "Dose")),
-            # Second, join with administered doses from prior weeks
-            prior_weeks_admin,
-            by = c("Site" = "Site", "Dose" = "Dose")),
-          # Third, join this week's doses administered/scheduled through today
-          this_week_admin_to_date,
-          by = c("Site" = "Site", "Dose" = "Dose")),
-        # Fourth, join this week's daily data through today
-        this_week_daily_admin,
-        by = c("Site" = "Site", "Dose" = "Dose")),
-      # Fifth, join today's arrived and scheduled appts
-      todays_sched,
-      by = c("Site" = "Site", "Dose" = "Dose")),
-    # Last, join scheduled doses for the next 7 days
-    next_7days_sched,
-    by = c("Site" = "Site", "Dose" = "Dose"))
-
-# Determine system-wide totals for each dose
-system_wide_summary <- do.call(
-  #Combine list of dataframes into single dataframe
-  rbind, lapply(
-    # First, split dataframe into list of dataframes by dose type
-    site_data_summary %>%
-      group_split(Dose),
-    # Next, adorn totals for each dataframe
-    function (x)
-      x %>%
-      adorn_totals(where = "row",
-                   fill = unique(x$Dose),
-                   na.rm = TRUE,
-                   name = "MSHS",
-                   -Dose)))
-```
-
-```{r Custom function for creating kable}
-
-vaccine_admin_summary <- function(x, dose) {
-  # Column Names ---------------
-  # Determine date ranges for each week
-  weekly_dates <- (vacc_week_dates %>%
-                   filter(VaccWeek <= this_week) %>%
-                   mutate(Title = paste0("Wk ", VaccWeek, ": ", Dates)))$Title
-
-  # Determine dates this week through yesterday
-  # this_weeks_dates <- format(
-  # sort(unique(daily_sched_summary %>%
-  #               filter(VaccWeek == this_week &
-  #                        ApptDate < today) %>%
-  #               select(ApptDate))$ApptDate), "%m/%d/%y")
-
-  this_weeks_dates <- format(
-    sort((this_week_prior_days %>%
-           select(ApptDate))$ApptDate), "%m/%d/%y")
-
-  # Create column names for today's data
-  todays_cols <- c(paste(format(today, "%m/%d/%y"), " - Arrived"),
-                   paste(format(today, "%m/%d/%y"), " - Later Today"),
-                   paste(format(today, "%m/%d/%y"), " - Total"))
-
-  # Create vector with column names
-  kable_column_names <- c(colnames(x)[1],
-                      "Doses To Date",
-                      weekly_dates,
-                      this_weeks_dates,
-                      todays_cols,
-                      format(
-                        as.Date(tail(colnames(x), 7), "%Y-%m-%d"), "%m/%d/%y"))
-
-  # Header Names ------------
-  # Create header for doses administered each week to date
-  weekly_columns_header <- this_week
-  names(weekly_columns_header) <- "Adminstered Doses By Week"
-
-  # Create header for this week
-  this_week_header <- wday(today) + 2
-  names(this_week_header) <- paste("Week", this_week, "To Date")
-
-  # Create header for schedule for next 7 days
-  next_7days_header <- 7
-  names(next_7days_header) <- "Scheduled Doses Over Next 7 Days"
-
-  # Create vector with header names and length
-  kable_headers <- c(" " = 2,
-                   weekly_columns_header,
-                   this_week_header,
-                   next_7days_header)
-
-  kable(x, format = "html", escape = FALSE,
-        align = "c", digits = 0,
-        col.names = kable_column_names,
-        caption = paste0(dose, " Summary")) %>%
-    kable_styling(bootstrap_options = "hover", position = "center",
-                  font_size = 11, full_width = FALSE) %>%
-    column_spec(column = c(1,
-                           2,
-                           this_week + 2,
-                           ncol(x) - 10,
-                           ncol(x) - 7),
-                border_right = "thin solid lightgray") %>%
-    column_spec(column = c(3:(this_week + 2)),
-                background = sinai_colors[2]) %>%
-    column_spec(column = c((this_week + 3):(ncol(x) - 7)),
-                background = sinai_colors[4]) %>%
-    # include_thead =  TRUE) %>%
-    column_spec(column = c((ncol(x) - 6):ncol(x)),
-                background = sinai_colors[6]) %>%
-    # # include_thead =  TRUE) %>%
-    # column_spec(column = c(3:5), background = "inherit", color = "inherit") %>%
-    # row_spec(row = 0, background = "#221f72", color = "white") %>%
-    row_spec(row = nrow(x), background = "lightgrey",
-             bold = T, color = "black") %>%
-    add_header_above(kable_headers,
-                     background = c("",
-                                    sinai_colors[1],
-                                    sinai_colors[3],
-                                    sinai_colors[5]),
-                     line = FALSE,
-                     color = "white") %>%
-    scroll_box(width = "800px")
-
-}
+write_xlsx(admin_doses_by_mfg, path = paste0(user_directory,
+                                             "/AdHoc/Admin Doses By Mfg Through 03312021.xlsx"))
 
 ```
-
-#### Administered & Scheduled Vaccines as of `r format(Sys.Date(), "%m/%d/%y")` 3:40PM {.tabset}
-
-##### All Doses
-```{r Subset data and create kable for all doses administered}
-all_doses <- system_wide_summary %>%
-  filter(Dose == "AllDoses") %>%
-  mutate(Dose = NULL)
-
-vaccine_admin_summary(x = all_doses, dose = "All Doses")
-
-```
-<p></p>
-
-##### First Doses
-<p></p>
-```{r Subset data and create kable for first doses administered}
-first_doses <- system_wide_summary %>%
-  filter(Dose == "Dose1") %>%
-  mutate(Dose = NULL)
-
-vaccine_admin_summary(x = first_doses, dose = "Dose 1")
-
-```
-
-<p></p>
-##### Second Doses
-<p></p>
-```{r Subset data and create kable for second doses administered}
-second_doses <- system_wide_summary %>%
-  filter(Dose == "Dose2") %>%
-  mutate(Dose = NULL)
-
-vaccine_admin_summary(x = second_doses, dose = "Dose 2")
-
-```

### 2021-05-20 Evening-Huddle-Stats.Rmd
Update reference file

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-05-03.xlsx"),
+                                   "Automation Ref 2021-05-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-05-03.xlsx"),
+                                  "Automation Ref 2021-05-20.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-05-20 Vaccine Sched Repo w Automated Epic Reporting.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-05-03.xlsx"),
+                                   "Automation Ref 2021-05-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-05-03.xlsx"),
+                                  "Automation Ref 2021-05-20.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-06-16 Evening-Huddle-Stats.Rmd
Update analysis reference file.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-05-20.xlsx"),
+                                   "Automation Ref 2021-06-09.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-05-20.xlsx"),
+                                  "Automation Ref 2021-06-09.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-06-16 Ad Hoc Vaccine Reporting and Export.R
Create a new script for vaccine schedule reporting that does not need to be run every day.

@@ -1,0 +1,929 @@
+# Code for creating repository of COVID vaccine administration -----------------
+
+#Install and load necessary packages --------------------
+# install.packages("readxl")
+# install.packages("writexl")
+# install.packages("ggplot2")
+# install.packages("lubridate")
+# install.packages("dplyr")
+# install.packages("reshape2")
+# install.packages("svDialogs")
+# install.packages("stringr")
+# install.packages("formattable")
+# install.packages("kableExtra")
+# install.packages("ggpubr")
+# install.packages("zipcodeR")
+# install.packages("tidyr")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Determine whether or not to update an existing repo
+initial_run <- FALSE
+update_repo <- TRUE
+
+# Determine whether or not to update walk-in analysis
+update_walkins <- FALSE
+
+# Import reference data for site and pod mappings
+site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                   "Automation Ref 2021-06-09.xlsx"),
+                            sheet = "Site Mappings")
+pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                  "Automation Ref 2021-06-09.xlsx"),
+                           sheet = "Pod Mappings Simple")
+
+# Store today's date
+today <- Sys.Date()
+
+# Create dataframe with dates and weeks
[…]

### 2021-07-08 Daily Vaccine Reporting and Export.R
Update reference file with Adolescent Hospital.

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-07.xlsx"),
+                                   "Automation Ref 2021-07-08.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-07.xlsx"),
+                                  "Automation Ref 2021-07-08.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-07-08 Employee Arrival Tracking.Rmd
Create script for visualizing employee vaccination over the last 6 weeks and schedule/appointment demand over the next week.

---
title: "MSHS COVID-19 Vaccinations"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Install and load packages}
# Code for summarizing employee vaccinations -----------------

# Install and load necessary packages --------------------
# install.packages("readxl")
# install.packages("writexl")
# install.packages("ggplot2")
# install.packages("lubridate")
# install.packages("dplyr")
# install.packages("reshape2")
# install.packages("svDialogs")
# install.packages("stringr")
# install.packages("formattable")
# install.packages("kableExtra")
# install.packages("ggpubr")
# install.packages("zipcodeR")
# install.packages("tidyr")

# Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(janitor)
```

```{r  Import reference data and repository, set fixed variables, include = FALSE}
# Set working directory and select raw data ----------------------------
rm(list = ls())

# Determine path for working directory
if ("Presidents" %in% list.files("J://")) {
  user_directory <- paste0("J:/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
} else {
  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
}

# Set path for file selection
user_path <- paste0(user_directory, "\\*.*")

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-07-08.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-07-08.xlsx"),
                           sheet = "Pod Mappings Simple")

# Store today's date
today <- Sys.Date()

this_week_start <- today - (wday(today) - 1)

employee_summary_start <- this_week_start - 7 * 6

# Create dataframe with dates and weeks
all_dates <- data.frame("Date" = seq.Date(as.Date("1/1/20",
                                                  format = "%m/%d/%y"),
                                          as.Date("12/31/21",
                                                  format = "%m/%d/%y"),
                                          by = 1))
all_dates <- all_dates %>%
  mutate(Year = year(Date),
         WeekNum = format(Date, "%U"))

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network LI")

# Site order
city_sites <- c("MSB",
                "MSBI",
                "MSH",
                "MSM",
                "MSQ",
                "MSW",
                "MSVD")

# Employee home sites
employee_sites <- c("MSH",
                    "MSQ",
                    "MSBI",
                    "MSB",
                    "MSW",
                    "MSM",
                    "MSSN",
                    "NYEE",
                    "ISMMS",
                    "Corporate")

# Pod type order
pod_type <- c("Employee", "Patient", "All")

# Vaccine manufacturers
mfg <- c("Pfizer", "Moderna", "J&J")

# NY zip codes
ny_zips <- search_state("NY")

# Mappings for dose names for tables
dose_name_mappings = data.frame("Dose" = c("Dose1", "Dose2", "AllDoses"),
                                "Name" = c("Dose 1", "Dose 2", "All Doses"))

# Specify Sinai colors for table
sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2")

# Import schedule repository
sched_repo <- readRDS(choose.files(default = paste0(user_directory,
                                                    "/R_Sched_AM_Repo/*.*"),
                                   caption = "Select schedule repository"))
```

```{r Format and process schedule repository, include = FALSE}

# Format and analyze schedule to date for dashboards ---------------------------
sched_to_date <- sched_repo

sched_to_date <- sched_to_date %>%
  mutate(
    # Update timezones to EST if imported as UTC
    `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
    # Determine whether appointment is for dose 1 or dose 2
    Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                  ifelse(str_detect(Type, "DOSE 2"), 2, NA)),
    # Determine appointment date, year, month, etc.
    ApptDate = date(Date),
    ApptYear = year(Date),
    ApptMonth = month(Date),
    ApptDay = day(Date),
    ApptWeek = week(Date),
    # Clean up department if it is duplicated in that column
    Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
    # Group arrived, completed, and checked out appts as arrived
    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                    "Arr", `Appt Status`),
    # (Only needed when manually pulling data in the morning)
    # Classify any arrivals from today as scheduled for morning export and
    # classify any appts from prior days that are still in scheduled status as
    # no shows
    # Status2 = ifelse(ApptDate == today & Status == "Arr", "Sch",
    #                  ifelse(ApptDate < today & Status == "Sch", "No Show",
    # Status)),
    # Update appointment status: classify any appts from prior days that are
    # still in scheduled as No Shows
    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
                     # Correct any appts erroneously marked as arrived early
                     ifelse(ApptDate >= today & Status == "Arr", "Sch",
                            Status)),
    # Determine manufacturer based on immunization field
    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
      ifelse(Status2 != "Arr", NA,
             # Any blank immunizations assumed to be Pfizer
             ifelse(is.na(Immunizations), "Pfizer",
                    # Any immunizations with Moderna in text classified as Moderna
                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                           # Any visiting docs or Johnson and Johnson
                           # immunizations classified as J&J
                           ifelse(str_detect(Department, "VISITING DOCS") |
                                    str_detect(Immunizations,
                                               "Johnson and Johnson"),
                                  "J&J", "Pfizer")))),
    # Determine week number of year
    WeekNum = format(ApptDate, "%U"),
    # Determine appointment day of week
    DOW = weekdays(ApptDate),
    # Determine if patient's zip code is in NYS
    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode)

# Crosswalk sites
sched_to_date <- left_join(sched_to_date, site_mappings,
                           by = c("Department" = "Department"))

# Roll up any Moderna administered at MSB for YWCA to MSH
sched_to_date <- sched_to_date %>%
  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))

# Crosswalk pod type (employee vs patient)
sched_to_date <- left_join(sched_to_date,
                           unique(pod_mappings[, c("Provider", "Pod Type")]),
                           by = c("Provider/Resource" = "Provider"))

# Assume any pods without a mapping are patient pods
sched_to_date[is.na(sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"

sched_to_date <- sched_to_date %>%
  mutate(MSHS_Employee = str_detect(
    replace_na(`MOUNT SINAI HEALTH SYSTEM`, "No Site Provided"),
    pattern = paste(employee_sites, collapse = "|")),
         Employee_Site = ifelse(MSHS_Employee,
                            str_extract(`MOUNT SINAI HEALTH SYSTEM`,
                                        pattern = paste(employee_sites,
                                                        collapse = "|")),
                            NA))
```

```{r Analysis of arrived employee visits, include = FALSE}
arr_empl_visits <- sched_to_date %>%
  filter(MSHS_Employee & Status2 == "Arr") %>%
  mutate(WeekStart = ApptDate - (wday(ApptDate) - 1),
         WeekEnd = ApptDate + (7 - wday(ApptDate)),
         WeekOf = paste0(format(WeekStart, "%m/%d/%y"),
                         "-",
                         format(WeekEnd, "%m/%d/%y")))

all_doses <- arr_empl_visits %>%
  group_by(Site, Dose) %>%
  summarize(Count = n()) %>%
  mutate(Dose = ifelse(Dose == 1, "Dose1", "Dose2")) %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  adorn_totals(name = "MSHS", na.rm = TRUE)

arr_empl_visits_summary <- arr_empl_visits %>%
  group_by(Site,
           WeekStart,
           Dose) %>%
  summarize(Count = n()) %>%
  mutate(Dose = ifelse(Dose == 1, "Dose1", "Dose2")) %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Site = factor(Site,
                       levels = all_sites,
                       ordered = TRUE)) %>%
  arrange(Site,
          WeekStart) %>%
  filter(WeekStart > employee_summary_start) %>%
  mutate(WeekStart = format(WeekStart, "%m/%d/%y")) %>%
  pivot_wider(names_from = WeekStart,
              values_from = Count)
```

```{r Analysis for scheduled appointments over the next week, include = FALSE}
sched_outlook <- 7
sched_dates <- seq.Date(today, today + sched_outlook - 1, by = 1)

vacc_sites <- all_sites[!(all_sites == "MSVD")]

doses <- c(1, 2)

dates_rep <- data.frame(ApptDate = rep(sched_dates, length(vacc_sites)))
site_dates_rep <- data.frame(Site = sort(rep(vacc_sites, length(sched_dates))))

site_dates_templ <- cbind(site_dates_rep, dates_rep)

doses_rep <- data.frame(Dose = rep(doses, length(vacc_sites)))
site_doses_rep <- data.frame(Site = sort(rep(vacc_sites, length(doses))))

site_dose_templ <- cbind(site_doses_rep, doses_rep)

site_date_dose_templ <- left_join(site_dates_templ, site_dose_templ,
                                  by = c("Site" = "Site"))

sched_appts <- sched_to_date %>%
  filter(ApptDate >= today &
           ApptDate < today + 7 &
           Status2 == "Sch") %>%
  group_by(Site,
           ApptDate,
           Dose) %>%
  summarize(Count = n())

sched_appts <- left_join(site_date_dose_templ, sched_appts,
                         by = c("Site" = "Site",
                                "ApptDate" = "ApptDate",
                                "Dose" = "Dose"))

sched_appts_summary <- sched_appts %>%
  group_by(Site, ApptDate) %>%
  mutate(Dose = ifelse(Dose == 1, "Dose1", "Dose2")) %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Site = factor(Site,
                       levels = vacc_sites,
                       ordered = TRUE)) %>%
  arrange(Site,
          ApptDate) %>%
  mutate(ApptDate = format(ApptDate, "%m/%d/%y")) %>%
  pivot_wider(names_from = ApptDate,
              values_from = Count)

```

```{r Custom functions for creating tables of arrived and scheduled visits, include = FALSE}
arr_empl_kable <- function(dose) {
  arr_df <- arr_empl_visits_summary %>%
    filter(Dose == dose) %>%
    mutate(Dose = NULL) %>%
    adorn_totals(name = "Total",
                 na.rm = TRUE) %>%
    rename(`Vaccination Site` = Site)

  kable(arr_df,
        format = "html",
        escape = FALSE,
        align = "c",
        digits = 0,
        caption = paste0(
          dose_name_mappings$Name[dose_name_mappings$Dose == dose],
          ": Employee Vaccinations Over the Last 6 Weeks")) %>%
    kable_styling(bootstrap_options = "hover",
                  position = "center",
                  font_size = 11,
                  full_width = FALSE) %>%
    column_spec(column = c(1, ncol(arr_df)),
                border_right = "thin solid lightgray") %>%
    row_spec(row = nrow(arr_df),
             background = "lightgrey",
             bold = T,
             color = "black") %>%
    add_header_above(c(" " = 1,
                       "Week Of" = ncol(arr_df) - 1),
                     background = c("", sinai_colors[1]),
                     line = FALSE,
                     color = "white")
}

sched_appts_kable <- function(dose) {
  sch_df <- sched_appts_summary %>%
    filter(Dose == dose) %>%
    mutate(Dose = NULL) %>%
    adorn_totals(name = "Total",
                 na.rm = TRUE) %>%
    rename(`Vaccination Site` = Site)

  kable(sch_df,
        format = "html",
        escape = FALSE,
        align = "c",
        digits = 0,
        caption = paste0(
          dose_name_mappings$Name[dose_name_mappings$Dose == dose],
          ": Scheduled Appointments Over Next 7 Days")) %>%
    kable_styling(bootstrap_options = "hover",
                  position = "center",
                  font_size = 11,
                  full_width = FALSE) %>%
    column_spec(column = c(1, ncol(sch_df)),
                border_right = "thin solid lightgray") %>%
    row_spec(row = nrow(sch_df),
             background = "lightgrey",
             bold = T,
             color = "black") %>%
    add_header_above(c(" " = 1,
                       "Appointment Date" = ncol(sch_df) - 1),
                     background = c("", sinai_colors[1]),
                     line = FALSE,
                     color = "white")
}

```

### Administered Employee Vaccinations
#### Arrived Visits Through `r format(max(arr_empl_visits$ApptDate), "%m/%d/%y")` 10:40PM {.tabset}

##### All Doses
```{r Call custom function for all doses administered to employees over last 6 weeks}
arr_empl_kable(dose = "AllDoses")
```

##### Dose 1
```{r Call custom function for dose 1 administered to employees over last 6 weeks}
arr_empl_kable(dose = "Dose1")
```

##### Dose 2
```{r Call custom function for dose 2 administered to employees over last 6 weeks}
arr_empl_kable(dose = "Dose2")
```

#### {-}

<h6><i>Analysis based on repository of Epic schedule data. Employees identified as those patients who identify themselves as employees during visit, resulting in presence of MSHS site and life number in Epic.</i></h6>

### Scheduled Vaccinations
#### Employee & Patient Appointments Through `r format(max(sched_dates), "%m/%d/%y")` {.tabset}

##### All Doses
```{r Call custom function for all doses scheduled over next 7 days}
sched_appts_kable(dose = "AllDoses")
```

##### Dose 1
```{r Call custom function for dose 1 scheduled over next 7 days}
sched_appts_kable(dose = "Dose1")
```

##### Dose 2
```{r Call custom function for dose 2 scheduled over next 7 days}
sched_appts_kable(dose = "Dose2")
```

#### {-}

<h6><i>End of report.</i></h6>

### 2021-07-09 Evening-Huddle-Stats.Rmd
Update reference file with new pods.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-06-09.xlsx"),
+                                   "Automation Ref 2021-07-09.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-06-09.xlsx"),
+                                  "Automation Ref 2021-07-09.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-07-09 Daily Vaccine Reporting and Export.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-08.xlsx"),
+                                   "Automation Ref 2021-07-09.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-08.xlsx"),
+                                  "Automation Ref 2021-07-09.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-07-19 Evening-Huddle-Stats.Rmd
Update analysis reference files with latest department mappings.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-09.xlsx"),
+                                   "Automation Ref 2021-07-12.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-09.xlsx"),
+                                  "Automation Ref 2021-07-12.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-07-19 Ad Hoc Vaccine Reporting and Export.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-06-09.xlsx"),
+                                   "Automation Ref 2021-07-12.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-06-09.xlsx"),
+                                  "Automation Ref 2021-07-12.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-07-26 Evening-Huddle-Stats.Rmd
Update analysis reference file.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-12.xlsx"),
+                                   "Automation Ref 2021-07-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-12.xlsx"),
+                                  "Automation Ref 2021-07-20.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-07-26 Ad Hoc Vaccine Reporting and Export.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-12.xlsx"),
+                                   "Automation Ref 2021-07-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-12.xlsx"),
+                                  "Automation Ref 2021-07-20.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-07-26 Daily Vaccine Reporting and Export.R

@@ -60,10 +60,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-12.xlsx"),
+                                   "Automation Ref 2021-07-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-12.xlsx"),
+                                  "Automation Ref 2021-07-20.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's da

### 2021-08-20 Arr Sched Dose1 Appts.Rmd
Update reference file. Add code to render markdown for dose 1 appointments.

---
title: "MSHS Dose 1 Vaccine Appointments"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Reference data}
dashboard_start_date <- as.Date("8/5/21", format = "%m/%d/%y")

mandate_date <- as.Date("8/12/21", format = "%m/%d/%y")

sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2",
                  "#7F7F7F")
```

```{r Summarize and format first dose schedule data}

# Summarize first dose arrived and scheduled visits
first_dose_sch <- sched_to_date %>%
  filter(ApptDate >= dashboard_start_date &
           Dose == 1 &
           Status2 %in% c("Arr", "Sch") &
           !(Site %in% c("MSVD"))) %>%
  mutate(Timeframe = ifelse(ApptDate < mandate_date, "Before Mandate",
                            "After Mandate")) %>%
  group_by(Site, ApptDate, Status2, Timeframe) %>%
  summarize(Count = n()) %>%
  ungroup() %>%
  arrange(ApptDate, Site) %>%
  pivot_wider(names_from = c(ApptDate, Status2, Timeframe),
              values_from = Count,
              names_sep = ";") %>%
  adorn_totals(where = "row",
               name = "MSHS",
               na.rm = TRUE) %>%
  pivot_longer(cols = starts_with("2021-"),
               names_to = c("ApptDate", "Status2", "Timeframe"),
               names_sep = ";",
               values_to = "Count") %>%
  mutate(ApptDate = as.Date(ApptDate, "%Y-%m-%d"))

# Format schedule summary for use in kable
sch_summary_table <- first_dose_sch %>%
  mutate(ApptDate = format(ApptDate, "%m/%d/%y"),
         Timeframe = NULL) %>%
  pivot_wider(names_from = c(ApptDate, Status2),
              values_from = Count,
              names_sort = FALSE,
              names_sep = ";")

# Create a function for creating site level kables
first_dose_kable <- function(site) {
  site_sch_kable <- sch_summary_table %>%
    filter(Site == site)

  arr_col_start <- min(
    which(str_detect(colnames(site_sch_kable), ";Arr")))
  arr_col_end <- max(
    which(str_detect(colnames(site_sch_kable), ";Arr")))
  sch_col_start <- min(
    which(str_detect(colnames(site_sch_kable), ";Sch")))
  sch_col_end <- max(
    which(str_detect(colnames(site_sch_kable), ";Sch")))

  kable_col_names <- gsub(";.*", "", colnames(site_sch_kable))

  kable_headers <- c(" " = 1,
                   "Arrived Visits" = (arr_col_end - arr_col_start + 1),
                   "Scheduled Visits" = (sch_col_end - sch_col_start + 1))

  kable(site_sch_kable, format = "html", escape = FALSE,
        align = "c", digits = 0,
        col.names = kable_col_names,
        caption = paste0(site, " Dose 1 Summary")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           arr_col_end,
                           sch_col_end),
                border_right = "thin solid lightgray") %>%
    column_spec(column = c(arr_col_start:arr_col_end),
                background = sinai_colors[2]) %>%
    column_spec(column = c(sch_col_start:sch_col_end),
                background = sinai_colors[4]) %>%
    add_header_above(kable_headers,
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px")

}

first_dose_graph <- function(site) {
  site_sch_graph <- first_dose_sch %>%
    filter(Site == site)

  ggplot(site_sch_graph,
         aes(fill = Status2,
             y = Count,
             x = ApptDate)) +
    geom_col(position = "identity") +
    labs(title = paste(site,
                       " Arrived and Scheduled Dose 1 Visits"),
         x = "Date",
         y = "Volume") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5),
          legend.position = "bottom",
          axis.text.x = element_text(angle = 30, hjust = 1)) +
    guides(fill = guide_legend(title = "Visit Status")) +
    geom_text(aes(x = ApptDate, y = Count, label = Count),
              # color = "white",
              # position = "identity",
              color = "black",
              position = "identity",
              vjust = -0.5, 
              # position = position_nudge(y = 0.5),
              size = 3) +
    scale_fill_manual(values = c(sinai_colors[1], sinai_colors[3]),
                      breaks = unique(site_sch_graph$Status2),
                      labels = c("Arrived", "Scheduled")) +
    scale_y_continuous(expand = c(0, 0, 0.1, 0)) +
    scale_x_date(date_labels = "%m/%d",
                 breaks = seq.Date(from = min(site_sch_graph$ApptDate),
                                   to = max(site_sch_graph$ApptDate),
                                   by = 2),
                 expand = c(0, 1)) +
  geom_vline(xintercept = mandate_date,
             color = "#7F7F7F",
             linetype ="dashed",
             size = .75) +
  geom_text(aes(x = mandate_date, y = max(site_sch_graph$Count, na.rm = TRUE)*1.15),
            label = "Vaccine Mandate Date",
            color = "#7F7F7F",
            size = 4,
            hjust = 0)
}

```

## {.tabset}

### MSHS
```{r Create table and graph for MSHS}
first_dose_kable(site = "MSHS")
asis_output("<h4>")
first_dose_graph(site = "MSHS")
```

### MSBI
```{r Create table and graph for MSBI}
first_dose_kable(site = "MSBI")
asis_output("<h4>")
first_dose_graph(site = "MSBI")
```

### MSB
```{r Create table and graph for MSB}
first_dose_kable(site = "MSB")
asis_output("<h4>")
first_dose_graph(site = "MSB")
```

### MSH
```{r Create table and graph for MSH}
first_dose_kable(site = "MSH")
asis_output("<h4>")
first_dose_graph(site = "MSH")
```

### MSM
```{r Create table and graph for MSM}
first_dose_kable(site = "MSM")
asis_output("<h4>")
first_dose_graph(site = "MSM")
```

### MSQ
```{r Create table and graph for MSQ}
first_dose_kable(site = "MSQ")
asis_output("<h4>")
first_dose_graph(site = "MSQ")
```

### MSW
```{r Create table and graph for MSW}
first_dose_kable(site = "MSW")
asis_output("<h4>")
first_dose_graph(site = "MSW")
```

## {-}

### 2021-08-20 Evening-Huddle-Stats.Rmd
Update reference file. Add code to render markdown for dose 1 appointments.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-20.xlsx"),
+                                   "Automation Ref 2021-08-16.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-20.xlsx"),
+                                  "Automation Ref 2021-08-16.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-08-20 Daily Vaccine Reporting and Export.R

@@ -33,6 +33,7 @@ library(kableExtra)
 library(rmarkdown)
 library(zipcodeR)
 library(tidyr)
+library(janitor)
 
 # Set working directory and select raw data ----------------------------
 rm(list = ls())
@@ -60,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-07-20.xlsx"),
+                                   "Automation Ref 2021-08-16.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-07-20.xlsx"),
+                                  "Automation Ref 2021-08-16.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's da
@@ -908,3 +909,11 @@ write_xlsx(export_list, path = paste0(user_directory,
                                       "Auto Epic Report Sched Data Export ",
                                       format(Sys.time(), "%m%d%y %H%M"),
                                       ".xlsx"))
+
+rmarkdown::render(input = "Arr Sched Dose1 Appts.Rmd",
+                  output_file = paste0(
+                    user_directory,
+                    "/Vaccine Mandate Dashboard Output",
+                    "/MSHS Dose 1 Sched ",
+                    format(Sys.Date(), "%m-%d-%y")))
+

### 2021-08-23 Manual Update for Dose 3.R
Continue cleaning up manual script with Dose 2. Make corrects for erroneously documented dose 2 J&J.

@@ -247,9 +247,12 @@ sched_to_date <- sched_to_date %>%
 sched_to_date <- left_join(sched_to_date, site_mappings,
                            by = c("Department" = "Department"))
 
-# Roll up any Moderna administered at MSB for YWCA to MSH
+# Manually update discrepancies in site/mfg/dose
 sched_to_date <- sched_to_date %>%
-  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))
+  mutate(# Roll up any Moderna administered at MSB for YWCA to MSH
+    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
+    # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
+    Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c(2), 1, Dose))
 
 # Crosswalk pod type (employee vs patient)
 sched_to_date <- left_join(sched_to_date,
@@ -373,6 +376,10 @@ site_dose_mfg_date_templ <- left_join(site_dates_templ,
                                       site_dose_mfg_templ,
                                       by = c("Site" = "Site"))
 
+# Manually remove J&J dose 2 and 3 from template
+site_dose_mfg_date_templ <- site_dose_mfg_date_templ %>%
+  filter(!(Mfg == "J&J" & Dose > 1))
+
 # Merge template dataframe with schedule breakdown data
 sched_breakdown <- left_join(site_dose_date_templ,
                              sched_breakdown,
@@ -413,8 +420,11 @@ city_sites_sched <- city_sites_sched %>%
   #Determine expected manufacturer for scheduled appointment based on above
   # assumptions
   mutate(ExpSchMfg = ifelse(Status2 != "Sch", NA,
+                            # Assume all MSVD scheduled appointments receive J&J
                             ifelse(Site == "MSVD", "J&J",
-                                   ifelse(Dose == 1, "Pfizer",
+                                   # Assume all scheduled Dose 1 and Dose 3 appointments receive Pfizer
+                                   ifelse(Dose %in% c(1, 3), "Pfizer",
+                                          # Assume scheduled Dose 2 only receive Moderna if Dose 1 was Moderna
[…]

### 2021-08-24 Manual Update for Dose 3.R
Add code to determine if patient is an employee based on response to question at time of vaccination and presence of MSHS site for older visits. Add summary of arrived appointments for employees vs non-employees to daily export.

@@ -125,6 +125,10 @@ if (update_repo) {
                                                         "/R_Sched_AM_Repo/*.*"),
                                        caption = "Select schedule repository"))
     
+    # # Manually add a column for MSHS employee to historical repo one time
+    # sched_repo <- sched_repo %>%
+    #   mutate(`Is the patient a Mount Sinai employee` = NA)
+    
     # # Convert appointment date in schedule repository from posixct to date
     # sched_repo <- sched_repo %>%
     #   mutate(ApptDate = date(ApptDate))
@@ -189,6 +193,7 @@ if (update_repo) {
 sched_to_date <- sched_repo
 
 sched_to_date <- sched_to_date %>%
+  rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
   mutate(
     # Update timezones to EST if imported as UTC
     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
@@ -241,7 +246,18 @@ sched_to_date <- sched_to_date %>%
     # Determine appointment day of week
     DOW = weekdays(ApptDate),
     # Determine if patient's zip code is in NYS
-    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode)
+    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
+    # Determine if patient is a MSHS employee based on response to question
+    MSHSEmployee =
+      # First see if patient responded "YES" to question about MSHS employee
+      str_detect(
+        str_replace_na(IsPtEmployee, ""),
+        regex("yes", ignore_case = TRUE)) |
+      # Next, see if there is a MSHS site listed for patients who were vaccinated
+      # prior to the addition of the MSHS employee field
+      str_detect(
+        str_replace_na(`MOUNT SINAI HEALTH SYSTEM`, " "),
+        regex("[a-z]", ignore_case = TRUE)))
 
 # Crosswalk sites
 sched_to_date <- left_join(sched_to_date, site_mappings,
@@ -266,6 +282,14 @@ sched_to_date[is.na(sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"
 sched_summary <- sched_to_date %>%
   group_by(Site, `Pod Type`, Dose, ApptDate, NYZip, Status2) %>%
   summarize(Count = n())
+
+# Summarize arrivals by patient type (employees vs. non-employees)
+employee_arr <- sched_to_date %>%
+  filter(Status2 %in% c("Arr")) %>%
[…]

### 2021-08-24 Manual Update for Dose 3.R
Create script to show departmets at each site with highest number of people no reporting vaccination status.

@@ -883,3 +883,8 @@ write_xlsx(export_list, path = paste0(user_directory,
                                       format(Sys.time(), "%m%d%y %H%M"),
                                       ".xlsx"))
 
+rmarkdown::render(input = "Vax_Arr_Sch_Tracking_Tool.Rmd",
+                  output_file = paste0(user_directory,
+                                       "/Daily Dashboard Drafts",
+                                       "/Vaccine Arr & Sch Tracking Tool ",
+                                       format(Sys.Date(), "%Y-%m-%d")))

### 2021-08-24 Render_Depts_Not_Reporting_Status.R

@@ -1,0 +1,7 @@
+rmarkdown::render(input = "MSHS_Depts_NotReporting_VaccineStatus.Rmd",
+                  output_file = paste0(
+                    user_directory,
+                    "/AdHoc",
+                    "/Vaccine Status Non Reporting Depts",
+                    "/MSHS Vaccination Status - Depts Not Reporting ",
+                    format(Sys.Date(), "%m-%d-%y")))

### 2021-08-25 Empl_Arrival_Tracking.Rmd
Create code and script for daily tracking of employee vaccinations.

---
output: html_document
---

### MSHS COVID-19 Employee Vaccination Tracking
#### As of `r format(Sys.Date(), "%m/%d/%y")`
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Create table to track employee arrivals}
empl_arr_start_date <- as.Date("8/20/21", format = "%m/%d/%y")

empl_arr_date_range <- seq.Date(from = empl_arr_start_date,
                                to = today - 1,
                                by = 1)
empl_vacc_sites <- c("MSH", "MSQ", "MSBI", "MSB", "MSM", "MSW")

empl_vacc_doses <- 1:3

empl_vacc_sites_dates <- data.frame(
  "Site" = sort(rep(empl_vacc_sites, length(empl_arr_date_range))),
  "ApptDate" = rep(empl_arr_date_range, length(empl_vacc_sites)))

empl_vacc_sites_doses <- data.frame(
  "Site" = sort(rep(empl_vacc_sites, length(empl_vacc_doses))),
  "Dose" = rep(empl_vacc_doses, length(empl_vacc_sites)))

empl_vacc_templ <- left_join(empl_vacc_sites_dates,
                             empl_vacc_sites_doses,
                             by = c("Site" = "Site"))

empl_arr_df <- employee_arr %>%
  filter(PatientType == "Employee" &
           ApptDate >= employee_arr_start_date) %>%
  mutate(PatientType = NULL)

empl_arr_df <- left_join(empl_vacc_templ,
                         empl_arr_df,
                         by = c("Site" = "Site",
                                "ApptDate" = "ApptDate",
                                "Dose" = "Dose"))

empl_arr_df_test <- empl_arr_df %>%
  mutate(Count = replace_na(Count, 0))  %>%
  pivot_wider(names_from = c(Dose, ApptDate),
              names_sep = "_",
              values_from = "Count",
              names_sort = FALSE,
              names_prefix = "Dose") %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  pivot_longer(cols = contains("Dose"),
               names_to = c("Dose", "ApptDate"),
               names_sep = "_",
               values_to = "Count") %>%
  mutate(Dose = str_replace(Dose, "Dose", "Dose "),
         Site = factor(Site, levels = c(empl_vacc_sites, "MSHS"), ordered = TRUE),
         ApptDate = as.Date(ApptDate, format = "%Y-%m-%d")) %>%
  arrange(Dose, ApptDate, Site) %>%
  relocate(Site, .after = Dose) %>%
  mutate(ApptDate = format(ApptDate, "%m/%d/%y")) %>%
  pivot_wider(names_from = c(Dose, Site),
              names_sep = "_",
              values_from = Count) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "Total") %>%
  pivot_longer(cols = contains("Dose"),
               names_to = c("Dose", "Site"),
               names_sep = "_",
               values_to = "Count") %>%
  pivot_wider(names_from = ApptDate,
              values_from = Count,
              names_sort = FALSE)

empl_vacc_tables <- function(dose) {
  data <- empl_arr_df_test %>%
    filter(Dose == paste("Dose", dose)) %>%
    mutate(Dose = NULL)

  kable(data, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste("Dose", dose, "Employee Vaccine Arrivals")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(data) - 1,
                           ncol(data)),
                border_right = "thin solid lightgray") %>%
    column_spec(column = ncol(data),
                bold = TRUE,
                italic = TRUE) %>%
    add_header_above(c(" " = 1, "Date" = ncol(data) - 1),
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(data),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE)
}
```

```{r Dose 1}
empl_vacc_tables(dose = 1)

```
###

```{r Dose 2}
empl_vacc_tables(dose = 2)
```
###

```{r Dose 3}
empl_vacc_tables(dose = 3)
```

<h4><bold>Data Sources:</bold></h4>
Analysis based on Epic schedule data for arrived appointments through prior day. Employees identified as those patients who answer "yes" when asked if s/he is a Mount Sinai employee.

### 2021-08-25 Manual Update for Dose 3.R

@@ -888,3 +888,10 @@ rmarkdown::render(input = "Vax_Arr_Sch_Tracking_Tool.Rmd",
                                        "/Daily Dashboard Drafts",
                                        "/Vaccine Arr & Sch Tracking Tool ",
                                        format(Sys.Date(), "%Y-%m-%d")))
+
+
+rmarkdown::render(input = "Empl_Arrival_Tracking.Rmd",
+                  output_file = paste0(user_directory,
+                                       "/Daily Dashboard Drafts",
+                                       "/Employee Arrival Tracking Tool ",
+                                       format(Sys.Date(), "%Y-%m-%d")))

### 2021-08-31 Empl_Arrival_Tracking.Rmd
Update markdown file for daily employee vaccine tracking. Update top level file to reflect changes to automated report.

@@
 
+# MSHS color scheme
+sinai_colors <- c("#221f72", "#C4C3EF",
+                  "#00AEEF", "#B3EBFF",
+                  "#D80B8C", "#FBB6E2",
+                  "#7F7F7F")
+
 empl_vacc_sites_dates <- data.frame(
@@
   filter(PatientType == "Employee" &
-           ApptDate >= employee_arr_start_date) %>%
+           ApptDate >= empl_arr_start_date) %>%
   mutate(PatientType = NULL)

### 2021-08-31 Manual Update for Dose 3.R

@@ -135,13 +135,14 @@ if (update_repo) {
     
     raw_df <- read.csv(choose.files(
       default =
-        paste0(user_directory, "/Epic Manual Sched Pulls/*.*"),
+        paste0(user_directory, "/Epic Auto Report Sched All Status/*.*"),
       caption = "Select current Epic schedule"),
       stringsAsFactors = FALSE,
       check.names = FALSE)
   }
   
-  new_sched <- raw_df[, 1:ncol(raw_df) - 1]
+  new_sched <- raw_df
+  # new_sched <- raw_df[, 1:ncol(raw_df) - 1]
   
   # Remove test patient
   new_sched <- new_sched[new_sched$Patient != "Patient, Test", ]
@@ -151,12 +152,14 @@ if (update_repo) {
     mutate(DOB = as.Date(DOB, format = "%m/%d/%Y"),
            `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
            Date = as.Date(Date, format = "%m/%d/%Y"),
-           `Appt Time` = as.POSIXct(
-             ifelse(nchar(`Appt Time`) == 3,
-                    paste0("1899-12-31 0", `Appt Time`),
-                    paste0("1899-12-31 ", `Appt Time`)),
-             tz = "",
-             format = "%Y-%m-%d %H%M"),
+           `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
+                                    tz = "", format = "%Y-%m-%d %H:%M %p"),
+           # `Appt Time` = as.POSIXct(
+           #   ifelse(nchar(`Appt Time`) == 3,
+           #          paste0("1899-12-31 0", `Appt Time`),
+           #          paste0("1899-12-31 ", `Appt Time`)),
+           #   tz = "",
+           #   format = "%Y-%m-%d %H%M"),
            
            # `Appt Time` = as.POSIXct(paste0("1899-12-31 ", `Appt Time`),
            #                          tz = "", format = "%Y-%m-%d %H%M"),
@@ -883,11 +886,11 @@ write_xlsx(export_list, path = paste0(user_directory,
                                       format(Sys.time(), "%m%d%y %H%M"),
                                       ".xlsx"))
 
-rmarkdown::render(input = "Vax_Arr_Sch_Tracking_Tool.Rmd",
-                  output_file = paste0(user_directory,
-                                       "/Daily Dashboard Drafts",
-                                       "/Vaccine Arr & Sch Tracking Tool ",
[…]

### 2021-08-31 Ad Hoc Vaccine Reporting and Export.R
Update daily and ad hoc vaccine reporting and export scripts to account for third doses.

@@ -34,6 +34,7 @@ library(rmarkdown)
 library(zipcodeR)
 library(tidyr)
 library(purrr)
+library(janitor)
 
 # Set working directory and select raw data ----------------------------
 rm(list = ls())
@@ -186,12 +187,14 @@ if (update_repo) {
 sched_to_date <- sched_repo
 
 sched_to_date <- sched_to_date %>%
+  rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
   mutate(
     # Update timezones to EST if imported as UTC
     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
-    # Determine whether appointment is for dose 1 or dose 2
+    # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
     Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
-                  ifelse(str_detect(Type, "DOSE 2"), 2, NA)),
+                  ifelse(str_detect(Type, "DOSE 2"), 2,
+                         ifelse(str_detect(Type, "DOSE 3"), 3, NA))),
     # Determine appointment date, year, month, etc.
     ApptDate = date(Date),
     ApptYear = year(Date),
@@ -237,15 +240,29 @@ sched_to_date <- sched_to_date %>%
     # Determine appointment day of week
     DOW = weekdays(ApptDate),
     # Determine if patient's zip code is in NYS
-    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode)
+    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
+    # Determine if patient is a MSHS employee based on response to question
+    MSHSEmployee =
+      # First see if patient responded "YES" to question about MSHS employee
+      str_detect(
+        str_replace_na(IsPtEmployee, ""),
+        regex("yes", ignore_case = TRUE)) |
+      # Next, see if there is a MSHS site listed for patients who were vaccinated
+      # prior to the addition of the MSHS employee field
+      str_detect(
+        str_replace_na(`MOUNT SINAI HEALTH SYSTEM`, " "),
+        regex("[a-z]", ignore_case = TRUE)))
 
 # Crosswalk sites
 sched_to_date <- left_join(sched_to_date, site_mappings,
                            by = c("Department" = "Department"))
 
-# Roll up any Moderna administered at MSB for YWCA to MSH
+# Manually update discrepancies in site/mfg/dose
[…]

### 2021-08-31 Daily Vaccine Reporting and Export.R

@@ -67,7 +67,7 @@ pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-08-16.xlsx"),
                            sheet = "Pod Mappings Simple")
 
-# Store today's da
+# Store today's date
 today <- Sys.Date()
 
 # Create dataframe with dates and weeks
@@ -82,24 +82,24 @@ all_dates <- all_dates %>%
 
 # Site order
 all_sites <- c("MSB",
-           "MSBI",
-           "MSH",
-           "MSM",
-           "MSQ",
-           "MSW",
-           "MSVD",
-           "Network LI")#,
-           # "MSHS")
+               "MSBI",
+               "MSH",
+               "MSM",
+               "MSQ",
+               "MSW",
+               "MSVD",
+               "Network LI")#,
+# "MSHS")
 
 # Site order
 city_sites <- c("MSB",
-           "MSBI",
-           "MSH",
-           "MSM",
-           "MSQ",
-           "MSW",
-           "MSVD")#,
-           # "MSHS")
+                "MSBI",
+                "MSH",
+                "MSM",
+                "MSQ",
+                "MSW",
+                "MSVD")#,
+# "MSHS")
 
 # Pod type order
 pod_type <- c("Employee", "Patient", "All")
@@ -124,10 +124,6 @@ if (update_repo) {
     sched_repo <- readRDS(choose.files(default = paste0(user_directory,
                                                         "/R_Sched_AM_Repo/*.*"),
                                        caption = "Select schedule repository"))
-
-    # # Convert appointment date in schedule repository from posixct to date
-    # sched_repo <- sched_repo %>%
-    #   mutate(ApptDate = date(ApptDate))
 
     raw_df <- read.csv(choose.files(
       default =
@@ -182,12 +178,14 @@ if (update_repo) {
 sched_to_date <- sched_repo
 
 sched_to_date <- sched_to_date %>%
+  rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
   mutate(
     # Update timezones to EST if imported as UTC
     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
-    # Determine whether appointment is for dose 1 or dose 2
+    # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
     Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
[…]

### 2021-08-31 Manual Update for Dose 3.R

@@ -124,15 +124,7 @@ if (update_repo) {
     sched_repo <- readRDS(choose.files(default = paste0(user_directory,
                                                         "/R_Sched_AM_Repo/*.*"),
                                        caption = "Select schedule repository"))
-    
-    # # Manually add a column for MSHS employee to historical repo one time
-    # sched_repo <- sched_repo %>%
-    #   mutate(`Is the patient a Mount Sinai employee` = NA)
-    
-    # # Convert appointment date in schedule repository from posixct to date
-    # sched_repo <- sched_repo %>%
-    #   mutate(ApptDate = date(ApptDate))
-    
+
     raw_df <- read.csv(choose.files(
       default =
         paste0(user_directory, "/Epic Auto Report Sched All Status/*.*"),
@@ -200,7 +192,7 @@ sched_to_date <- sched_to_date %>%
   mutate(
     # Update timezones to EST if imported as UTC
     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
-    # Determine whether appointment is for dose 1 or dose 2
+    # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
     Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                   ifelse(str_detect(Type, "DOSE 2"), 2,
                          ifelse(str_detect(Type, "DOSE 3"), 3, NA))),
@@ -287,7 +279,7 @@ sched_summary <- sched_to_date %>%
   summarize(Count = n())
 
 # Summarize arrivals by patient type (employees vs. non-employees)
-employee_arr <- sched_to_date %>%
+arr_pt_type_summary <- sched_to_date %>%
   filter(Status2 %in% c("Arr")) %>%
   mutate(PatientType = ifelse(MSHSEmployee, "Employee", "Non-Employee")) %>%
   group_by(Site, ApptDate, Dose, PatientType) %>%
@@ -870,7 +862,7 @@ admin_to_date_mfg_export <- left_join(city_sites_doses_mfg, admin_to_date_mfg_ca
 # Export schedule summary, schedule breakdown, and cumulative administered
 # doses to excel file
 export_list <- list("SchedSummary" = sched_summary,
-                    "Arrivals_PatientType" = employee_arr,
+                    "Arrivals_PatientType" = arr_pt_type_summary,
                     "SchedBreakdown" = sched_breakdown_cast,
[…]

### 2021-09-01 Evening-Huddle-Dashboard.R
Update evening huddle dashboard to reflect alternate format for reporting arrived and scheduled appointments.

@@ -10,8 +10,9 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-rmarkdown::render("Evening-Huddle-Stats.Rmd",
+rmarkdown::render("Weekly_Arrivals_Future_Sched_Tracking.Rmd",
                   output_file = paste0(user_directory,
                                        "/Daily PM Huddle Output/",
                                        "MSHS Vaccine Summary ",
                                        format(Sys.Date(), "%m-%d-%y")))
+

### 2021-09-09 Empl_Arrival_Tracking.Rmd
Update daily and ad hoc vaccine reporting and export scripts to account for third doses.
Add scroll boxes to daily employee vaccination report.

@@
 
-empl_arr_df <- employee_arr %>%
+empl_arr_df <- arr_pt_type_summary %>%
   filter(PatientType == "Employee" &
@@
              italic = TRUE,
-             hline_after = TRUE)
+             hline_after = TRUE) %>%
+    scroll_box(width = "800px")
 }

### 2021-09-29 Daily Vaccine Reporting and Export.R
Update analysis reference file.

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-09-17.xlsx"),
+                                   "Automation Ref 2021-09-29.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-09-17.xlsx"),
+                                  "Automation Ref 2021-09-29.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-09-29 Amb_Sched_Tracking.Rmd
Create file for tracking weekly arrivals and schedule data for vaccine pod huddle. Create new markdown file and render file for tracking dose 3 schedule data to support ambulatory operations team.

---
output: html_document
---

### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Install and load packages}
# Code for updating data analysis for afternoon huddle

#Install and load necessary packages --------------------
#install.packages("readraw_dfl")
#install.packages("writeraw_dfl")
#install.packages("ggplot2")
#install.packages("lubridate")
#install.packages("dplyr")
#install.packages("reshape2")
#install.packages("svDialogs")
#install.packages("stringr")
#install.packages("formattable")
#install.packages("ggpubr")
#install.packages("zipcodeR")
#install.packages("tidyr")
#install.packages("janitor")
#install.packages("knitr")
#install.packages("rmarkdown")
#install.packages("kableExtra")

#Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(janitor)
library(knitr)
library(rmarkdown)
library(kableExtra)
```

```{r Import schedule data and reference data}
# Set path for file selection
user_path <- paste0(user_directory, "\\*.*")

# Determine whether or not to update an existing repo
initial_run <- FALSE
update_repo <- TRUE

# Determine whether or not to update walk-in analysis
update_walkins <- FALSE

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-09-29.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-09-29.xlsx"),
                           sheet = "Pod Mappings Simple")

# MSHS color scheme
sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2",
                  "#7F7F7F")

# Store today's date
today <- Sys.Date()

# Create dataframe with dates and weeks
all_dates <- data.frame("Date" = seq.Date(as.Date("1/1/20",
                                                  format = "%m/%d/%y"),
                                          as.Date("12/31/21",
                                                  format = "%m/%d/%y"),
                                          by = 1))
all_dates <- all_dates %>%
  mutate(Year = year(Date),
         WeekNum = format(Date, "%U"))

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network LI")

report_run_time <- ifelse(hour(Sys.time()) > 14, "PM", "AM")

sched_data_file <- choose.files(
  default =
    paste0(user_directory,
           ifelse(report_run_time == "AM",
                  "/Epic Auto Report Sched All Status/*.*",
                  "/Epic PM Huddle Sched All Status/*.*")),
      caption = "Select current Epic schedule")

report_date <- date(file.info(sched_data_file)$ctime)

raw_data <- read.csv(sched_data_file,
                     stringsAsFactors = FALSE,
                     check.names = FALSE)

```

```{r Format and preprocess raw schedule data}
sched_data <- raw_data %>%
  filter(Patient != "Patient, Test") %>%
  rename(MadeDate = `Made Date`,
         IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
  mutate(DOB = as.Date(DOB, format = "%m/%d/%Y"),
         MadeDate = as.Date(MadeDate, format = "%m/%d/%y"),
         ApptDate = as.Date(Date, format = "%m/%d/%Y"),
         # Clean up department if it is duplicated in that column
         Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
         # Group arrived, completed, and checked out appointments as arrived
         Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                         "Arr", `Appt Status`),
         # Update appointment status: classify any appts from prior days that are
         # still in scheduled as No Shows
         Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
                          # Correct any appts erroneously marked as arrived early
                          ifelse(report_date < today &
                                   ApptDate >= today &
                                   Status == "Arr", "Sch",
                                 Status)),
         # Determine whether appointment is for dose 1, 2, or 3 based on
         # scheduled visit type
         Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                       ifelse(str_detect(Type, "DOSE 2"), 2,
                              ifelse(str_detect(Type, "DOSE 3"), 3, NA))))

# Crosswalk sites
sched_data <- left_join(sched_data, site_mappings,
                        by = c("Department" = "Department"))

```

```{r Create template of sites and dates}
dates_2wks <- seq.Date(from = today - 1,
                       to = today + 14,
                       by = 1)

dates_templ <- data.frame(
  "Date" = rep(dates_2wks,
               length(all_sites)),
   stringsAsFactors = FALSE)

dates_templ <- dates_templ %>%
  arrange(Date)

# Combine site and dates
site_dates_templ <- data.frame(
  "Site" = rep(all_sites, length(dates_2wks)),
  "Date" = dates_templ,
  stringsAsFactors = FALSE)

```

```{r Subset dose 3 schedule data}
# Create dose 3 schedule summary for ambulatory team
dose3_sch_next_2wks <- sched_data %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate %in% dates_2wks &
           Dose == 3) %>%
  group_by(ApptDate, Site, Status2) %>%
  summarize(Count = n())

dose3_sch_next_2wks <- left_join(
  site_dates_templ,
  dose3_sch_next_2wks, 
  by = c("Site" = "Site",
         "Date" = "ApptDate")
)

dose3_sch_next_2wks <- dose3_sch_next_2wks %>%
  mutate(Count = replace_na(Count, 0),
         Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
                          ifelse(is.na(Status2) & Date >= today, "Sch",
                                 Status2)),
         Date = format(Date, "%m/%d/%y"))

dose3_sch_next_2wks_cast <- pivot_wider(dose3_sch_next_2wks,
                                        names_from = c(Status2, Date),
                                        names_sep = "_",
                                        names_sort = FALSE,
                                        values_from = Count)

dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS")

dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
  mutate_all(~replace_na(., 0))

col_names_df <- colnames(dose3_sch_next_2wks_cast)
col_names_table <- str_replace(col_names_df, regex("^[a-z]*_", ignore_case = TRUE), "")
arr_cols <- max(which(str_detect(col_names_df, "Arr"))) - min(which(str_detect(col_names_df, "Arr"))) + 1
sch_cols <- max(which(str_detect(col_names_df, "Sch"))) - min(which(str_detect(col_names_df, "Sch"))) + 1

kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
        align = "c", digits = 0,
        # caption = paste("Dose 3 Schedule"),
      col.names = col_names_table) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(dose3_sch_next_2wks_cast)),
                border_right = "thin solid lightgray") %>%
    add_header_above(c(" " = 1,
                       "Arrived Visits" = arr_cols,
                       "Scheduled Visits" = sch_cols),
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3]),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(dose3_sch_next_2wks_cast),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE) %>%
    scroll_box(width = "800px")

```

```{r Subset dose 3 appointments made yesterday and today for all appointment statuses}
# Summarize all appointments made yesterday and today, regardless of appointment status
dose3_sch_made_date <- sched_data %>%
  filter(MadeDate %in% seq.Date(today - 1, today, by = 1) &
           ApptDate %in% dates_2wks &
           Dose == 3)

made_dates <- sort(unique(dose3_sch_made_date$MadeDate))

made_dates_str <- ifelse(length(made_dates) == 1,
                         format(made_dates, "%m/%d/%y"),
                         paste(format(min(made_dates), "%m/%d/%y"),
                                "to",
                               format(max(made_dates), "%m/%d/%y")))

dose3_made_date_all_status <- dose3_sch_made_date %>%
  group_by(Site, ApptDate) %>%
  summarize(Count = n())

dose3_made_date_all_status <- left_join(
  site_dates_templ,
  dose3_made_date_all_status,
  by = c("Site" = "Site",
         "Date" = "ApptDate")
)

dose3_made_date_all_status <- dose3_made_date_all_status %>%
  mutate(Count = replace_na(Count, 0),
         Date = format(Date, "%m/%d/%y"))

dose3_made_date_all_status_cast <- pivot_wider(
  dose3_made_date_all_status,
  names_from = Date,
  values_from = Count,
  names_sort = FALSE
)

dose3_made_date_all_status_cast <- dose3_made_date_all_status_cast %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  adorn_totals(where = "col",
               na.rm = TRUE,
               name = "Total")

kable_dose3_made_date_all_status <- 
  kable(dose3_made_date_all_status_cast,
        format = "html",
        escape = FALSE,
        align = "c",
        digits = 0,
        caption = "All Appointment Statuses Including Cancellations & No Shows") %>%
  kable_styling(bootstrap_options = "hover",
                position = "center",
                font_size = 11,
                full_width = FALSE) %>%
  column_spec(column = c(1,
                         ncol(dose3_made_date_all_status_cast) -1,
                         ncol(dose3_made_date_all_status_cast)),
                border_right = "thin solid lightgray") %>%
  add_header_above(c(" " = 1,
                     "Appointment Date" =
                       ncol(dose3_made_date_all_status_cast) - 1),
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
  row_spec(row = nrow(dose3_made_date_all_status_cast),
           bold = TRUE,
           italic = TRUE,
           hline_after = TRUE) %>%
  column_spec(column = ncol(dose3_made_date_all_status_cast),
              bold = TRUE,
              italic = TRUE) %>%
  scroll_box(width = "800px")

```

```{r Further subset dose 3 appointment made yesterday and today to only include arrived and scheduled appointments}
dose3_made_date_arr_sch <- dose3_sch_made_date %>%
  filter(Status2 %in% c("Arr", "Sch")) %>%
  group_by(Site, ApptDate) %>%
  summarize(Count = n())

dose3_made_date_arr_sch <- left_join(
  site_dates_templ,
  dose3_made_date_arr_sch,
  by = c("Site" = "Site",
         "Date" = "ApptDate")
)

dose3_made_date_arr_sch <- dose3_made_date_arr_sch %>%
  mutate(Count = replace_na(Count, 0),
         Date = format(Date, "%m/%d/%y"))

dose3_made_date_arr_sch_cast <- pivot_wider(
  dose3_made_date_arr_sch,
  names_from = Date,
  values_from = Count,
  names_sort = FALSE
)

dose3_made_date_arr_sch_cast <- dose3_made_date_arr_sch_cast %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  adorn_totals(where = "col",
               na.rm = TRUE,
               name = "Total")

kable_dose3_made_date_arr_sch <-
  kable(dose3_made_date_arr_sch_cast,
        format = "html",
        escape = FALSE,
        align = "c",
        digits = 0,
        caption = "Arrived & Scheduled Appointments Only") %>%
  kable_styling(bootstrap_options = "hover",
                position = "center",
                font_size = 11,
                full_width = FALSE) %>%
  column_spec(column = c(1,
                         ncol(dose3_made_date_arr_sch_cast) -1,
                         ncol(dose3_made_date_arr_sch_cast)),
                border_right = "thin solid lightgray") %>%
  add_header_above(c(" " = 1,
                     "Appointment Date" =
                       ncol(dose3_made_date_arr_sch_cast) - 1),
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
  row_spec(row = nrow(dose3_made_date_arr_sch_cast),
           bold = TRUE,
           italic = TRUE,
           hline_after = TRUE) %>%
  column_spec(column = ncol(dose3_made_date_arr_sch_cast),
              bold = TRUE,
              italic = TRUE) %>%
  scroll_box(width = "800px")

```

```{r Create kable for scheduled appointments over next 14 days}

asis_output(paste0("<h4>Based on Epic schedule data as of ",
                   format(file.info(sched_data_file)$ctime,
                          "%m/%d/%y %I:%M %p"),
                   "</h4>"))

asis_output("<br>")
asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>")
kable_dose3_sch

asis_output("<br>")
asis_output("<br>")
asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ",
                   made_dates_str,
                   "</h4>"))

kable_dose3_made_date_all_status

asis_output("<br>")

kable_dose3_made_date_arr_sch

asis_output("<h6><i>End of report.</i></h6>")

```

### 2021-09-29 Weekly_Arrivals_Future_Sched_Tracking.Rmd
Create file for tracking weekly arrivals and schedule data for vaccine pod huddle. Create new markdown file and render file for tracking dose 3 schedule data to support ambulatory operations team.

--- 2021-08-20 Evening-Huddle-Stats.Rmd
@@
 # Determine whether or not to update an existing repo
-update_repo <- TRUE
-
-# Determine whether or not to update an existing repo
 initial_run <- FALSE
@@
 today <- Sys.Date()
+yesterday <- today - 1
 
@@
 
+vacc_week_dates_today <- all_dates %>%
+  filter(Date <= today) %>%
+  group_by(VaccWeek) %>%
+  summarize(Dates =
+              paste0(format(min(Date), "%m/%d/%y"),
+                     "-",
+                     format(max(Date), "%m/%d/%y")))
+
 # Create variable with doses
-doses <- c("Dose1", "Dose2", "AllDoses")
+doses <- c("Dose1", "Dose2", "Dose3", "AllDoses")
 
@@
     # Determine whether appointment is for dose 1 or dose 2
-    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose1",
-                  ifelse(str_detect(Type, "DOSE 2"), "Dose2", NA)),
+    Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
+                  ifelse(str_detect(Type, "DOSE 2"), 2,
+                         ifelse(str_detect(Type, "DOSE 3"), 3, NA))),
     # Determine appointment date, year, month, etc.
@@
                            # classified as J&J
-                           ifelse(str_detect(Immunizations,
+                           ifelse(str_detect(Department, "VISITING DOCS") |
+                                    str_detect(Immunizations,
                                                "Johnson and Johnson"),
@@
 
-# Roll up any Moderna administered at MSB for YWCA to MSH
+# Manually update discrepancies in site/mfg/dose
 epic_sched_to_date <- epic_sched_to_date %>%
-  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))
+  mutate(# Roll up any Moderna administered at MSB for YWCA to MSH
+    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
+    # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
+    Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c(2), 1, Dose))
 
@@
   pivot_wider(names_from = Dose,
+              names_prefix = "Dose",
               values_from = Count) %>%
-  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
-  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
+  mutate(AllDoses = sum(Dose1, Dose2, Dose3, na.rm = TRUE)) %>%
+  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
                names_to = "Dose",
                values_to = "Count") %>%
+  mutate(Count = replace_na(Count, 0)) %>%
   ungroup()
@@
          VaccWeek = as.numeric(
-           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
-  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
+           floor((ApptDate - vacc_start_first_sun) / 7 +1)),
+         Dose3 = NA) %>%
+  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
                names_to = "Dose",
-               values_to = "Count")
+               values_to = "Count") %>%
+  mutate(Count = replace_na(Count, 0))
 
@@
               values_from = AdminDoses) %>%
-  mutate(Total = sum(Arr, Sch, na.rm = TRUE),
+  mutate(Sch = 0,
+         Total = sum(Arr, Sch, na.rm = TRUE),
          VaccWeek = NULL) %>%
@@
 
+```{r Alternate format}
+arr_visits <- daily_sched_summary %>%
+  filter(Status2 %in% c("Arr")) %>%
+  group_by(Site, Dose, VaccWeek) %>%
+  summarize(Count = sum(Count, na.rm = TRUE))
+
+arr_visits <- left_join(arr_visits,
+                        vacc_week_dates_today,
+                        by = c("VaccWeek" = "VaccWeek"))
+arr_visits <- arr_visits %>%
+  arrange(Site, Dose, VaccWeek) %>%
+  mutate(WkDate = paste0("Wk ", VaccWeek, ": ", Dates),
+         VaccWeek = NULL,
+         Dates = NULL)
+
+arr_visits_totals <- arr_visits %>%
+  pivot_wider(names_from = c(Dose, WkDate),
+              names_sep = "__",
+              values_from = Count) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "MSHS") %>%
+  pivot_longer(cols = contains("__", ignore.case = TRUE),
+               names_to = c("Dose", "Week"),
+               names_sep = "__",
+               values_to = "Count") %>%
+  mutate(Count = replace_na(Count, 0)) %>%
+  pivot_wider(names_from = c(Site, Dose),
+              names_sep = "__",
+              values_from = Count) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "TotalDosesAdmin") %>%
+  pivot_longer(cols = contains("__", ignore.case = TRUE),
+               names_to = c("Site", "Dose"),
+               names_sep = "__",
+               values_to = "Count") %>%
+  relocate(Site) %>%
+  relocate(Dose, .after = Site) %>%
+  pivot_wider(names_from = Week,
+              values_from = Count) %>%
+  relocate(TotalDosesAdmin, .after = Dose) %>%
+  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
+         Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
+  arrange(Site, Dose)
+
+arr_visits_kable <- function(dose) {
+  if (!(dose %in% c(1, 2, 3, "All"))) {
+    msg <- "Invalid argument"
+    stop(msg)
+  } else {
+    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
+                          paste0(dose, "Doses"))
+
+    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
+                         paste (dose, "Doses"))
+    arr_visits_kable_df <<- arr_visits_totals %>%
+      filter(Dose == dose_filter) %>%
+      mutate(Dose = NULL) %>%
+      rename(`Admin Doses to Date` = TotalDosesAdmin)
+
+    arr_visits_kable_headers <- 
+      c(" " = 2,
+        "Administered Doses by Week" = ncol(arr_visits_kable_df) - 2)
+
+    kable(arr_visits_kable_df, format = "html", escape = FALSE,
+        align = "c", digits = 0,
+        caption = paste0(dose_title, ": Administered Doses To Date")) %>%
+    kable_styling(bootstrap_options = "hover", position = "center",
+                  font_size = 11, full_width = FALSE) %>%
+    column_spec(column = c(1,
+                           2,
+                           ncol(arr_visits_kable_df)),
+                border_right = "thin solid lightgray") %>%
+    column_spec(column = c(3:ncol(arr_visits_kable_df)),
+                background = sinai_colors[2]) %>%
+    row_spec(row = nrow(arr_visits_kable_df),
+             background = "lightgrey",
+             bold = T,
+             italic = T,
+             color = "black") %>%
+    add_header_above(arr_visits_kable_headers,
+                     background = c("",
+                                    sinai_colors[1]),
+                     line = FALSE,
+                     color = "white") %>%
+    scroll_box(width = "800px")
+  }
+}
+
+# arr_visits_kable(dose = 3)
+# 
+# 
+# arr_visits_kable_df <- arr_visits_totals %>%
+#   filter(Dose == "AllDoses") %>%
+#   mutate(Dose = NULL) %>%
+#   rename(`Admin Doses to Date` = TotalDosesAdmin)
+# 
+# arr_visits_kable_headers <- 
+#   c(" " = 2,
+#     "Admin Doses by Week" = ncol(arr_visits_kable_df) - 2)
+# 
+# 
+# kable(arr_visits_kable_df, format = "html", escape = FALSE,
+#         align = "c", digits = 0,
+#         caption = paste0("All Doses", " Summary")) %>%
+#     kable_styling(bootstrap_options = "hover", position = "center",
+#                   font_size = 11, full_width = FALSE) %>%
+#     column_spec(column = c(1,
+#                            2,
+#                            ncol(arr_visits_kable_df)),
+#                 border_right = "thin solid lightgray") %>%
+#     column_spec(column = c(3:ncol(arr_visits_kable_df)),
+#                 background = sinai_colors[2]) %>%
+#     row_spec(row = nrow(arr_visits_kable_df),
+#              background = "lightgrey",
+#              bold = T,
+#              italic = T,
+#              color = "black") %>%
+#     add_header_above(arr_visits_kable_headers,
+#                      background = c("",
+#                                     sinai_colors[1]),
+#                      line = FALSE,
+#                      color = "white") %>%
+#     scroll_box(width = "800px")
+
+sch_visits <- daily_sched_summary %>%
+  filter(Status2 %in% c("Sch")) %>%
+  group_by(Site, Dose, ApptDate) %>%
+  summarize(Count = sum(Count, na.rm = TRUE))
+
+# Create template of today through the next 7 days for each site and dose to ensure holidays are included
+today_to_7days <- seq(from = today, to = today + 7, by = 1)
+
+today_to_7days_rep <- data.frame("ApptDate" = rep(today_to_7days,
+                                          length(all_sites)))
+
+site_today_to_7days_rep <- data.frame("Site" = sort(rep(all_sites,
+                                                        length(today_to_7days))))
+
+site_today_to_7days_templ <- cbind(site_today_to_7days_rep, today_to_7days_rep)
+
+site_dose_today_to_7days_templ <- left_join(site_dose_rep,
+                                            site_today_to_7days_templ,
+                                            by = c("Site" = "Site"))
+
+sch_visits <- left_join(site_dose_today_to_7days_templ,
+                          sch_visits,
+                          by = c("Site" = "Site",
+                                 "Dose" = "Dose",
+                                 "ApptDate" = "ApptDate"))
+
+sch_visits_totals <- sch_visits %>%
+  mutate(Count = replace_na(Count, 0)) %>%
+  arrange(Site, Dose, ApptDate) %>%
+  pivot_wider(names_from = c(Dose, ApptDate),
+              names_sep = "__",
+              values_from = Count,
+              names_sort = FALSE) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "MSHS") %>%
+  pivot_longer(cols = contains("__", ignore.case = TRUE),
+               names_to = c("Dose", "Date"),
+               names_sep = "__",
+               values_to = "Count") %>%
+  mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%m/%d")) %>%
+  pivot_wider(names_from = c(Site, Dose),
+              names_sep = "__",
+              values_from = Count) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "Total") %>%
+  pivot_longer(cols = contains("__", ignore.case = TRUE),
+               names_to = c("Site", "Dose"),
+               names_sep = "__",
+               values_to = "Count") %>%
+  relocate(Site) %>%
+  relocate(Dose, .after = Site) %>%
+  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
+         Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
+  arrange(Site, Dose) %>%
+  pivot_wider(names_from = Date,
+              values_from = Count)
+
+# sch_visits_kable_df <-sch_visits_totals %>%
+#   filter(Dose == "AllDoses") %>%
+#   mutate(Dose = NULL)
+# 
+# sch_visits_kable_headers <- 
+#   c(" " = 1,
+#     "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)
+# 
+# 
+# kable(sch_visits_kable_df, format = "html", escape = FALSE,
+#         align = "c", digits = 0,
+#         caption = paste0("All Doses", " Summary")) %>%
+#     kable_styling(bootstrap_options = "hover", position = "center",
+#                   font_size = 11, full_width = FALSE) %>%
+#     column_spec(column = c(1,
+#                            ncol(sch_visits_kable_df) - 1,
+#                            ncol(sch_visits_kable_df)),
+#                 border_right = "thin solid lightgray") %>%
+#     row_spec(row = nrow(sch_visits_kable_df),
+#              background = "lightgrey",
+#              bold = T,
+#              italic = T,
+#              color = "black") %>%
+#     add_header_above(sch_visits_kable_headers,
+#                      background = c("",
+#                                     sinai_colors[1]),
+#                      line = FALSE,
+#                      color = "white") %>%
+#     scroll_box(width = "800px")
+
+sch_visits_kable <- function(dose) {
+  if (!(dose %in% c(1, 2, 3, "All"))) {
+    msg <- "Invalid argument"
+    stop(msg)
+  } else {
+    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
+                          paste0(dose, "Doses"))
+
+    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
+                         paste (dose, "Doses"))
+    sch_visits_kable_df <- sch_visits_totals %>%
+      filter(Dose == dose_filter) %>%
+      mutate(Dose = NULL)
+
+    sch_visits_kable_headers <-
+      c(" " = 1,
+        "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)
+
+    kable(sch_visits_kable_df, format = "html", escape = FALSE,
+          align = "c", digits = 0,
+          caption = paste0(dose_title, ": Scheduled Appointments")) %>%
+      kable_styling(bootstrap_options = "hover", position = "center",
+                    font_size = 11, full_width = FALSE) %>%
+      column_spec(column = c(1,
+                             ncol(sch_visits_kable_df) - 1,
+                             ncol(sch_visits_kable_df)),
+                  border_right = "thin solid lightgray") %>%
+      row_spec(row = nrow(sch_visits_kable_df),
+               background = "lightgrey",
+               bold = T,
+               italic = T,
+               color = "black") %>%
+      add_header_above(sch_visits_kable_headers,
+                       background = c("",
+                                      sinai_colors[1]),
+                       line = FALSE,
+                       color = "white")
+  }
+}
+
+```
+
 #### Administered & Scheduled Vaccines as of `r format(Sys.Date(), "%m/%d/%y")` 3:40PM {.tabset}
@@
 ```{r Subset data and create kable for all doses administered}
-all_doses <- system_wide_summary %>%
-  filter(Dose == "AllDoses") %>%
-  mutate(Dose = NULL)
+# all_doses <- system_wide_summary %>%
+#   filter(Dose == "AllDoses") %>%
+#   mutate(Dose = NULL)
+# 
+# vaccine_admin_summary(x = all_doses, dose = "All Doses")
 
-vaccine_admin_summary(x = all_doses, dose = "All Doses")
+arr_visits_kable(dose = "All")
+
+asis_output("<h3>  </h3>")
+
+sch_visits_kable(dose = "All")
 
@@
 ```{r Subset data and create kable for first doses administered}
-first_doses <- system_wide_summary %>%
-  filter(Dose == "Dose1") %>%
-  mutate(Dose = NULL)
+# first_doses <- system_wide_summary %>%
+#   filter(Dose == "Dose1") %>%
+#   mutate(Dose = NULL)
+# 
+# vaccine_admin_summary(x = first_doses, dose = "Dose 1")
 
-vaccine_admin_summary(x = first_doses, dose = "Dose 1")
+arr_visits_kable(dose = 1)
+
+asis_output("<h3>  </h3>")
+
+sch_visits_kable(dose = 1)
 
@@
 ```{r Subset data and create kable for second doses administered}
-second_doses <- system_wide_summary %>%
-  filter(Dose == "Dose2") %>%
-  mutate(Dose = NULL)
+# second_doses <- system_wide_summary %>%
+#   filter(Dose == "Dose2") %>%
+#   mutate(Dose = NULL)
+# 
+# vaccine_admin_summary(x = second_doses, dose = "Dose 2")
 
-vaccine_admin_summary(x = second_doses, dose = "Dose 2")
+arr_visits_kable(dose = 2)
+
+asis_output("<h3>  </h3>")
+
+sch_visits_kable(dose = 2)
 
 ```
+
+<p></p>
+##### Third Doses
+<p></p>
+```{r Subset data and create kable for third doses administered}
+# third_doses <- system_wide_summary %>%
+#   filter(Dose == "Dose3") %>%
+#   mutate(Dose = NULL)
+# 
+# vaccine_admin_summary(x = third_doses, dose = "Dose 3")
+
+arr_visits_kable(dose = 3)
+
+asis_output("<h3>  </h3>")
+
+sch_visits_kable(dose = 3)
+
+```

### 2021-09-29 Render_Amb_Sched_Tracking.R

@@ -1,0 +1,19 @@
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+rmarkdown::render(input = "Amb_Sched_Tracking.Rmd",
+                  output_file = paste0(user_directory,
+                                       "/Dose3 Amb Sched Tracking",
+                                       "/Dose3 Schedule Tracking ",
+                                       format(Sys.time(), "%Y-%m-%d %I%M%p")))

### 2021-09-30 Amb_Sched_Tracking.Rmd
Add a column with total for arrived and scheduled appointments.

@@
                na.rm = TRUE,
-               name = "MSHS")
+               name = "MSHS") %>%
+  adorn_totals(where = "col",
+               na.rm = TRUE,
+               name = "Total")
 
@@
       col.names = col_names_table) %>%
-    kable_styling(bootstrap_options = "hover", position = "center",
-                  font_size = 11, full_width = FALSE) %>%
+  kable_styling(bootstrap_options = "hover",
+                position = "center",
+                font_size = 11,
+                full_width = FALSE) %>%
   column_spec(column = c(1,
+                         ncol(dose3_sch_next_2wks_cast) - 1,
                          ncol(dose3_sch_next_2wks_cast)),
@@
                      "Arrived Visits" = arr_cols,
-                       "Scheduled Visits" = sch_cols),
+                     "Scheduled Visits" = sch_cols,
+                     " " = 1),
                    background = c("",
                                   sinai_colors[1],
-                                    sinai_colors[3]),
+                                  sinai_colors[3],
+                                  ""),
                    line = FALSE,
@@
            hline_after = TRUE) %>%
+  column_spec(column = ncol(dose3_sch_next_2wks_cast),
+           bold = TRUE,
+           italic = TRUE) %>%
   scroll_box(width = "800px")

### 2021-10-12 Amb_Sched_Tracking.Rmd
Update analysis reference file. Change format of daily amb schedule tracking dashboard to include all scheduled doses.

--- 2021-09-29 Amb_Sched_Tracking.Rmd
@@
 ---
-output: html_document
+title: MSHS COVID-19 Vaccine Schedule Tracking
+output:
+  html_document:
+    toc: true
+    toc_depth: 3
+    toc_float:
+      collapsed: false
 ---
 
-### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking
+<!-- ### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking -->
 
@@
 ```{r Create template of sites and dates}
+# Create dataframe of dates for next 2 weeks
 dates_2wks <- seq.Date(from = today - 1,
@@
 
+# Create dataframe of doses
+all_doses <- seq(from = 1, to = 3, by = 1)
+
+doses_templ <- data.frame(
+  "Dose" = rep(all_doses,
+               length(all_sites)))
+
+doses_templ <- doses_templ %>%
+  arrange(Dose)
+
 # Combine site and dates
@@
 
+# Combine site and doses
+site_doses_templ <- data.frame(
+  "Site" = rep(all_sites, length(all_doses)),
+  "Dose" = doses_templ,
+  stringsAsFactors = FALSE)
+
+site_date_dose_templ <- left_join(site_dates_templ,
+                                  site_doses_templ,
+                                  by = c("Site" = "Site"))
+
+```
+
+```{r Summarize schedule data by day and dose}
+sched_summary <- sched_data %>%
+  filter(Status2 %in% c("Arr", "Sch") &
+           ApptDate %in% dates_2wks) %>%
+  group_by(Dose, Site, Status2, ApptDate) %>%
+  summarize(Count = n(), .groups = "keep")
+
+sched_summary <- left_join(site_date_dose_templ,
+                           sched_summary,
+                           by = c("Site" = "Site",
+                                  "Date" = "ApptDate",
+                                  "Dose" = "Dose"))
+
+sched_summary <- sched_summary %>%
+  mutate(Count = replace_na(Count, 0),
+         Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
+                          ifelse(is.na(Status2) & Date >= today, "Sch",
+                                 Status2))) %>%
+  arrange(Site, Date, Dose, Status2) %>%
+  mutate(
+    # Date = format(Date, "%m/%d/%y"),
+         Dose = paste0("Dose", Dose))
+
+sched_summary_table <- pivot_wider(sched_summary,
+                                   names_from = c(Status2, Dose, Date),
+                                   names_sep = "_",
+                                   names_sort = FALSE,
+                                   values_from = Count) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "MSHS") %>%
+  pivot_longer(cols = contains("_"),
+               names_to = c("Status2", "Dose", "Date"),
+               names_sep = "_",
+               values_to = "Count") %>%
+  # arrange(Site, Date, Status2) %>%
+  pivot_wider(names_from = c(Site, Status2, Date),
+              names_sep = "_",
+              names_sort = FALSE,
+              values_from = Count) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "AllDoses") %>%
+  pivot_longer(cols = contains("_"),
+               names_to = c("Site", "Status2", "Date"),
+               names_sep = "_",
+               values_to = "Count") %>%
+  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
+         Dose = factor(Dose, levels = c("Dose1", "Dose2", "Dose3", "AllDoses")),
+         Count = replace_na(Count, 0),
+         Date = as.Date(Date, format = "%Y-%m-%d")) %>%
+  arrange(Site, Date, Status2) %>%
+  mutate(Date = format(Date, "%m/%d/%y")) %>%
+  pivot_wider(names_from = c(Status2, Date),
+              names_sep = "_",
+              names_sort = FALSE,
+              values_from = Count) %>%
+  adorn_totals(where = "col",
+               na.rm = TRUE,
+               name = "Total")
+
+```
+
+```{r Create a kable for each dose}
+
+sched_data_kable <- function(dose) {
+  kable_dose <- dose
+
+  kable_dose_title <- ifelse(dose == "AllDoses", "All Doses",
+                             str_replace(kable_dose, "Dose", "Dose "))
+
+  sched_kable_df <- sched_summary_table %>%
+  filter(Dose == kable_dose) %>%
+  mutate(Dose = NULL)
+
+  sched_summary_cols <- colnames(sched_kable_df)
+  sched_summary_table_names <- str_replace(sched_summary_cols,
+                                           regex("^[a-z]*_",
+                                                 ignore_case = TRUE),
+                                           "")
+
+  arr_cols <- max(which(str_detect(sched_summary_cols, "Arr"))) -
+    min(which(str_detect(sched_summary_cols, "Arr"))) + 1
+
+  sch_cols <- max(which(str_detect(sched_summary_cols, "Sch"))) -
+    min(which(str_detect(sched_summary_cols, "Sch"))) + 1
+
+  sched_kable <- kable(sched_kable_df,
+                       format = "html",
+                       escape = FALSE,
+                       align = "c",
+                       digits = 0,
+                       caption = paste(kable_dose_title, "Schedule"),
+                       col.names = sched_summary_table_names) %>%
+    kable_styling(bootstrap_options = "hover",
+                  position = "center",
+                  font_size = 11,
+                  full_width = FALSE) %>%
+    column_spec(column = c(1,
+                           ncol(sched_kable_df) - 1,
+                           ncol(sched_kable_df)),
+                border_right = "thin solid lightgray") %>%
+    add_header_above(c(" " = 1,
+                       "Arrived Visits" = arr_cols,
+                       "Scheduled Visits" = sch_cols,
+                       " " = 1),
+                     background = c("",
+                                    sinai_colors[1],
+                                    sinai_colors[3],
+                                    ""),
+                     line = FALSE,
+                     color = "white") %>%
+    row_spec(row = nrow(sched_kable_df),
+             bold = TRUE,
+             italic = TRUE,
+             hline_after = TRUE) %>%
+    column_spec(column = ncol(sched_kable_df),
+                bold = TRUE,
+                italic = TRUE) %>%
+    scroll_box(width = "800px")
+
+  return(sched_kable)
+}
+
 ```
@@
 ```{r Subset dose 3 schedule data}
-# Create dose 3 schedule summary for ambulatory team
-dose3_sch_next_2wks <- sched_data %>%
-  filter(Status2 %in% c("Arr", "Sch") &
-           ApptDate %in% dates_2wks &
-           Dose == 3) %>%
-  group_by(ApptDate, Site, Status2) %>%
-  summarize(Count = n())
-
-dose3_sch_next_2wks <- left_join(
-  site_dates_templ,
-  dose3_sch_next_2wks, 
-  by = c("Site" = "Site",
-         "Date" = "ApptDate")
-)
-
-dose3_sch_next_2wks <- dose3_sch_next_2wks %>%
-  mutate(Count = replace_na(Count, 0),
-         Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
-                          ifelse(is.na(Status2) & Date >= today, "Sch",
-                                 Status2)),
-         Date = format(Date, "%m/%d/%y"))
-
-dose3_sch_next_2wks_cast <- pivot_wider(dose3_sch_next_2wks,
-                                        names_from = c(Status2, Date),
-                                        names_sep = "_",
-                                        names_sort = FALSE,
-                                        values_from = Count)
-
-dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
-  adorn_totals(where = "row",
-               na.rm = TRUE,
-               name = "MSHS")
-
-dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
-  mutate_all(~replace_na(., 0))
-
-col_names_df <- colnames(dose3_sch_next_2wks_cast)
-col_names_table <- str_replace(col_names_df, regex("^[a-z]*_", ignore_case = TRUE), "")
-arr_cols <- max(which(str_detect(col_names_df, "Arr"))) - min(which(str_detect(col_names_df, "Arr"))) + 1
-sch_cols <- max(which(str_detect(col_names_df, "Sch"))) - min(which(str_detect(col_names_df, "Sch"))) + 1
-
-kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
-        align = "c", digits = 0,
-        # caption = paste("Dose 3 Schedule"),
-      col.names = col_names_table) %>%
-    kable_styling(bootstrap_options = "hover", position = "center",
-                  font_size = 11, full_width = FALSE) %>%
-    column_spec(column = c(1,
-                           ncol(dose3_sch_next_2wks_cast)),
-                border_right = "thin solid lightgray") %>%
-    add_header_above(c(" " = 1,
-                       "Arrived Visits" = arr_cols,
-                       "Scheduled Visits" = sch_cols),
-                     background = c("",
-                                    sinai_colors[1],
-                                    sinai_colors[3]),
-                     line = FALSE,
-                     color = "white") %>%
-    row_spec(row = nrow(dose3_sch_next_2wks_cast),
-             bold = TRUE,
-             italic = TRUE,
-             hline_after = TRUE) %>%
-    scroll_box(width = "800px")
+# # Create dose 3 schedule summary for ambulatory team
+# dose3_sch_next_2wks <- sched_data %>%
+#   filter(Status2 %in% c("Arr", "Sch") &
+#            ApptDate %in% dates_2wks &
+#            Dose == 3) %>%
+#   group_by(ApptDate, Site, Status2) %>%
+#   summarize(Count = n())
+# 
+# dose3_sch_next_2wks <- left_join(
+#   site_dates_templ,
+#   dose3_sch_next_2wks, 
+#   by = c("Site" = "Site",
+#          "Date" = "ApptDate")
+# )
+# 
+# dose3_sch_next_2wks <- dose3_sch_next_2wks %>%
+#   mutate(Count = replace_na(Count, 0),
+#          Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
+#                           ifelse(is.na(Status2) & Date >= today, "Sch",
+#                                  Status2)),
+#          Date = format(Date, "%m/%d/%y"))
+# 
+# dose3_sch_next_2wks_cast <- pivot_wider(dose3_sch_next_2wks,
+#                                         names_from = c(Status2, Date),
+#                                         names_sep = "_",
+#                                         names_sort = FALSE,
+#                                         values_from = Count)
+# 
+# dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
+#   adorn_totals(where = "row",
+#                na.rm = TRUE,
+#                name = "MSHS") %>%
+#   adorn_totals(where = "col",
+#                na.rm = TRUE,
+#                name = "Total")
+# 
+# dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
+#   mutate_all(~replace_na(., 0))
+# 
+# col_names_df <- colnames(dose3_sch_next_2wks_cast)
+# col_names_table <- str_replace(col_names_df, regex("^[a-z]*_", ignore_case = TRUE), "")
+# arr_cols <- max(which(str_detect(col_names_df, "Arr"))) - min(which(str_detect(col_names_df, "Arr"))) + 1
+# sch_cols <- max(which(str_detect(col_names_df, "Sch"))) - min(which(str_detect(col_names_df, "Sch"))) + 1
+# 
+# kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
+#         align = "c", digits = 0,
+#         # caption = paste("Dose 3 Schedule"),
+#       col.names = col_names_table) %>%
+#   kable_styling(bootstrap_options = "hover",
+#                 position = "center",
+#                 font_size = 11,
+#                 full_width = FALSE) %>%
+#   column_spec(column = c(1,
+#                          ncol(dose3_sch_next_2wks_cast) - 1,
+#                          ncol(dose3_sch_next_2wks_cast)),
+#               border_right = "thin solid lightgray") %>%
+#   add_header_above(c(" " = 1,
+#                      "Arrived Visits" = arr_cols,
+#                      "Scheduled Visits" = sch_cols,
+#                      " " = 1),
+#                    background = c("",
+#                                   sinai_colors[1],
+#                                   sinai_colors[3],
+#                                   ""),
+#                    line = FALSE,
+#                    color = "white") %>%
+#   row_spec(row = nrow(dose3_sch_next_2wks_cast),
+#            bold = TRUE,
+#            italic = TRUE,
+#            hline_after = TRUE) %>%
+#   column_spec(column = ncol(dose3_sch_next_2wks_cast),
+#            bold = TRUE,
+#            italic = TRUE) %>%
+#   scroll_box(width = "800px")
 
@@
 
+## Vaccine Schedules by Dose
+
+### All Doses
+```{r Call custom function for schedule for all doses}
+sched_data_kable(dose = "AllDoses")
+
+```
+
+<br>
+
+### Dose 1
+```{r Call custom function for schedule for dose 1 appointments}
+sched_data_kable(dose = "Dose1")
+
+```
+
+<br>
+
+### Dose 2
+```{r Call custom function for schedule for dose 2 appointments}
+sched_data_kable(dose = "Dose2")
+
+```
+
+<br>
+
+### Dose 3
+```{r Call custom function for schedule for dose 3 appointments}
+sched_data_kable(dose = "Dose3")
+
+```
+<br>
+<br>
+
+## Appts Made Yesterday & Today
+
+### Dose 3 Appts: All Statuses
 ```{r Create kable for scheduled appointments over next 14 days}
 
-asis_output(paste0("<h4>Based on Epic schedule data as of ",
-                   format(file.info(sched_data_file)$ctime,
-                          "%m/%d/%y %I:%M %p"),
-                   "</h4>"))
-
-asis_output("<br>")
-asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>")
-kable_dose3_sch
-
-asis_output("<br>")
-asis_output("<br>")
-asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ",
-                   made_dates_str,
-                   "</h4>"))
+# asis_output(paste0("<h4>Based on Epic schedule data as of ",
+#                    format(file.info(sched_data_file)$ctime,
+#                           "%m/%d/%y %I:%M %p"),
+#                    "</h4>"))
+# 
+# asis_output("<br>")
+# asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>")
+# kable_dose3_sch
+# 
+# asis_output("<br>")
+# asis_output("<br>")
+# asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ",
+#                    made_dates_str,
+#                    "</h4>"))
 
@@
 asis_output("<br>")
+
+```
+
+### Dose 3 Appts: Arrived & Scheduled Only
+```{r Test}
 

### 2021-10-12 Render_Amb_Sched_Tracking.R

@@ -14,6 +14,6 @@ if ("Presidents" %in% list.files("J://")) {
 
 rmarkdown::render(input = "Amb_Sched_Tracking.Rmd",
                   output_file = paste0(user_directory,
-                                       "/Dose3 Amb Sched Tracking",
-                                       "/Dose3 Schedule Tracking ",
+                                       "/Amb Sched Tracking",
+                                       "/Vaccine Schedule Tracking ",
                                        format(Sys.time(), "%Y-%m-%d %I%M%p")))

### 2021-10-13 Weekly_Arrivals_Future_Sched_Tracking.Rmd
Update analysis reference file and incorporate dose 3 for MSSN for weekly dashboard.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-08-16.xlsx"),
+                                   "Automation Ref 2021-09-29.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-08-16.xlsx"),
+                                  "Automation Ref 2021-09-29.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
 
-colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
+colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "Dose3", "AllDoses")
 ```
@@
          VaccWeek = as.numeric(
-           floor((ApptDate - vacc_start_first_sun) / 7 +1)),
-         Dose3 = NA) %>%
+           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
   pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),

### 2021-10-27 Amb_Sched_Tracking.Rmd
Add logic to account for future appointments erroneously marked as arrived.

@@
                           # Correct any appts erroneously marked as arrived early
-                          ifelse(report_date < today &
+                          ifelse((report_date < today &
                                     ApptDate >= today &
-                                   Status == "Arr", "Sch",
+                                    Status == "Arr") |
+                                   (ApptDate > today & Status == "Arr"), "Sch",
                                  Status)),

### 2021-11-05 Amb_Sched_Tracking.Rmd
Update ambulatory schedule tracking dashboard to include pediatrics vaccine schedules.

--- 2021-09-30 Amb_Sched_Tracking.Rmd
@@
 ---
-output: html_document
+title: MSHS COVID-19 Vaccine Schedule Tracking
+output:
+  html_document:
+    toc: true
+    toc_depth: 3
+    toc_float:
+      collapsed: true
 ---
 
-### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking
+<!-- ### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking -->
 
@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-09-29.xlsx"),
+                                   "Automation Ref 2021-11-03.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-09-29.xlsx"),
+                                  "Automation Ref 2021-11-03.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
 
+# Vaccine types
+vax_types <- c("Adult", "Peds")
+
 report_run_time <- ifelse(hour(Sys.time()) > 14, "PM", "AM")
@@
                      check.names = FALSE)
+
+# raw_data[, ncol(raw_data)] <- NULL
 
@@
                           # Correct any appts erroneously marked as arrived early
-                          ifelse(report_date < today &
+                          ifelse((report_date < today &
                                     ApptDate >= today &
-                                   Status == "Arr", "Sch",
+                                    Status == "Arr") |
+                                   (ApptDate > today & Status == "Arr"), "Sch",
                                  Status)),
+         # Determine whether the vaccine is an adult or pediatric dose
+         VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
+                            `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
+                                                       "DOSE 2 PEDIATRIC [1324685]"),
+                          "Peds", "Adult"),
          # Determine whether appointment is for dose 1, 2, or 3 based on
@@
 
+# Create dataframe of doses
+all_doses <- seq(from = 1, to = 3, by = 1)
+
+doses_templ <- data.frame(
+  "Dose" = rep(all_doses,
+               length(all_sites)))
+
+doses_templ <- doses_templ %>%
+  arrange(Dose)
+
+# Create a dataframe of vaccine types
+vax_type_templ <- data.frame(
+  "VaxType" = rep(vax_types,
+                  length(all_sites)),
+  stringsAsFactors = FALSE
+)
+
+vax_type_templ <- vax_type_templ %>%
+  arrange(VaxType)
+
 # Combine site and dates
@@
 
+# Combine site and doses
+site_doses_templ <- data.frame(
+  "Site" = rep(all_sites, length(all_doses)),
+  "Dose" = doses_templ,
+  stringsAsFactors = FALSE)
+
+# Combine site and vaccine types
+site_vax_templ <- data.frame(
+  "Site" = rep(all_sites, length(vax_types)),
+  "VaxType" = vax_type_templ,
+  stringsAsFactors = FALSE
+)
+
+site_vax_templ <- site_vax_templ %>%
+  filter(VaxType %in% c("Adult") |
+           (VaxType %in% c("Peds") & Site %in% c("MSH", "MSBI")))
+
+site_date_dose_templ <- left_join(site_dates_templ,
+                                  site_doses_templ,
+                                  by = c("Site" = "Site"))
+
+site_vax_dose_templ <- left_join(site_vax_templ,
+                                 site_doses_templ,
+                                 by = c("Site" = "Site"))
+
+site_vax_dose_templ <- site_vax_dose_templ %>%
+  filter(!(VaxType %in% c("Peds") & Dose %in% c(3)))
+
+# Combine site, dose, date, and vaccine type
+site_date_vax_dose_templ <- left_join(site_date_dose_templ,
+                                      site_vax_dose_templ,
+                                      by = c("Site" = "Site",
+                                             "Dose" = "Dose"))
+
 ```
 
-```{r Subset dose 3 schedule data}
-# Create dose 3 schedule summary for ambulatory team
-dose3_sch_next_2wks <- sched_data %>%
+```{r Summarize schedule data by day and dose}
+sched_summary <- sched_data %>%
   filter(Status2 %in% c("Arr", "Sch") &
-           ApptDate %in% dates_2wks &
-           Dose == 3) %>%
-  group_by(ApptDate, Site, Status2) %>%
-  summarize(Count = n())
+           ApptDate %in% dates_2wks) %>%
+  group_by(Dose, Site, VaxType, Status2, ApptDate) %>%
+  summarize(Count = n(), .groups = "keep")
 
-dose3_sch_next_2wks <- left_join(
-  site_dates_templ,
-  dose3_sch_next_2wks, 
+sched_summary <- left_join(site_date_vax_dose_templ,
+                           sched_summary,
                            by = c("Site" = "Site",
-         "Date" = "ApptDate")
-)
+                                  "Date" = "ApptDate",
+                                  "VaxType" = "VaxType",
+                                  "Dose" = "Dose"))
 
-dose3_sch_next_2wks <- dose3_sch_next_2wks %>%
+sched_summary <- sched_summary %>%
   mutate(Count = replace_na(Count, 0),
@@
                           ifelse(is.na(Status2) & Date >= today, "Sch",
-                                 Status2)),
-         Date = format(Date, "%m/%d/%y"))
+                                 Status2))) %>%
+  arrange(VaxType, Site, Date, Dose, Status2) %>%
+  mutate(
+    # Date = format(Date, "%m/%d/%y"),
+         Dose = paste0("Dose", Dose))
 
-dose3_sch_next_2wks_cast <- pivot_wider(dose3_sch_next_2wks,
-                                        names_from = c(Status2, Date),
+sched_summary_table <- sched_summary %>%
+  pivot_wider(names_from = c(Status2, VaxType, Dose, Date),
               names_sep = "_",
               names_sort = FALSE,
-                                        values_from = Count)
-
-dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
+              values_from = Count) %>%
   adorn_totals(where = "row",
@@
                name = "MSHS") %>%
+  pivot_longer(cols = contains("_"),
+               names_to = c("Status2", "VaxType", "Dose", "Date"),
+               names_sep = "_",
+               values_to = "Count") %>%
+  # arrange(Site, Date, Status2) %>%
+  pivot_wider(names_from = c(Site, Status2, VaxType, Date),
+              names_sep = "_",
+              names_sort = FALSE,
+              values_from = Count) %>%
+  adorn_totals(where = "row",
+               na.rm = TRUE,
+               name = "AllDoses") %>%
+  pivot_longer(cols = contains("_"),
+               names_to = c("Site", "Status2", "VaxType", "Date"),
+               names_sep = "_",
+               values_to = "Count") %>%
+  filter(VaxType %in% c("Adult") |
+           (VaxType %in% c("Peds") & Site %in% c("MSH", "MSBI", "MSHS"))) %>%
+  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
+         Dose = factor(Dose, levels = c("Dose1", "Dose2", "Dose3", "AllDoses")),
+         Count = replace_na(Count, 0),
+         Date = as.Date(Date, format = "%Y-%m-%d")) %>%
+  arrange(VaxType, Site, Date, Status2) %>%
+  mutate(Date = format(Date, "%m/%d/%y")) %>%
+  pivot_wider(names_from = c(Status2, Date),
+              names_sep = "_",
+              names_sort = FALSE,
+              values_from = Count) %>%
   adorn_totals(where = "col",
@@
 
-dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
-  mutate_all(~replace_na(., 0))
+```
 
-col_names_df <- colnames(dose3_sch_next_2wks_cast)
-col_names_table <- str_replace(col_names_df, regex("^[a-z]*_", ignore_case = TRUE), "")
-arr_cols <- max(which(str_detect(col_names_df, "Arr"))) - min(which(str_detect(col_names_df, "Arr"))) + 1
-sch_cols <- max(which(str_detect(col_names_df, "Sch"))) - min(which(str_detect(col_names_df, "Sch"))) + 1
+```{r Create a kable for each dose}
 
-kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
-        align = "c", digits = 0,
-        # caption = paste("Dose 3 Schedule"),
-      col.names = col_names_table) %>%
+sched_data_kable <- function(vax_type, dose) {
+  kable_vax_type <- vax_type
+
+  kable_dose <- dose
+
+  kable_dose_title <- ifelse(dose == "AllDoses", "All Doses",
+                             str_replace(kable_dose, "Dose", "Dose "))
+
+  sched_kable_df <- sched_summary_table %>%
+  filter(VaxType == kable_vax_type,
+           Dose == kable_dose) %>%
+  mutate(VaxType = NULL,
+         Dose = NULL)
+
+  sched_summary_cols <- colnames(sched_kable_df)
+  sched_summary_table_names <- str_replace(sched_summary_cols,
+                                           regex("^[a-z]*_",
+                                                 ignore_case = TRUE),
+                                           "")
+
+  arr_cols <- max(which(str_detect(sched_summary_cols, "Arr"))) -
+    min(which(str_detect(sched_summary_cols, "Arr"))) + 1
+
+  sch_cols <- max(which(str_detect(sched_summary_cols, "Sch"))) -
+    min(which(str_detect(sched_summary_cols, "Sch"))) + 1
+
+  sched_kable <- kable(sched_kable_df,
+                       format = "html",
+                       escape = FALSE,
+                       align = "c",
+                       digits = 0,
+                       caption = paste(kable_vax_type, kable_dose_title, "Schedule"),
+                       col.names = sched_summary_table_names) %>%
     kable_styling(bootstrap_options = "hover",
@@
     column_spec(column = c(1,
-                         ncol(dose3_sch_next_2wks_cast) - 1,
-                         ncol(dose3_sch_next_2wks_cast)),
+                           ncol(sched_kable_df) - 1,
+                           ncol(sched_kable_df)),
                 border_right = "thin solid lightgray") %>%
@@
                      color = "white") %>%
-  row_spec(row = nrow(dose3_sch_next_2wks_cast),
+    row_spec(row = nrow(sched_kable_df),
              bold = TRUE,
@@
              hline_after = TRUE) %>%
-  column_spec(column = ncol(dose3_sch_next_2wks_cast),
+    column_spec(column = ncol(sched_kable_df),
                 bold = TRUE,
@@
     scroll_box(width = "800px")
+
+  return(sched_kable)
+}
 
@@
 
-```{r Create kable for scheduled appointments over next 14 days}
+## Adult Vaccine Schedules by Dose
 
-asis_output(paste0("<h4>Based on Epic schedule data as of ",
-                   format(file.info(sched_data_file)$ctime,
-                          "%m/%d/%y %I:%M %p"),
-                   "</h4>"))
-
-asis_output("<br>")
-asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>")
-kable_dose3_sch
-
-asis_output("<br>")
-asis_output("<br>")
-asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ",
-                   made_dates_str,
-                   "</h4>"))
-
-kable_dose3_made_date_all_status
-
-asis_output("<br>")
-
-kable_dose3_made_date_arr_sch
-
-asis_output("<h6><i>End of report.</i></h6>")
+### All Doses
+```{r Call custom function for schedule for all adult doses}
+sched_data_kable(vax_type = "Adult", dose = "AllDoses")
 
 ```
+
+<br>
+
+### Dose 1
+```{r Call custom function for schedule for adult dose 1 appointments}
+sched_data_kable(vax_type = "Adult", dose = "Dose1")
+
+```
+
+<br>
+
+### Dose 2
+```{r Call custom function for schedule for adult dose 2 appointments}
+sched_data_kable(vax_type = "Adult", dose = "Dose2")
+
+```
+
+<br>
+
+### Dose 3
+```{r Call custom function for schedule for adult dose 3 appointments}
+sched_data_kable(vax_type = "Adult", dose = "Dose3")
+
+```
+<br>
+<br>
+
+## Peds Vaccine Schedules by Dose
+
+<!-- ### All Doses -->
+<!-- ```{r Call custom function for schedule for all peds doses} -->
+<!-- sched_data_kable(vax_type = "Peds", dose = "AllDoses") -->
+
+<!-- ``` -->
+
+<br>
+
+### Dose 1
+```{r Call custom function for schedule for peds dose 1 appointments}
+sched_data_kable(vax_type = "Peds", dose = "Dose1")
+
+```
+
+<!-- <br> -->
+
+<!-- ### Dose 2 -->
+<!-- ```{r Call custom function for schedule for peds dose 2 appointments} -->
+<!-- sched_data_kable(vax_type = "Peds", dose = "Dose2") -->
+
+<!-- ``` -->
+
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- ## Adult Appts Made Yesterday & Today -->
+
+<!-- ### Dose 3 Appts: All Statuses (Made on `r made_dates_str`) -->
+<!-- ```{r Create kable for scheduled appointments over next 14 days} -->
+
+<!-- # asis_output(paste0("<h4>Based on Epic schedule data as of ", -->
+<!-- #                    format(file.info(sched_data_file)$ctime, -->
+<!-- #                           "%m/%d/%y %I:%M %p"), -->
+<!-- #                    "</h4>")) -->
+<!-- #  -->
+<!-- # asis_output("<br>") -->
+<!-- # asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>") -->
+<!-- # kable_dose3_sch -->
+<!-- #  -->
+<!-- # asis_output("<br>") -->
+<!-- # asis_output("<br>") -->
+<!-- # asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ", -->
+<!-- #                    made_dates_str, -->
+<!-- #                    "</h4>")) -->
+
+<!-- kable_dose3_made_date_all_status -->
+
+<!-- asis_output("<br>") -->
+
+<!-- ``` -->
+
+<!-- ### Dose 3 Appts: Arrived & Scheduled Only (Made on `r made_dates_str`) -->
+<!-- ```{r Test} -->
+
+<!-- kable_dose3_made_date_arr_sch -->
+
+<!-- asis_output("<h6><i>End of report.</i></h6>") -->
+
+<!-- ``` -->
+
+<h6><i>End of report.</i></h6>

### 2021-11-05 Daily Vaccine Reporting and Export.R

@@ -953,9 +953,9 @@ write_xlsx(export_list, path = paste0(user_directory,
                                       format(Sys.time(), "%m%d%y %H%M"),
                                       ".xlsx"))
 
-rmarkdown::render(input = "Empl_Arrival_Tracking.Rmd",
-                  output_file = paste0(user_directory,
-                                       "/Daily Dashboard Drafts",
-                                       "/Employee Arrival Tracking Tool ",
-                                       format(Sys.Date(), "%Y-%m-%d")))
+# rmarkdown::render(input = "Empl_Arrival_Tracking.Rmd",
+#                   output_file = paste0(user_directory,
+#                                        "/Daily Dashboard Drafts",
+#                                        "/Employee Arrival Tracking Tool ",
+#                                        format(Sys.Date(), "%Y-%m-%d")))
 

### 2021-11-05 Render_Amb_Sched_Tracking.R

@@ -15,5 +15,5 @@ if ("Presidents" %in% list.files("J://")) {
 rmarkdown::render(input = "Amb_Sched_Tracking.Rmd",
                   output_file = paste0(user_directory,
                                        "/Amb Sched Tracking",
-                                       "/Vaccine Schedule Tracking ",
+                                       "/Vaccine Schedule Tracking Test ",
                                        format(Sys.time(), "%Y-%m-%d %I%M%p")))

### 2021-11-05 Ad Hoc Vaccine Reporting and Export.R
Update ad hoc vaccine reporting and export code to include peds vaccine similar to the daily vaccine reporting and export code.

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-09-29.xlsx"),
+                                   "Automation Ref 2021-11-03.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-09-29.xlsx"),
+                                  "Automation Ref 2021-11-03.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -106,6 +106,9 @@ pod_type <- c("Employee", "Patient", "All")
 
 # Vaccine manufacturers
 mfg <- c("Pfizer", "Moderna", "J&J")
+
+# Vaccine types
+vax_types <- c("Adult", "Peds")
 
 # NY zip codes
 ny_zips <- search_state("NY")
@@ -222,11 +225,17 @@ sched_to_date <- sched_to_date %>%
                      # Correct any appts erroneously marked as arrived early
                      ifelse(ApptDate >= today & Status == "Arr", "Sch",
                             Status)),
-    # Determine manufacturer based on immunization field
+    # Determine whether the vaccine is an adult or pediatric dose
+    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
+                       `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
+                                                  "DOSE 2 PEDIATRIC [1324685]"),
+                     "Peds", "Adult"),
+    # Determine manufacturer based on immunization field and vaccine type fields
     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
       ifelse(Status2 != "Arr", NA,
-             # Any blank immunizations assumed to be Pfizer
-             ifelse(is.na(Immunizations), "Pfizer",
+             # Any blank immunizations and any peds assumed to be Pfizer
+             ifelse(is.na(Immunizations) |
+                      VaxType %in% c("Peds"), "Pfizer",
                     # Any immunizations with Moderna in text classified as Moderna
[…]

### 2021-11-05 Daily Vaccine Reporting and Export.R

@@ -425,6 +425,10 @@ site_dose_mfg_date_templ <- left_join(site_dates_templ,
                                       site_dose_mfg_templ,
                                       by = c("Site" = "Site"))
 
+# Manually remove J&J dose 2 and 3 from template
+site_dose_mfg_date_templ <- site_dose_mfg_date_templ %>%
+  filter(!(Mfg == "J&J" & Dose > 1))
+
 # Combine site, vaccine type, dose, manufacturer, and dates
 site_vax_dose_mfg_date_templ <- left_join(site_vax_templ,
                                           site_dose_mfg_date_templ,
@@ -443,10 +447,6 @@ site_vax_dose_date_templ <- left_join(site_vax_templ,
 # Remove booster shots from peds vaccine type
 site_vax_dose_date_templ <- site_vax_dose_date_templ %>%
   filter(!(VaxType == "Peds" & Dose == 3))
-
-# Manually remove J&J dose 2 and 3 from template
-site_dose_mfg_date_templ <- site_dose_mfg_date_templ %>%
-  filter(!(Mfg == "J&J" & Dose > 1))
 
 # Merge template dataframe with schedule breakdown data
 sched_breakdown <- left_join(site_vax_dose_date_templ,

### 2021-11-18 Evening-Huddle-Dashboard.R
Rename ambulatory schedule tracking dashboard output.

@@ -13,6 +13,6 @@ if ("Presidents" %in% list.files("J://")) {
 rmarkdown::render("Adult_Peds_Weekly_Arrivals_Sched_Tracking.Rmd",
                   output_file = paste0(user_directory,
                                        "/Daily PM Huddle Output/",
-                                       "MSHS Vaccine Summary Test ",
+                                       "MSHS Vaccine Summary ",
                                        format(Sys.Date(), "%m-%d-%y")))
 

### 2021-11-18 Adult_Peds_Weekly_Arrivals_Sched_Tracking.Rmd
Create new script for daily ambulatory schedule tracking that includes peds vaccinations.

---
title: "MSHS COVID-19 Vaccinations"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Install and load packages}
# Code for updating data analysis for afternoon huddle

#Install and load necessary packages --------------------
#install.packages("readraw_dfl")
#install.packages("writeraw_dfl")
#install.packages("ggplot2")
#install.packages("lubridate")
#install.packages("dplyr")
#install.packages("reshape2")
#install.packages("svDialogs")
#install.packages("stringr")
#install.packages("formattable")
#install.packages("ggpubr")
#install.packages("zipcodeR")
#install.packages("tidyr")
#install.packages("janitor")
#install.packages("knitr")
#install.packages("rmarkdown")
#install.packages("kableExtra")

#Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(janitor)
library(knitr)
library(rmarkdown)
library(kableExtra)
```

```{r Import reference data, set variables, and import raw data, include = FALSE}

# Set working directory and select raw data ----------------------------
rm(list = ls())

# Determine path for working directory
if ("Presidents" %in% list.files("J://")) {
  user_directory <- paste0("J:/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
} else {
  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
}

# Set path for file selection
user_path <- paste0(user_directory, "\\*.*")

# Determine whether or not to update an existing repo
initial_run <- FALSE
update_repo <- TRUE

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-11-03.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-11-03.xlsx"),
                           sheet = "Pod Mappings Simple")

# Store today's date
today <- Sys.Date()
yesterday <- today - 1

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network LI",
               "MSSN")

peds_sites <- c("MSH", "MSBI")

# Pod type order
pod_type <- c("Employee", "Patient", "All")

# Vaccine manufacturers
mfg <- c("Pfizer", "Moderna", "J&J")

# Vaccine types
vax_types <- c("Adult", "Peds")

# NY zip codes
ny_zips <- search_state("NY")

# Create dataframe with start dates for adult and peds vaccination
vacc_start_df <- data.frame("VaxType" = c("Adult", "Peds"),
                            "StartDate" = c(as.Date("12/15/20",
                                                    format = "%m/%d/%y"),
                                            as.Date("11/04/21",
                                                    format = "%m/%d/%y")))

vacc_start_df <- vacc_start_df %>%
  mutate(
    # Determine the Sunday of the first week of vaccination
    FirstSun = StartDate - (wday(StartDate) - 1),
    # Determine this week number
    ThisWeek = as.numeric(floor((today - FirstSun) / 7) + 1))

# Create dataframe with dates and weeks since vaccines started
all_dates <- data.frame("Date" = seq.Date(min(vacc_start_df$StartDate),
                                          today + 7,
                                          by = 1
                                          )
                        )

all_dates <- all_dates %>%
  mutate(
    # Determine vaccine week for adult vaccinations
    Adult_VaccWeek = as.numeric(
      floor((Date -
               vacc_start_df$FirstSun[
                 which(vacc_start_df$VaxType == "Adult")]) / 7) + 1),
    # Determine vaccine week for pediatric vaccinations
    Peds_VaccWeek = ifelse(
      as.numeric(
        floor((Date -
                 vacc_start_df$FirstSun[
                 which(vacc_start_df$VaxType == "Peds")]) / 7) + 1) < 1, NA,
      as.numeric(
      floor((Date -
               vacc_start_df$FirstSun[
                 which(vacc_start_df$VaxType == "Peds")]) / 7) + 1)
    )
  ) %>%
  pivot_longer(cols = contains("_VaccWeek"),
               names_to = "VaxType",
               values_to = "VaccWeek") %>%
  mutate(VaxType = str_remove(VaxType, "_VaccWeek"),
         WeekStart = Date - (wday(Date) - 1),
         WeekEnd = Date + (7 - wday(Date)),
         WeekDates = paste0(
           format(WeekStart, "%m/%d/%y"),
           "-",
           format(WeekEnd, "%m/%d/%y")
           ),
         WeekStart = NULL,
         WeekEnd = NULL
         ) %>%
  filter(!is.na(VaccWeek)) %>%
  arrange(VaxType, Date)

# Create variable with doses
doses <- c("Dose1", "Dose2", "Dose3", "AllDoses")

# Specify Sinai colors for table
sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2")

# Import raw data from Epic
if (update_repo) {
  sched_repo <- readRDS(
    choose.files(default = paste0(user_directory,
                                  "/R_Sched_AM_Repo/*.*"),
                 caption = "Select this morning's schedule repository"))

  raw_df <- read.csv(choose.files(
    default =
      paste0(user_directory, "/Epic PM Huddle Sched All Status/*.*"),
    caption = "Select this afternoon's Epic schedule"),
    stringsAsFactors = FALSE,
    check.names = FALSE)

  new_sched <- raw_df

  # Remove test patient
  new_sched <- new_sched[new_sched$Patient != "Patient, Test", ]

  # Update data classes from .csv schedule import to match repository structure
  new_sched <- new_sched %>%
    mutate(DOB = as.Date(DOB, format = "%m/%d/%Y"),
           `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
           Date = as.Date(Date, format = "%m/%d/%Y"),
           `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
                                    tz = "", format = "%Y-%m-%d %H:%M %p"),
           `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)))

  # Determine dates in new report
  current_dates <- sort(unique(new_sched$Date))

  # Update schedule repository by removing duplicate dates and adding data
  # from new report
  sched_repo <- sched_repo %>%
    filter(!(Date >= current_dates[1]))
  sched_repo <- rbind(sched_repo, new_sched)

  # # Save schedule
  # saveRDS(sched_repo, paste0(user_directory, "/R_Sched_PM_Huddle_Repo/",
  #                            "Epic Sched 340PM ",
  #                            format(min(sched_repo$Date), "%m%d%y"), " to ",
  #                            format(max(sched_repo$Date), "%m%d%y"),
  #                            " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

} else {

  sched_repo <- readRDS(
    choose.files(default = paste0(user_directory,
                                  "/R_Sched_AM_Repo/*.*"),
                 caption = "Select this morning's schedule repository"))

}

# Import MSSN data from Tableau
mssn_admin <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select latest MSSN Tableau Administration Data"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

mssn_admin <- mssn_admin[1:nrow(mssn_admin) - 1, ]

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "Dose3", "AllDoses")

mssn_admin <- mssn_admin %>%
  mutate(VaxType = "Adult")
```

```{r Format Epic schedule data}
# Format and analyze Epic schedule to date for dashboards ---------------------
epic_sched_to_date <- sched_repo

epic_sched_to_date <- epic_sched_to_date %>%
  mutate(
    # Determine whether appointment is for dose 1 or dose 2
    Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                  ifelse(str_detect(Type, "DOSE 2"), 2,
                         ifelse(str_detect(Type, "DOSE 3"), 3, NA))),
    # Determine appointment date, year, month, etc.
    ApptDate = date(Date),
    ApptYear = year(Date),
    ApptMonth = month(Date),
    ApptDay = day(Date),
    ApptWeek = week(Date),
    # Clean up department if it is duplicated in that column
    Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
    # Group arrived, completed, and checked out appts as arrived
    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                    "Arr", `Appt Status`),
    # Update appointment status: classify any appts from prior days that are
    # still in scheduled as No Shows
    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", Status),
    # Determine whether the vaccine is an adult or pediatric dose
    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
                       `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
                                                  "DOSE 2 PEDIATRIC [1324685]"),
                     "Peds", "Adult"),
    # Determine manufacturer based on immunization and vaccine type fields
    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
      ifelse(Status2 != "Arr", NA,
             # Assume any visits without immunization record are Pfizer
             ifelse(is.na(Immunizations) |
                      VaxType %in% c("Peds"), "Pfizer",
                    # Any immunizations with Moderna in text classified as
                    # Moderna, otherwise Pfizer
                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                           # Any immunizations with Johnson and Johnson are
                           # classified as J&J
                           ifelse(str_detect(Department, "VISITING DOCS") |
                                    str_detect(Immunizations,
                                               "Johnson and Johnson"),
                                  "J&J", "Pfizer")))),
    # Determine week number of year
    WeekNum = format(ApptDate, "%U"),
    # Determine appointment day of week
    DOW = weekdays(ApptDate),
    # Determine if patient's zip code is in NYS
    NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode
  )

# Crosswalk sites
epic_sched_to_date <- left_join(epic_sched_to_date, site_mappings,
                                by = c("Department" = "Department"))

# Manually update discrepancies in site/mfg/dose
epic_sched_to_date <- epic_sched_to_date %>%
  mutate(# Roll up any Moderna administered at MSB for YWCA to MSH
    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
    # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
    Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c(2), 1, Dose))

# Crosswalk pod type (employee vs patient)
epic_sched_to_date <- left_join(epic_sched_to_date,
                                pod_mappings[, c("Provider", "Pod Type")],
                                by = c("Provider/Resource" = "Provider"))

# Assume any pods without a mapping are patient pods
epic_sched_to_date[is.na(epic_sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"

# Determine vaccine week based on appointment date
epic_sched_to_date <- left_join(epic_sched_to_date,
                                all_dates,
                                by = c("ApptDate" = "Date",
                                       "VaxType" = "VaxType"))

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           VaxType,
           Dose,
           VaccWeek,
           WeekDates,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              names_prefix = "Dose",
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, Dose3, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0)) %>%
  filter(!(VaxType %in% c("Peds") & Dose %in% c("Dose3"))) %>%
  ungroup()

```

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y")) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0))

mssn_admin_to_date <- left_join(mssn_admin_to_date,
                                all_dates,
                                by = c("ApptDate" = "Date",
                                       "VaxType" = "VaxType"))

mssn_admin_to_date <- mssn_admin_to_date[, colnames(epic_sched_summary)]
```

```{r Combine data across all sites}
# Bind MSSN data with Epic sites data
daily_sched_summary <- rbind(epic_sched_summary, mssn_admin_to_date)

```

```{r Create and combine tables with vaccine administration and schedule data}
# Create a template of all sites, vaccine dates, and doses ---------
# Repeat dose type
doses_templ <- data.frame(
  "Dose" = rep(doses,
               length(all_sites)))

doses_templ <- doses_templ %>%
  arrange(Dose)

# Repeat vaccine types
vax_templ <- data.frame(
  "VaxType" = rep(vax_types,
                  length(all_sites)
                  )
)

vax_templ <- vax_templ %>%
  arrange(VaxType)

# Create template of sites, doses, and vaccine types
site_dose_templ <- data.frame(
  "Site" = rep(all_sites, length(doses)),
  "Dose" = doses_templ
)

site_vax_templ <- data.frame(
  "Site" = rep(all_sites, length(vax_types)),
  "VaxType" = vax_templ
)

# Manually update site-vaccine type template based on sites that are administering peds vaccine
site_vax_templ <- site_vax_templ %>%
  filter(VaxType %in% c("Adult") |
           (VaxType %in% c("Peds") & Site %in% peds_sites))

# Combine site-dose and site-vaccine type templates
site_vax_dose_templ <- left_join(site_dose_templ,
                                 site_vax_templ,
                                 by = c("Site" = "Site"))

# Remove peds dose 3
site_vax_dose_templ <- site_vax_dose_templ %>%
  filter(!(VaxType %in% c("Peds") & Dose %in% c("Dose3")))

```

```{r Subset data and create custom function for visualizing all arrived appointments to date}
vacc_weeks <- all_dates %>%
  select(VaxType, VaccWeek, WeekDates) %>%
  distinct()

site_vax_dose_week_templ <- left_join(site_vax_dose_templ,
                                      vacc_weeks,
                                      by = c("VaxType" = "VaxType")
                                      )

# Summarize arrived visits to date
arr_visits <- daily_sched_summary %>%
  filter(Status2 %in% c("Arr")) %>%
  group_by(Site,
           VaxType,
           Dose,
           VaccWeek,
           WeekDates) %>%
  summarize(Count = sum(Count, na.rm = TRUE))

# Determine the week of the last arrived visits for adults and peds vaccinations
last_arr_visits <- arr_visits %>%
  group_by(VaxType) %>%
  summarize(LatestWeek = max(VaccWeek))

# Modify the template dataframe to only include weeks with already arrived patients
arr_site_vax_dose_week_templ <- site_vax_dose_week_templ %>%
  filter((VaxType %in% c("Adult") &
            VaccWeek <=
            last_arr_visits$LatestWeek[last_arr_visits$VaxType %in% c("Adult")]
          ) |
           (VaxType %in% c("Peds") &
              VaccWeek <=
              last_arr_visits$LatestWeek[last_arr_visits$VaxType %in% c("Peds")]
            )         
         )

# Join template with all prior weeks, vaccine types, and doses with arrived visits dataframe to ensure no weeks are missing
arr_visits <- left_join(arr_site_vax_dose_week_templ %>%
                          filter(VaccWeek <= max(arr_visits$VaccWeek)),
                        arr_visits,
                        by = c("Site" = "Site",
                               "VaxType" = "VaxType",
                               "VaccWeek" = "VaccWeek",
                               "WeekDates" = "WeekDates",
                               "Dose" = "Dose"))

arr_visits <- arr_visits %>%
  mutate(Count = replace_na(Count, 0),
         WkAndDate = paste0("Wk ", VaccWeek, ": ", WeekDates))

arr_visits_kable <- function(vax_type, dose) {
  if (!(vax_type %in% c("Adult", "Peds") |
         dose %in% c(1, 2, 3, "All"))) {
    msg <- "Invalid argument"
    stop(msg)
  } else {

    arr_visits_totals <<- arr_visits %>%
      filter(VaxType %in% vax_type) %>%
      mutate(VaxType = NULL) %>%
      arrange(Dose,
              VaccWeek,
              Site) %>%
      mutate(VaccWeek = NULL,
             WeekDates = NULL) %>%
      pivot_wider(names_from = c(Dose, WkAndDate),
                  names_sep = "__",
                  values_from = Count) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "MSHS") %>%
      pivot_longer(cols = contains("__", ignore.case = TRUE),
                   names_to = c("Dose", "Week"),
                   names_sep = "__",
                   values_to = "Count") %>%
      pivot_wider(names_from = c(Site, Dose),
                  names_sep = "__",
                  values_from = Count) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "TotalDosesAdmin") %>%
      pivot_longer(cols = contains("__", ignore.case = TRUE),
                   names_to = c("Site", "Dose"),
                   names_sep = "__",
                   values_to = "Count") %>%
      relocate(Site) %>%
      relocate(Week, .after = Dose) %>%
      pivot_wider(names_from = Week,
                  values_from = Count) %>%
      relocate(TotalDosesAdmin, .after = Dose) %>%
      mutate(Site = factor(Site, levels = c(all_sites, "MSHS"),
                           ordered = TRUE),
             Dose = factor(Dose, levels = doses,
                           ordered = TRUE)) %>%
      arrange(Site, Dose)

    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
                          paste0(dose, "Doses"))

    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
                         paste (dose, "Doses"))

    arr_visits_kable_df <<- arr_visits_totals %>%
      filter(Dose == dose_filter) %>%
      mutate(Dose = NULL) %>%
      rename(`Admin Doses to Date` = TotalDosesAdmin)

    arr_visits_kable_headers <- 
      c(" " = 2,
        "Administered Doses by Week" = ncol(arr_visits_kable_df) - 2)

    kable(arr_visits_kable_df, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste0(vax_type, " ", dose_title, ": Administered Doses To Date")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           2,
                           ncol(arr_visits_kable_df)),
                border_right = "thin solid lightgray") %>%
    column_spec(column = c(3:ncol(arr_visits_kable_df)),
                background = sinai_colors[2]) %>%
    row_spec(row = nrow(arr_visits_kable_df),
             background = "lightgrey",
             bold = T,
             italic = T,
             color = "black") %>%
    add_header_above(arr_visits_kable_headers,
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px")
  }
}
```

```{r Subset data and create custom function for visualizing schedule over next 7 days}

sch_visits <- daily_sched_summary %>%
  filter(Status2 %in% c("Sch")) %>%
  group_by(Site,
           VaxType,
           Dose,
           ApptDate) %>%
  summarize(Count = sum(Count, na.rm = TRUE))

# Create template of today through the next 7 days for each site and dose to ensure holidays are included
today_to_7days <- seq(from = today, to = today + 7, by = 1)

today_to_7days_templ <- data.frame("ApptDate" = rep(today_to_7days,
                                          length(all_sites)))

site_7day_sched_templ <- data.frame("Site" = sort(rep(all_sites,
                                                        length(today_to_7days)
                                                        )
                                                    ),
                                      "ApptDate" = today_to_7days_templ)

site_vax_dose_7day_sched_templ <- left_join(site_vax_dose_templ,
                                            site_7day_sched_templ,
                                            by = c("Site" = "Site"))

sch_visits <- left_join(site_vax_dose_7day_sched_templ,
                          sch_visits,
                          by = c("Site" = "Site",
                                 "VaxType" = "VaxType",
                                 "Dose" = "Dose",
                                 "ApptDate" = "ApptDate"))

sch_visits_kable <- function(vax_type, dose) {
  if (!(vax_type %in% c("Adult", "Peds") |
        dose %in% c(1, 2, 3, "All"))) {
    msg <- "Invalid argument"
    stop(msg)
  } else {

    sch_visits_totals <<- sch_visits %>%
      filter(VaxType %in% vax_type) %>%
      mutate(VaxType = NULL,
             Count = replace_na(Count, 0)) %>%
      arrange(Site, Dose, ApptDate) %>%
      pivot_wider(names_from = c(Dose, ApptDate),
                  names_sep = "__",
                  values_from = Count,
                  names_sort = FALSE) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "MSHS") %>%
      pivot_longer(cols = contains("__", ignore.case = TRUE),
                   names_to = c("Dose", "Date"),
                   names_sep = "__",
                   values_to = "Count") %>%
      mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%m/%d")) %>%
      pivot_wider(names_from = c(Site, Dose),
                  names_sep = "__",
                  values_from = Count) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "Total") %>%
      pivot_longer(cols = contains("__", ignore.case = TRUE),
                   names_to = c("Site", "Dose"),
                   names_sep = "__",
                   values_to = "Count") %>%
      relocate(Site) %>%
      relocate(Dose, .after = Site) %>%
      mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
             Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
      arrange(Site, Dose) %>%
      pivot_wider(names_from = Date,
                  values_from = Count)
    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
                          paste0(dose, "Doses"))

    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
                         paste (dose, "Doses"))

    sch_visits_kable_df <<- sch_visits_totals %>%
      filter(Dose == dose_filter) %>%
      mutate(Dose = NULL)

    sch_visits_kable_headers <-
      c(" " = 1,
        "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)

    kable(sch_visits_kable_df, format = "html", escape = FALSE,
          align = "c", digits = 0,
          caption = paste0(vax_type, " ", dose_title, ": Scheduled Appointments")) %>%
      kable_styling(bootstrap_options = "hover", position = "center",
                    font_size = 11, full_width = FALSE) %>%
      column_spec(column = c(1,
                             ncol(sch_visits_kable_df) - 1,
                             ncol(sch_visits_kable_df)),
                  border_right = "thin solid lightgray") %>%
      row_spec(row = nrow(sch_visits_kable_df),
               background = "lightgrey",
               bold = T,
               italic = T,
               color = "black") %>%
      add_header_above(sch_visits_kable_headers,
                       background = c("",
                                      sinai_colors[1]),
                       line = FALSE,
                       color = "white")
  }
}

```

#### Administered & Scheduled Vaccines as of `r format(Sys.Date(), "%m/%d/%y")` 3:40PM {.tabset}

##### <span style = "color:#221f72;font-weight:bold">Adult - All Doses</span>
```{r Subset data and create kable for all adult doses administered}

arr_visits_kable(vax_type = "Adult", dose = "All")

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Adult", dose = "All")

```
<p></p>

##### <span style = "color:#221f72">Adult - Dose 1</span>
<p></p>
```{r Subset data and create kable for adult first doses administered}
arr_visits_kable(vax_type = "Adult", dose = 1)

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Adult", dose = 1)

```

<p></p>
##### <span style = "color:#221f72">Adult - Dose 2</span>
<p></p>
```{r Subset data and create kable for adult second doses administered}
arr_visits_kable(vax_type = "Adult", dose = 2)

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Adult", dose = 2)

```

<p></p>
##### <span style = "color:#221f72">Adult - Dose 3</span>
<p></p>
```{r Subset data and create kable for adult third doses administered}
arr_visits_kable(vax_type = "Adult", dose = 3)

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Adult", dose = 3)

```

<p></p>
##### <span style = "color:#00AEEF;font-weight:bold">Peds - All Doses</span>
<p></p>
```{r Subset data and create kable for all peds doses administered}
arr_visits_kable(vax_type = "Peds", dose = "All")

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Peds", dose = "All")

```

<p></p>
##### <span style = "color:#00AEEF">Peds - Dose 1</span>
<p></p>
```{r Subset data and create kable for peds first doses administered}
arr_visits_kable(vax_type = "Peds", dose = 1)

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Peds", dose = 1)

```

<p></p>
##### <span style = "color:#00AEEF">Peds - Dose 2</span>
<p></p>
```{r Subset data and create kable for peds second doses administered}
arr_visits_kable(vax_type = "Peds", dose = 2)

asis_output("<h3>  </h3>")

sch_visits_kable(vax_type = "Peds", dose = 2)

```

### 2021-12-10 Adult_Peds_Weekly_Arrivals_Sched_Tracking.Rmd
Update analysis reference files. Add Peds Dose 2 to Amb Sched Tracking tool.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-11-03.xlsx"),
+                                   "Automation Ref 2021-11-22.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-11-03.xlsx"),
+                                  "Automation Ref 2021-11-22.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2021-12-10 Amb_Sched_Tracking.Rmd
Update analysis reference files. Add Peds Dose 2 to Amb Sched Tracking tool.

@@
 
+### All Doses
+```{r Call custom function for schedule for all peds appointments}
+sched_data_kable(vax_type = "Peds", dose = "AllDoses")
+
+```
+
+<br>
+
 ### Dose 1
@@
 
-<!-- <br> -->
+### Dose 2
+```{r Call custom function for schedule for peds dose 2 appointments}
+sched_data_kable(vax_type = "Peds", dose = "Dose2")
+
+```
+
+<br>
 

### 2021-12-10 Ad Hoc Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-11-03.xlsx"),
+                                   "Automation Ref 2021-11-22.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-11-03.xlsx"),
+                                  "Automation Ref 2021-11-22.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2021-12-10 Evening-Huddle-Dashboard.R

@@ -10,7 +10,7 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-rmarkdown::render("Adult_Peds_Weekly_Arrivals_Sched_Tracking.Rmd",
+rmarkdown::render("Combined Dashboard Arrived and Sched Appts.Rmd",
                   output_file = paste0(user_directory,
                                        "/Daily PM Huddle Output/",
                                        "MSHS Vaccine Summary ",

### 2021-12-10 Combined Dashboard Arrived and Sched Appts.Rmd
Create new script for combined dashboard showing cumulative doses to date and arrived and scheduled appointments from yesterday out two weeks.

--- 2021-12-10 Adult_Peds_Weekly_Arrivals_Sched_Tracking.Rmd
@@
 # Store today's date
-today <- Sys.Date()
+today <- Sys.Date() - 1
 yesterday <- today - 1
@@
 # Specify Sinai colors for table
-sinai_colors <- c("#221f72", "#C4C3EF",
-                  "#00AEEF", "#B3EBFF",
-                  "#D80B8C", "#FBB6E2")
+sinai_colors <- c("Dark Blue" = "#221f72",
+                  "Light Purple" = "#C4C3EF",
+                  "Aqua" = "#00AEEF",
+                  "Light Blue" = "#B3EBFF",
+                  "Hot Pink" = "#D80B8C",
+                  "Light Pink" = "#FBB6E2")
 
@@
   filter(Status2 %in% c("Arr", "Sch") &
-           ApptDate <= today + 7) %>%
+           ApptDate <= today + 14) %>%
   group_by(Site,
@@
                 border_right = "thin solid lightgray") %>%
-    column_spec(column = c(3:ncol(arr_visits_kable_df)),
-                background = sinai_colors[2]) %>%
+    # column_spec(column = c(3:ncol(arr_visits_kable_df)),
+    #             background = sinai_colors[2]) %>%
     row_spec(row = nrow(arr_visits_kable_df),
@@
                      background = c("",
-                                    sinai_colors[1]),
+                                    sinai_colors["Dark Blue"]),
                      line = FALSE,
                      color = "white") %>%
-    scroll_box(width = "800px")
+    scroll_box(width = "800px",
+               box_css = "margin: auto;")
   }
@@
 
-```{r Subset data and create custom function for visualizing schedule over next 7 days}
+```{r Subset data for appointments arrived yesterday, today, and scheduled for the next 2 weeks}
 
-sch_visits <- daily_sched_summary %>%
-  filter(Status2 %in% c("Sch")) %>%
+# Create a template of dates from yesterday out 2 weeks for each site and dose to ensure holidays/weekends are included
+# First create a template of yesterday and today's date for appointments that have beena arrived
+yest_today <- seq(from = yesterday,
+                    to = today, by = 1)
+
+yest_today_status <- data.frame("ApptDate" = yest_today,
+                                "Status" = "Arr")
+
+# Then create a template of today out 2 weeks for appointments in scheduled status
+today_2wks <- seq(from = today,
+                  to = today + 14,
+                  by = 1)
+
+today_2wks_status <- data.frame("ApptDate" = today_2wks,
+                                "Status" = "Sch")
+
+# Combine the arrived and scheduled appt status data frames
+yest_2wks_status <- rbind(yest_today_status,
+                          today_2wks_status)
+
+yest_2wks_status <- yest_2wks_status %>%
+  arrange(ApptDate, Status)
+
+# Repeate the dates and appt statuses for all sites
+yest_2wks_status_site <- bind_rows(
+  replicate(length(all_sites),
+            yest_2wks_status,
+            simplify = FALSE
+            )
+)
+
+# Create a dataframe of all sites repeated for arrived and scheduled appt status
+sites_yest_2wks <- data.frame("Site" = rep(all_sites,
+                       nrow(yest_2wks_status)))
+
+sites_yest_2wks <- sites_yest_2wks %>%
+  arrange(Site)
+
+# Combine the two templates
+yest_2wks_status_site_templ <- cbind(yest_2wks_status_site,
+                                     sites_yest_2wks)
+
+# Combine date, appointment status, and site datagrame with vaccine dose and type dataframe
+yest_2wks_status_site_vax_dose_templ <- left_join(
+  yest_2wks_status_site_templ,
+  site_vax_dose_templ,
+  by = c("Site" = "Site")
+)
+
+# Subset arrived visits yesterday and today and scheduled visits through the next 2 weeks
+
+yest_2wks_arr_sch_visits <- daily_sched_summary %>%
+  filter(ApptDate >= yesterday &
+           ApptDate <= today + 14) %>%
   group_by(Site,
@@
            Dose,
+           Status2,
            ApptDate) %>%
@@
 
-# Create template of today through the next 7 days for each site and dose to ensure holidays are included
-today_to_7days <- seq(from = today, to = today + 7, by = 1)
+# Combine with template to ensure no dates, sites, doses, etc. are missing
+yest_2wks_arr_sch_visits <- left_join(
+  yest_2wks_status_site_vax_dose_templ,
+  yest_2wks_arr_sch_visits,
+  by = c("ApptDate" = "ApptDate",
+         "Status" = "Status2",
+         "Site" = "Site",
+         "Dose" = "Dose",
+         "VaxType" = "VaxType")
+)
 
-today_to_7days_templ <- data.frame("ApptDate" = rep(today_to_7days,
-                                          length(all_sites)))
-
-site_7day_sched_templ <- data.frame("Site" = sort(rep(all_sites,
-                                                        length(today_to_7days)
-                                                        )
-                                                    ),
-                                      "ApptDate" = today_to_7days_templ)
-
-site_vax_dose_7day_sched_templ <- left_join(site_vax_dose_templ,
-                                            site_7day_sched_templ,
-                                            by = c("Site" = "Site"))
-
-sch_visits <- left_join(site_vax_dose_7day_sched_templ,
-                          sch_visits,
-                          by = c("Site" = "Site",
-                                 "VaxType" = "VaxType",
-                                 "Dose" = "Dose",
-                                 "ApptDate" = "ApptDate"))
-
-sch_visits_kable <- function(vax_type, dose) {
+arr_sch_visits_kable <- function(vax_type, dose) {
   if (!(vax_type %in% c("Adult", "Peds") |
@@
 
-    sch_visits_totals <<- sch_visits %>%
-      filter(VaxType %in% vax_type) %>%
-      mutate(VaxType = NULL,
+    # Filter for dataframe based on custom function user input
+    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
+                          paste0(dose, "Doses"))
+
+    # Title for table based on user input
+    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
+                         paste (dose, "Doses"))
+
+    # Format dataframe of arrived and scheduled visits for kable visualization
+    arr_sch_visits_totals <<- yest_2wks_arr_sch_visits %>%
+      # Filter on vaccine type and dose
+      filter(VaxType %in% vax_type &
+               Dose %in% dose_filter) %>%
+      mutate(
+        # Remove vaccine type and dose columns
+        VaxType = NULL,
+        Dose = NULL,
+        # Replace any NA with 0 for better visualization
         Count = replace_na(Count, 0)) %>%
-      arrange(Site, Dose, ApptDate) %>%
-      pivot_wider(names_from = c(Dose, ApptDate),
-                  names_sep = "__",
+      arrange(Site, ApptDate, Status) %>%
+      # Pivot wider and calculate totals across health system for each day
+      pivot_wider(names_from = c(Status, ApptDate),
+                  names_sep = "_",
                   values_from = Count,
@@
                    name = "MSHS") %>%
-      pivot_longer(cols = contains("__", ignore.case = TRUE),
-                   names_to = c("Dose", "Date"),
-                   names_sep = "__",
+      # Pivot longer and reformat date from character to date
+      pivot_longer(cols = contains("_", ignore.case = TRUE),
+                   names_to = c("Status", "Date"),
+                   names_sep = "_",
                    values_to = "Count") %>%
       mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%m/%d")) %>%
-      pivot_wider(names_from = c(Site, Dose),
-                  names_sep = "__",
-                  values_from = Count) %>%
-      adorn_totals(where = "row",
+      # Pivot wider and calculate totals for each site from yesterday out 2 weeks
+      pivot_wider(names_from = c(Status, Date),
+                  names_sep = "_",
+                  values_from = "Count") %>%
+      adorn_totals(where = "col",
                    na.rm = TRUE,
                    name = "Total") %>%
-      pivot_longer(cols = contains("__", ignore.case = TRUE),
-                   names_to = c("Site", "Dose"),
-                   names_sep = "__",
-                   values_to = "Count") %>%
-      relocate(Site) %>%
-      relocate(Dose, .after = Site) %>%
-      mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
-             Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
-      arrange(Site, Dose) %>%
-      pivot_wider(names_from = Date,
-                  values_from = Count)
-    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
-                          paste0(dose, "Doses"))
+      # Convert sites to factor for improved visualizations
+      mutate(
+        Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE)
+      ) %>%
+      arrange(Site)
 
-    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
-                         paste (dose, "Doses"))
+    # Determine kable headers based on dataframe column names
+    kable_headers <- c(" " = 1,
+                       # Determine columns for arrived visits
+                       "Arrived Appts" = max(
+                         which(str_detect(colnames(arr_sch_visits_totals),
+                                          "Arr")
+                         )
+                       ) - 
+                         min(
+                           which(str_detect(colnames(arr_sch_visits_totals),
+                                            "Arr")
+                           )
+                         ) + 1,
 
-    sch_visits_kable_df <<- sch_visits_totals %>%
-      filter(Dose == dose_filter) %>%
-      mutate(Dose = NULL)
+                       # Determine columns for scheduled visits
+                       "Scheduled Appts" = max(
+                         which(str_detect(colnames(arr_sch_visits_totals),
+                                          "Sch")
+                         )
+                       ) -
+                         min(
+                           which(str_detect(colnames(arr_sch_visits_totals),
+                                            "Sch")
+                           )
+                         ) + 1,
+                       # Determine column for total visits
+                       "Total" = max(
+                         which(str_detect(colnames(arr_sch_visits_totals),
+                                          "Total")
+                         )
+                       ) -
+                         min(
+                           which(str_detect(colnames(arr_sch_visits_totals),
+                                            "Total")
+                           )
+                         ) + 1
+    )
 
-    sch_visits_kable_headers <-
-      c(" " = 1,
-        "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)
-
-    kable(sch_visits_kable_df, format = "html", escape = FALSE,
-          align = "c", digits = 0,
-          caption = paste0(vax_type, " ", dose_title, ": Scheduled Appointments")) %>%
-      kable_styling(bootstrap_options = "hover", position = "center",
-                    font_size = 11, full_width = FALSE) %>%
+    # Create kable for visualizing appointment volume from yesterday out 2 weeks
+    kable(arr_sch_visits_totals,
+          format = "html",
+          # Update column names to only show dates, where applicable
+          col.names = gsub("[A-Za-z]+\\_", "",
+                       colnames(arr_sch_visits_totals)),
+          escape = FALSE,
+          align = "c",
+          digits = 0,
+          caption = paste0(vax_type,
+                           " ",
+                           dose_title,
+                           ": Arrived & Scheduled Appts")) %>%
+      kable_styling(bootstrap_options = "hover",
+                    position = "center",
+                    font_size = 11,
+                    full_width = FALSE) %>%
       column_spec(column = c(1,
-                             ncol(sch_visits_kable_df) - 1,
-                             ncol(sch_visits_kable_df)),
+                             max(
+                               which(
+                                 str_detect(colnames(arr_sch_visits_totals),
+                                            "Arr")
+                               )
+                             ),
+                             max(
+                               which(
+                                 str_detect(colnames(arr_sch_visits_totals),
+                                            "Sch")
+                                 )
+                             ),
+                             ncol(arr_sch_visits_totals)
+                             ),
                   border_right = "thin solid lightgray") %>%
-      row_spec(row = nrow(sch_visits_kable_df),
+      row_spec(row = nrow(arr_sch_visits_totals),
                background = "lightgrey",
@@
                color = "black") %>%
-      add_header_above(sch_visits_kable_headers,
+      add_header_above(kable_headers,
                        background = c("",
-                                      sinai_colors[1]),
+                                      sinai_colors["Aqua"],
+                                      sinai_colors["Dark Blue"],
+                                      sinai_colors["Hot Pink"]),
                        line = FALSE,
@@
 
-sch_visits_kable(vax_type = "Adult", dose = "All")
+arr_sch_visits_kable(vax_type = "Adult", dose = "All")
 
@@
 
-sch_visits_kable(vax_type = "Adult", dose = 1)
+arr_sch_visits_kable(vax_type = "Adult", dose = 1)
 
@@
 
-sch_visits_kable(vax_type = "Adult", dose = 2)
+arr_sch_visits_kable(vax_type = "Adult", dose = 2)
 
@@
 
-sch_visits_kable(vax_type = "Adult", dose = 3)
+arr_sch_visits_kable(vax_type = "Adult", dose = 3)
 
@@
 
-sch_visits_kable(vax_type = "Peds", dose = "All")
+arr_sch_visits_kable(vax_type = "Peds", dose = "All")
 
@@
 
-sch_visits_kable(vax_type = "Peds", dose = 1)
+arr_sch_visits_kable(vax_type = "Peds", dose = 1)
 
@@
 
-sch_visits_kable(vax_type = "Peds", dose = 2)
+arr_sch_visits_kable(vax_type = "Peds", dose = 2)
 

### 2021-12-10 Combined Dashboard Arrived and Sched Appts.Rmd
Update analysis reference file with 31-60 21 St General Surgery.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-11-22.xlsx"),
+                                   "Automation Ref 2021-12-10.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-11-22.xlsx"),
+                                  "Automation Ref 2021-12-10.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
 # Store today's date
-today <- Sys.Date() - 1
+today <- Sys.Date()
 yesterday <- today - 1

### 2021-12-10 Daily Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-11-22.xlsx"),
+                                   "Automation Ref 2021-12-10.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-11-22.xlsx"),
+                                  "Automation Ref 2021-12-10.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2022-01-10 Combined Dashboard Arrived and Sched Appts.Rmd
Update analysis reference file to include school based practices and update logic for adult vs peds based on the vaccines these pods administer.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-12-10.xlsx"),
+                                   "Automation Ref 2021-12-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-12-10.xlsx"),
+                                  "Automation Ref 2021-12-20.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2022-01-10 Ad Hoc Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-12-10.xlsx"),
+                                   "Automation Ref 2022-01-10.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-12-10.xlsx"),
+                                  "Automation Ref 2022-01-10.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -109,6 +109,13 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 
 # Vaccine types
 vax_types <- c("Adult", "Peds")
+
+# Pediatric school based practices
+peds_school_practice_dept <- c("HOSP SBH PS 38",
+                               "HOSP SBH PS 83/ PS 182",
+                               "HOSP SBH PS 108",
+                               "HOSP SBH TPEC",
+                               "HOSP PEDS SCH HEALTH")
 
 # NY zip codes
 ny_zips <- search_state("NY")
@@ -228,7 +235,8 @@ sched_to_date <- sched_to_date %>%
     # Determine whether the vaccine is an adult or pediatric dose
     VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
                        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
-                                                  "DOSE 2 PEDIATRIC [1324685]"),
+                                                  "DOSE 2 PEDIATRIC [1324685]") |
+                       Department %in% peds_school_practice_dept,
                      "Peds", "Adult"),
     # Determine manufacturer based on immunization field and vaccine type fields
     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived

### 2022-01-10 Daily Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-12-10.xlsx"),
+                                   "Automation Ref 2021-12-20.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-12-10.xlsx"),
+                                  "Automation Ref 2021-12-20.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2022-01-11 Daily Vaccine Reporting and Export.R
Update analysis reference file in Daily Vaccing Reporting file.

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-12-20.xlsx"),
+                                   "Automation Ref 2022-01-10.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-12-20.xlsx"),
+                                  "Automation Ref 2022-01-10.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2022-01-12 Combined Dashboard Arrived and Sched Appts.Rmd
Create script to output summary of departments, providers, and visit types from 12/21 on.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2021-12-20.xlsx"),
+                                   "Automation Ref 2022-01-10.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2021-12-20.xlsx"),
+                                  "Automation Ref 2022-01-10.xlsx"),
                            sheet = "Pod Mappings Simple")

### 2022-01-12 Summarize Dept Providers Visit Types.R

@@ -1,0 +1,246 @@
+# Code for creating summary of departments, provider/resources, and visit types -----------------
+
+#Install and load necessary packages --------------------
+# install.packages("readxl")
+# install.packages("writexl")
+# install.packages("ggplot2")
+# install.packages("lubridate")
+# install.packages("dplyr")
+# install.packages("reshape2")
+# install.packages("svDialogs")
+# install.packages("stringr")
+# install.packages("formattable")
+# install.packages("kableExtra")
+# install.packages("ggpubr")
+# install.packages("zipcodeR")
+# install.packages("tidyr")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(janitor)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Determine whether or not to update an existing repo
+initial_run <- FALSE
+update_repo <- FALSE
+
+# Determine whether or not to update walk-in analysis
+update_walkins <- FALSE
+
+# Import reference data for site and pod mappings
+site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                   "Automation Ref 2022-01-10.xlsx"),
+                            sheet = "Site Mappings")
+pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                  "Automation Ref 2022-01-10.xlsx"),
+                           sheet = "Pod Mappings Simple")
+
+# Store today's date
+today <- Sys.Date()
+
+# Create dataframe with dates and weeks
[…]

### 2022-02-04 Combined Dashboard Arrived and Sched Appts.Rmd
Update analysis reference file.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-10.xlsx"),
+                                   "Automation Ref 2022-01-18.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-10.xlsx"),
+                                  "Automation Ref 2022-01-18.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
 ```
+
+#### {-}
+<h5><i>Appointments at school-based practices included in MSH volume.</i></h5>

### 2022-02-04 Ad Hoc Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-18.xlsx"),
+                                   "Automation Ref 2022-01-31.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-18.xlsx"),
+                                  "Automation Ref 2022-01-31.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -116,6 +116,7 @@ peds_school_practice_dept <- c("HOSP SBH PS 38",
                                "HOSP SBH PS 108",
                                "HOSP SBH TPEC",
                                "HOSP PEDS SCH HEALTH")
+
 
 # NY zip codes
 ny_zips <- search_state("NY")

### 2022-02-04 Daily Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-10.xlsx"),
+                                   "Automation Ref 2022-01-31.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-10.xlsx"),
+                                  "Automation Ref 2022-01-31.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2022-02-04 School Based Practice Summary.R
Create file for summarizing school based practice appointments.

@@ -1,0 +1,225 @@
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+library(janitor)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Determine whether or not to update an existing repo
+update_repo <- TRUE
+
+# Determine whether or not to update walk-in analysis
+update_walkins <- FALSE
+
+# Import reference data for site and pod mappings
+site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                   "Automation Ref 2022-01-31.xlsx"),
+                            sheet = "Site Mappings")
+pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                  "Automation Ref 2022-01-31.xlsx"),
+                           sheet = "Pod Mappings Simple")
+school_based_practices <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                            "Automation Ref 2022-01-31.xlsx"),
+                                     sheet = "School Based Practices")
+
+school_based_practices_dept <- (unique(school_based_practices[, c("Epic Department",
+                                                                "Vaccine Type")]))
+
+school_based_practices_dept <- school_based_practices_dept %>%
+  filter(!is.na(`Epic Department`)) %>%
+  rename(Epic_Dept = `Epic Department`,
+         Age_Group = `Vaccine Type`)
+
+# Store today's date
+today <- Sys.Date()
+
+# Create dataframe with dates and weeks
[…]

### 2022-03-16 Combined Dashboard Arrived and Sched Appts.Rmd
Create script to summary doses administered at MSH pods/departments for BC.

@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-18.xlsx"),
+                                   "Automation Ref 2022-03-02.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-18.xlsx"),
+                                  "Automation Ref 2022-03-02.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
     # Determine whether the vaccine is an adult or pediatric dose
-    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
+    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
+                                       "1468 MADISON HOSP PEDS GEN") |
                        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",

### 2022-03-16 Ad Hoc Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-31.xlsx"),
+                                   "Automation Ref 2022-03-02.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-31.xlsx"),
+                                  "Automation Ref 2022-03-02.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -234,7 +234,8 @@ sched_to_date <- sched_to_date %>%
                      ifelse(ApptDate >= today & Status == "Arr", "Sch",
                             Status)),
     # Determine whether the vaccine is an adult or pediatric dose
-    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
+    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
+                                       "1468 MADISON HOSP PEDS GEN") |
                        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
                                                   "DOSE 2 PEDIATRIC [1324685]") |
                        Department %in% peds_school_practice_dept,

### 2022-03-16 Daily Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-31.xlsx"),
+                                   "Automation Ref 2022-03-02.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-31.xlsx"),
+                                  "Automation Ref 2022-03-02.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -217,7 +217,8 @@ sched_to_date <- sched_to_date %>%
                      ifelse(ApptDate >= today & Status == "Arr", "Sch",
                             Status)),
     # Determine whether the vaccine is an adult or pediatric dose
-    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
+    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
+                                       "1468 MADISON HOSP PEDS GEN") |
                        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
                                                   "DOSE 2 PEDIATRIC [1324685]"),
                      "Peds", "Adult"),

### 2022-03-16 MSH Admin Dose Summary.R

@@ -1,0 +1,257 @@
+# Code for creating repository of COVID vaccine administration -----------------
+
+#Install and load necessary packages --------------------
+# install.packages("readxl")
+# install.packages("writexl")
+# install.packages("ggplot2")
+# install.packages("lubridate")
+# install.packages("dplyr")
+# install.packages("reshape2")
+# install.packages("svDialogs")
+# install.packages("stringr")
+# install.packages("formattable")
+# install.packages("kableExtra")
+# install.packages("ggpubr")
+# install.packages("zipcodeR")
+# install.packages("tidyr")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+library(janitor)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Determine whether or not to update an existing repo
+update_repo <- TRUE
+
+# Import reference data for site and pod mappings
+site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                   "Automation Ref 2022-03-02.xlsx"),
+                            sheet = "Site Mappings")
+pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
+                                  "Automation Ref 2022-03-02.xlsx"),
+                           sheet = "Pod Mappings Simple")
+
+dept_grouping <- read_excel(paste0(user_directory,
+                                   "/ScheduleData/",
+                                   "Automation Ref 2022-03-02.xlsx",)
[…]

### 2022-03-29 Combined Dashboard Arrived and Sched Appts.Rmd
Update logic for Peds only departments. Update analysis reference file.

--- 2022-02-04 Combined Dashboard Arrived and Sched Appts.Rmd
@@
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-01-18.xlsx"),
+                                   "Automation Ref 2022-03-21.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-01-18.xlsx"),
+                                  "Automation Ref 2022-03-21.xlsx"),
                            sheet = "Pod Mappings Simple")
@@
     # Determine whether the vaccine is an adult or pediatric dose
-    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD") |
+    VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
+                                       "1468 MADISON HOSP PEDS GEN",
+                                       "10 UNION SQ E PEDS GEN",
+                                       "234 E 85TH ST PEDS GEN",
+                                       "5 E 98  PEDS GENERAL") |
                        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",

### 2022-03-29 Ad Hoc Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-03-02.xlsx"),
+                                   "Automation Ref 2022-03-21.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-03-02.xlsx"),
+                                  "Automation Ref 2022-03-0.1xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date
@@ -235,7 +235,10 @@ sched_to_date <- sched_to_date %>%
                             Status)),
     # Determine whether the vaccine is an adult or pediatric dose
     VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
-                                       "1468 MADISON HOSP PEDS GEN") |
+                                       "1468 MADISON HOSP PEDS GEN",
+                                       "10 UNION SQ E PEDS GEN",
+                                       "234 E 85TH ST PEDS GEN",
+                                       "5 E 98  PEDS GENERAL") |
                        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
                                                   "DOSE 2 PEDIATRIC [1324685]") |
                        Department %in% peds_school_practice_dept,

### 2022-03-29 Daily Vaccine Reporting and Export.R

@@ -61,10 +61,10 @@ update_walkins <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-03-02.xlsx"),
+                                   "Automation Ref 2022-03-21.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-03-02.xlsx"),
+                                  "Automation Ref 2022-03-21.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2022-03-29 MSH Admin Dose Summary.R

@@ -54,19 +54,19 @@ if ("Presidents" %in% list.files("J://")) {
 user_path <- paste0(user_directory, "\\*.*")
 
 # Determine whether or not to update an existing repo
-update_repo <- TRUE
+update_repo <- FALSE
 
 # Import reference data for site and pod mappings
 site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                   "Automation Ref 2022-03-02.xlsx"),
+                                   "Automation Ref 2022-03-21.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-03-02.xlsx"),
+                                  "Automation Ref 2022-03-21.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 dept_grouping <- read_excel(paste0(user_directory,
                                    "/ScheduleData/",
-                                   "Automation Ref 2022-03-02.xlsx",)
+                                   "Automation Ref 2022-03-21.xlsx"),
                                    sheet = "Dept Mapping and Grouping")
 
 # Store today's date
@@ -112,16 +112,16 @@ mfg <- c("Pfizer", "Moderna", "J&J")
 # Vaccine types
 vax_types <- c("Adult", "Peds")
 
-# Pediatric school based practices
-peds_school_practice_dept <- c("HOSP SBH PS 38",
-                               "HOSP SBH PS 83/ PS 182",
-                               "HOSP SBH PS 108",
-                               "HOSP SBH TPEC",
-                               "HOSP PEDS SCH HEALTH")
+# Dept grouper
+dept_group <- c("Hospital POD", "School Based Practice", "MSHS Practice")
 
+# # Pediatric school based practices
+# peds_school_practice_dept <- c("HOSP SBH PS 38",
+#                                "HOSP SBH PS 83/ PS 182",
+#                                "HOSP SBH PS 108",
+#                                "HOSP SBH TPEC",
+#                                "HOSP PEDS SCH HEALTH")
 
-# NY zip codes
-ny_zips <- search_state("NY")
 
 # Import schedule repository and determine last date it was updated
 sched_repo_file <- choose.files(default = paste0(user_directory,
@@ -168,13 +168,92 @@ sched_to_date <- sched_to_date %>%
                      # Correct any appts erroneously marked as arrived early
[…]

### 2022-04-05 MSH Admin Dose Summary.Rmd
Create file for updated vaccine reporting based on total doses administered to date and new department mapping from OneDrive.

---
title: "MSHS COVID-19 Vaccination Summary"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Install and load packages}
# Code for creating summary of COVID vaccine administration -----------------

#Install and load necessary packages --------------------
# install.packages("readxl")
# install.packages("writexl")
# install.packages("ggplot2")
# install.packages("lubridate")
# install.packages("dplyr")
# install.packages("reshape2")
# install.packages("svDialogs")
# install.packages("stringr")
# install.packages("formattable")
# install.packages("kableExtra")
# install.packages("ggpubr")
# install.packages("zipcodeR")
# install.packages("tidyr")

#Analysis for weekend discharge tracking
library(readxl)
library(writexl)
library(ggplot2)
library(lubridate)
library(dplyr)
library(reshape2)
library(svDialogs)
library(stringr)
library(formattable)
library(scales)
library(ggpubr)
library(reshape2)
library(knitr)
library(kableExtra)
library(rmarkdown)
library(zipcodeR)
library(tidyr)
library(purrr)
library(janitor)
```

```{r Set directory, import reference data, and repository, include = FALSE}
# Set working directory and select raw data ----------------------------
rm(list = ls())

# Determine path for working directory
if ("Presidents" %in% list.files("J://")) {
  user_directory <- paste0("J:/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
} else {
  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
                           "Operations Analytics and Optimization/Projects/",
                           "System Operations/COVID Vaccine")
}

# Set path for file selection
user_path <- paste0(user_directory, "\\*.*")

# Determine whether or not to update an existing repo
update_repo <- FALSE

# Import reference data for site and pod mappings
dept_mappings <- read_excel(paste0(user_directory, "/Reference File Apr 2022/",
                                   "MSHS COVID-19 Vaccine Department Mappings 2022-04-05.xlsx"))

dept_mappings <- dept_mappings %>%
  select(-`Site (Historical)`, -Notes)

# Store today's date
today <- Sys.Date()

# Create dataframe with dates and weeks
all_dates <- data.frame("Date" = seq.Date(as.Date("1/1/20",
                                                  format = "%m/%d/%y"),
                                          as.Date("12/31/21",
                                                  format = "%m/%d/%y"),
                                          by = 1))
all_dates <- all_dates %>%
  mutate(Year = year(Date),
         WeekNum = format(Date, "%U"))

# Site order
all_sites <- c("MSB",
               "MSBI",
               "MSH",
               "MSM",
               "MSQ",
               "MSW",
               "MSVD",
               "Network LI")#,
# "MSHS")

# Site order
city_sites <- c("MSB",
                "MSBI",
                "MSH",
                "MSM",
                "MSQ",
                "MSW",
                "MSVD")#,
# "MSHS")

# Vaccine types
vax_types <- c("Adult", "Peds")

# Dept grouper
dept_group <- c("Hospital POD", "MSHS Practice")
```

```{r Import existing repo and append as needed}

# Import schedule repository and determine last date it was updated
sched_repo_file <- choose.files(default = paste0(user_directory,
                                                 "/R_Sched_AM_Repo/*.*"))

sched_repo <- readRDS(sched_repo_file)
sched_repo_update_date <- date(file.info(sched_repo_file)$ctime)

if (update_repo) {

  # Determine date range of reports to add to repository
  new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
  new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")

  # Find list of reports
  file_list_vacc_sched <- list.files(
    path = paste0(user_directory,
                  "/Epic Auto Report Sched All Status"),
    pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
                     new_report_dates_pattern,
                     ".*.csv",
                     collapse = "|"))

  # Import reports and add a column with report name and report date
  import_new_reports <- map_df(
    file_list_vacc_sched,
    .f = function(x){
      sched_data <- read.csv(
        paste0(user_directory,
               "/Epic Auto Report Sched All Status/",
               x),
        stringsAsFactors = FALSE,
        check.names = FALSE) %>%
        mutate(Filename = x,
               ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
                                    "%Y%m%d"),
               DOB = as.Date(DOB, format = "%m/%d/%Y"),
               `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
               Date = as.Date(Date, "%m/%d/%Y"),
               `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
                                        tz = "", format = "%Y-%m-%d %H:%M %p"),
               `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)))})

  # Filter schedule data from new reports to only keep appointments in latest reports
  sched_data_new_reports <- import_new_reports %>%
    group_by(Date) %>%
    slice_max(ReportDate) %>%
    mutate(Filename = NULL,
           ReportDate = NULL) %>%
    ungroup()

  new_reports_dates <- sort(unique(sched_data_new_reports$Date))

  # Remove vaccine appoints from any overlapping dates in repository and new reports
  sched_repo <- sched_repo %>%
    filter(!(Date >= new_reports_dates[1]))

  # Bind schedule repository and schedule from new reports
  sched_repo <- rbind(sched_repo, sched_data_new_reports)

  # Save new repository
  saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
                             "Auto Epic Report Sched ",
                             format(min(sched_repo$Date), "%m%d%y"), " to ",
                             format(max(sched_repo$Date), "%m%d%y"),
                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))

} else {

  sched_repo <- sched_repo

}
```

```{r Format and process schedule data}
# Format and analyze schedule to date for dashboards ---------------------------
sched_to_date <- sched_repo

sched_to_date <- sched_to_date %>%
  # rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
  mutate(
    # Update timezones to EST if imported as UTC
    `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
    # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
                  ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
                         ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
                                "Dose 3/Booster", NA))),
    # Determine appointment date, year, month, etc.
    ApptDate = date(Date),
    ApptYear = year(Date),
    ApptMonth = month(Date),
    ApptDay = day(Date),
    ApptWeek = week(Date),
    # Clean up department if it is duplicated in that column
    Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
    # Group arrived, completed, and checked out appts as arrived
    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                    "Arr", `Appt Status`),
    # (Only needed when manually pulling data in the morning)
    # Classify any arrivals from today as scheduled for morning export and
    # classify any appts from prior days that are still in scheduled status as
    # no shows
    # Status2 = ifelse(ApptDate == today & Status == "Arr", "Sch",
    #                  ifelse(ApptDate < today & Status == "Sch", "No Show",
    # Status)),
    # Update appointment status: classify any appts from prior days that are
    # still in scheduled as No Shows
    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
                     # Correct any appts erroneously marked as arrived early
                     ifelse(ApptDate >= today & Status == "Arr", "Sch",
                            Status)),
    # # Determine whether the vaccine is an adult or pediatric dose
    # VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
    #                                    "1468 MADISON HOSP PEDS GEN") |
    #                    `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
    #                                               "DOSE 2 PEDIATRIC [1324685]") |
    #                    Department %in% peds_school_practice_dept,
    #                  "Peds", "Adult"),
    # # Determine manufacturer based on immunization field and vaccine type fields
    # Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
    #   ifelse(Status2 != "Arr", NA,
    #          # Any blank immunizations and any peds assumed to be Pfizer
    #          ifelse(is.na(Immunizations) |
    #                   VaxType %in% c("Peds"), "Pfizer",
    #                 # Any immunizations with Moderna in text classified as Moderna
    #                 ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
    #                        # Any visiting docs or Johnson and Johnson
    #                        # immunizations classified as J&J
    #                        ifelse(str_detect(Department, "VISITING DOCS") |
    #                                 str_detect(Immunizations,
    #                                            "Johnson and Johnson"),
    #                               "J&J", "Pfizer")))),
    # Determine week number of year
    WeekNum = format(ApptDate, "%U"),
    # Determine appointment day of week
    DOW = weekdays(ApptDate),
    # # Determine if patient's zip code is in NYS
    # NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
    # Determine if patient is a MSHS employee based on response to question
    # MSHSEmployee =
    #   # First see if patient responded "YES" to question about MSHS employee
    #   str_detect(
    #     str_replace_na(IsPtEmployee, ""),
    #     regex("yes", ignore_case = TRUE)) |
    #   # Next, see if there is a MSHS site listed for patients who were vaccinated
    #   # prior to the addition of the MSHS employee field
    #   str_detect(
    #     str_replace_na(`MOUNT SINAI HEALTH SYSTEM`, " "),
    #     regex("[a-z]", ignore_case = TRUE))
    )

# Crosswalk sites and department grouper
sched_to_date <- left_join(sched_to_date, dept_mappings,
                           by = c("Department" = "Department"))

sched_to_date <- sched_to_date %>%
  rename(Site = `New Site`)

# Determine if there are any missing departments and notify user
unmapped_dept <- sched_to_date %>%
  filter(is.na(Site)) %>%
  select(Department) %>%
  distinct()

if(nrow(unmapped_dept) > 0) {
  stop(paste0("Check department mappings. Missing departments include ",
             paste(as.vector(unmapped_dept$Department), collapse = ", "),
             "."))
}

# Determine vaccine type (adult vs peds) administered based on department, provider, and age, as appropriate
sched_to_date <- sched_to_date %>%
  mutate(
    # Create a column for age grouper
    Age_Grouper = ifelse(str_detect(Age, "\\ y.o."), "years",
                        ifelse(str_detect(Age, "\\ m.o."), "months",
                               ifelse(str_detect(Age, "\\ days"), "days",
                                      "unknown"))),
    # Convert string with age to numeric
    Age_Numeric = 
      ifelse(Age_Grouper == "years",
                    as.numeric(str_extract(Age,
                                 # pattern = "(?<=Deceased\\ \\().+(?=\\ y.o.)")),
                                 paste("(?<=Deceased\\ \\()[0-9]+(?=\\ y.o.)",
                                       "[0-9]+(?=\\ y.o.)",
                                       sep = "|"))),
                    ifelse(Age_Grouper == "months",
                           as.numeric(str_extract(Age, "[0-9]+(?=\\ m.o.)")) / 12,
                           ifelse(Age_Grouper == "days",
                                  as.numeric(
                                    str_extract(Age, "[0-9]+(?=\\ days)")) / 365,
                                  ifelse(Age_Grouper == "unknown", 10000,
                                         NA_integer_)))),
    # Determine vaccine type based on department, provider/resource, and age if necessary
    VaxType = ifelse(
      `Vaccine Age Group` %in% "Peds" |
        (`Vaccine Age Group` %in% "Both" &
           # Determine if provider/resource at MSBI is peds
           (`Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
                                       "DOSE 2 PEDIATRIC [1324685]") |
              (`Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
                 Age_Numeric < 12))),
      "Peds", "Adult"),
    # Determine manufacturer based on immunization field and vaccine type fields
    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
      ifelse(Status2 != "Arr", NA,
             # Any blank immunizations and any peds assumed to be Pfizer
             ifelse(is.na(Immunizations) |
                      VaxType %in% c("Peds"), "Pfizer",
                    # Any immunizations with Moderna in text classified as Moderna
                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                           # Any visiting docs or Johnson and Johnson
                           # immunizations classified as J&J
                           ifelse(str_detect(Department, "VISITING DOCS") |
                                    str_detect(Immunizations,
                                               "Johnson and Johnson"),
                                  "J&J", "Pfizer")))),
    # Roll up any Moderna administered at MSB for YWCA to MSH
    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
                  ifelse(`Setting Grouper` %in% "School Based Practice" &
                           VaxType %in% "Peds", "Peds School Based Practice",
                         ifelse(`Setting Grouper` %in% "School Based Practice" &
                                  VaxType %in% "Adult",
                                "Adolescent School Based Practice",
                                Site))),
    # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
    Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c("Dose 2"), "Dose 1", Dose),
    `Setting Grouper` = ifelse(`Setting Grouper` %in% "School Based Practice",
                               "MSHS Practice", `Setting Grouper`))

vax_admin_start_date <- min(sched_to_date$ApptDate[
  which(sched_to_date$Status2 %in% "Arr")])

vax_admin_end_date <- max(sched_to_date$ApptDate[
  which(sched_to_date$Status2 %in% "Arr")])

# # Manually update discrepancies in site/mfg/dose
# sched_to_date <- sched_to_date %>%
#   mutate(# Roll up any Moderna administered at MSB for YWCA to MSH
#     Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
#     # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
#     Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c(2), 1, Dose))
# 
# # Crosswalk pod type (employee vs patient)
# sched_to_date <- left_join(sched_to_date,
#                            unique(pod_mappings[, c("Provider", "Pod Type")]),
#                            by = c("Provider/Resource" = "Provider"))
# 
# # Assume any pods without a mapping are patient pods
# sched_to_date[is.na(sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"

```

#### *Vaccines Administered from `r paste0(format(vax_admin_start_date, "%m/%d/%y"), "-", format(vax_admin_end_date, "%m/%d/%y"))`*

## {.tabset}
### All Patient Settings
```{r Create kable of all doses adminsitered to date}
# Summarize data for dashboard visualizations
summary_all_doses <- sched_to_date %>%
  filter(Status2 %in% "Arr") %>%
  group_by(`Setting Grouper`, Site, VaxType) %>%
  summarize(Count = n()) %>%
  rename(Setting = `Setting Grouper`) %>%
  arrange(Setting, VaxType, -Count) %>%
  pivot_wider(names_from = VaxType,
              values_from = Count) %>%
  ungroup() %>%
  arrange(Setting, Site) %>%
  group_split(Setting) %>%
  # split(.$Setting) %>%
    # relocate(Setting, .after = Site) %>%
    map_df(., function(x) {
      adorn_totals(x, where = "row",
                        name = unique(x$Setting),
                        fill = "MSHS Total")})

summary_all_doses <- as.data.frame(summary_all_doses)

summary_all_doses <- summary_all_doses %>%
  mutate(across(.cols = where(is.numeric),
                .fns = ~replace_na(.x, 0)))

summary_all_doses[
  which(str_detect(summary_all_doses$Site, "MSHS Total")), 2:ncol(summary_all_doses)] <- 
  lapply(summary_all_doses[
    which(str_detect(summary_all_doses$Site, "MSHS Total")), 2:ncol(summary_all_doses)], 
         function(x) {cell_spec(x, italic = TRUE, bold = TRUE)})

kable(summary_all_doses,
      format = "html",
      escape = FALSE,
      align = "l",
      digits = 0,
      caption = "MSHS Total COVID-19 Vaccine Doses Administered") %>%
  kable_styling(bootstrap_options = "hover", 
                font_size = 11,
                full_width = FALSE) %>%
  row_spec(row = 0,
           background = "#221f72",
           color = "white") %>%
  column_spec(1, bold = TRUE, italic = TRUE) %>%
  collapse_rows(columns = 1)

```

```{r Custom function for creating setting specific tables}
setting_kable <- function(setting, vax_type) {

  if(!(setting %in% unique(sched_to_date$`Setting Grouper`)) |
     (!(vax_type %in% unique(sched_to_date$VaxType)))) {
    stop(paste0("Check your setting and vaccine type."))
    }

  subset_data <- sched_to_date %>%
  filter(Status2 %in% "Arr",
         `Setting Grouper` %in% setting,
         VaxType %in% vax_type) %>%
  group_by(Site, Dose) %>%
  summarize(Count = n()) %>%
  pivot_wider(names_from = Dose,
              # names_prefix = "Dose ",
              values_from = Count) %>%
  arrange(Site) %>%
  mutate(Total = sum(across(contains("Dose")), na.rm = TRUE),
         across(.cols = where(is.numeric),
                .fns = ~replace_na(.x, 0))) %>%
  adorn_totals(where = "row",
               name = "MSHS Total",
               na.rm = TRUE)

kable(subset_data,
      format = "html",
      escape = FALSE,
      align = "l",
      digits = 0,
      caption = paste("MSHS", setting, vax_type,
                      "Vaccine Doses Administered"))%>%
  kable_styling(bootstrap_options = "hover", 
                font_size = 11,
                full_width = FALSE) %>%
  row_spec(row = 0,
           background = "#221f72",
           color = "white") %>%
  row_spec(row = nrow(subset_data),
           bold = TRUE,
           italic = TRUE)

}

```

### Hospital Based PODS
```{r Create tables for hospital POD vaccine summary}

setting_kable(setting = "Hospital POD",
              vax_type = "Adult")

setting_kable(setting = "Hospital POD",
              vax_type = "Peds")

```

### MSHS Practices
```{r Create tables for MSHS practice vaccine summary}

setting_kable(setting = "MSHS Practice",
              vax_type = "Adult")

setting_kable(setting = "MSHS Practice",
              vax_type = "Peds")

```

<!-- ### School Based Practices -->
<!-- ```{r Create tables for school based practice vaccine summary} -->

<!-- setting_kable(setting = "School Based Practice", -->
<!--               vax_type = "Adult") -->

<!-- setting_kable(setting = "School Based Practice", -->
<!--               vax_type = "Peds") -->

<!-- ``` -->

### 2022-04-11 MSH Admin Dose Summary.Rmd
Create a new file to render weekly dashboard for administered doses to date. Update .Rmd file to allow for updating repo after 1 day or multiple days.

@@
 ```{r Set directory, import reference data, and repository, include = FALSE}
-# Set working directory and select raw data ----------------------------
-rm(list = ls())
-
-# Determine path for working directory
-if ("Presidents" %in% list.files("J://")) {
-  user_directory <- paste0("J:/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-} else {
-  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-}
+# # Set working directory and select raw data ----------------------------
+# rm(list = ls())
+# 
+# # Determine path for working directory
+# if ("Presidents" %in% list.files("J://")) {
+#   user_directory <- paste0("J:/Presidents/HSPI-PM/",
+#                            "Operations Analytics and Optimization/Projects/",
+#                            "System Operations/COVID Vaccine")
+# } else {
+#   user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+#                            "Operations Analytics and Optimization/Projects/",
+#                            "System Operations/COVID Vaccine")
+# }
 
@@
 
-# Determine whether or not to update an existing repo
-update_repo <- FALSE
+# # Determine whether or not to update an existing repo
+# update_repo <- FALSE
 
 # Import reference data for site and pod mappings
-dept_mappings <- read_excel(paste0(user_directory, "/Reference File Apr 2022/",
-                                   "MSHS COVID-19 Vaccine Department Mappings 2022-04-05.xlsx"))
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Weekly Dashboard Doses Administered",
+  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-05.xlsx"))
 
@@
 today <- Sys.Date()
-
-# Create dataframe with dates and weeks
-all_dates <- data.frame("Date" = seq.Date(as.Date("1/1/20",
-                                                  format = "%m/%d/%y"),
-                                          as.Date("12/31/21",
-                                                  format = "%m/%d/%y"),
-                                          by = 1))
-all_dates <- all_dates %>%
-  mutate(Year = year(Date),
-         WeekNum = format(Date, "%U"))
 
@@
                "MSVD",
-               "Network LI")#,
-# "MSHS")
-
-# Site order
-city_sites <- c("MSB",
-                "MSBI",
-                "MSH",
-                "MSM",
-                "MSQ",
-                "MSW",
-                "MSVD")#,
-# "MSHS")
+               "Network LI")
 
@@
 ```{r Import existing repo and append as needed}
-
 # Import schedule repository and determine last date it was updated
@@
   # Determine date range of reports to add to repository
+  if (sched_repo_update_date == today - 1) {
+    new_report_dates <- today - 1
+  } else {
     new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
+  }
+
   new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")
@@
                          ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
-                                "Dose 3/Booster", NA))),
+                                "Dose 3/Boosters", NA))),
     # Determine appointment date, year, month, etc.
@@
                     "Arr", `Appt Status`),
-    # (Only needed when manually pulling data in the morning)
-    # Classify any arrivals from today as scheduled for morning export and
-    # classify any appts from prior days that are still in scheduled status as
-    # no shows
-    # Status2 = ifelse(ApptDate == today & Status == "Arr", "Sch",
-    #                  ifelse(ApptDate < today & Status == "Sch", "No Show",
-    # Status)),
     # Update appointment status: classify any appts from prior days that are
@@
                                   "J&J", "Pfizer")))),
+    Site =
       # Roll up any Moderna administered at MSB for YWCA to MSH
-    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
+      ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
+             # Manually classify school practices as peds or adolescent for schools administering both
              ifelse(`Setting Grouper` %in% "School Based Practice" &
@@
   which(sched_to_date$Status2 %in% "Arr")])
-
-# # Manually update discrepancies in site/mfg/dose
-# sched_to_date <- sched_to_date %>%
-#   mutate(# Roll up any Moderna administered at MSB for YWCA to MSH
-#     Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
-#     # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
-#     Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c(2), 1, Dose))
-# 
-# # Crosswalk pod type (employee vs patient)
-# sched_to_date <- left_join(sched_to_date,
-#                            unique(pod_mappings[, c("Provider", "Pod Type")]),
-#                            by = c("Provider/Resource" = "Provider"))
-# 
-# # Assume any pods without a mapping are patient pods
-# sched_to_date[is.na(sched_to_date$`Pod Type`), "Pod Type"] <- "Patient"
 

### 2022-04-11 Render MSHS Doses Admin To Date.R

@@ -1,0 +1,27 @@
+# This code renders the COVID-19 Vaccine Administration data for the health system
+# This dashboard looks at historical doses administered by setting type (hospital POD vs practices)
+# and is less focused on scheduled appointments in the coming weeks.
+
+# Clear environment
+rm(list = ls())
+
+# Determine directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+update_repo <- FALSE
+
+# Render markdown file with dashboard code and save with today's date
+rmarkdown::render(here::here("MSH Admin Dose Summary.Rmd"), 
+                  output_file = paste0(
+                    user_directory,
+                    "/Weekly Dashboard Doses Administered",
+                    "/MSHS COVID-19 Vaccine Administration Summary ",     
+                    format(Sys.Date(), "%m-%d-%y")))

### 2022-04-13 MSH Admin Dose Summary.Rmd
Update new vaccine summary dashboard and fix typos.

@@
 library(janitor)
+library(DT)
 ```
@@
   "/Weekly Dashboard Doses Administered",
-  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-05.xlsx"))
+  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))
 
@@
       digits = 0,
-      caption = paste("MSHS", setting, vax_type,
+      caption = paste(setting, vax_type,
                       "Vaccine Doses Administered"))%>%
@@
 
-### Hospital Based PODS
+### Hospital POD
 ```{r Create tables for hospital POD vaccine summary}
@@
 
+### Reference
+
+**Data Source**
+
+Analysis based on Epic schedule data.
+
+***
+
+**Department Mappings**
+```{r Reference tab with data sources and mappings}
+dept_mappings_dt <- dept_mappings %>%
+  # relocate(`Setting Grouper`) %>%
+  relocate(Department, .after = `New Site`) %>%
+  relocate(`Vaccine Age Group`, .after = Department) %>%
+  rename(Site = `New Site`,
+         Setting = `Setting Grouper`,
+         `Vaccine Administered` = `Vaccine Age Group`) %>%
+  mutate(Setting = ifelse(Setting %in% "School Based Practice",
+                          "MSHS Practice", Setting),
+         `Vaccine Administered` = ifelse(`Vaccine Administered` %in% "Both",
+                                         "Adult & Peds",
+                                         `Vaccine Administered`)) %>%
+  arrange(Setting, Site, Department)
+
+datatable(dept_mappings_dt,
+          rownames = FALSE,
+          options = list(
+            pageLength = 20,
+            paging = TRUE
+          ))
+
+```
+
 <!-- ### School Based Practices -->

### 2022-04-13 Ad Hoc Vaccine Reporting and Export.R

@@ -64,7 +64,7 @@ site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                    "Automation Ref 2022-03-21.xlsx"),
                             sheet = "Site Mappings")
 pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
-                                  "Automation Ref 2022-03-0.1xlsx"),
+                                  "Automation Ref 2022-03-21.xlsx"),
                            sheet = "Pod Mappings Simple")
 
 # Store today's date

### 2022-04-14 Render MSHS Doses Admin To Date.R
Create script for exporting administered doses as an Excel file.

@@ -16,7 +16,7 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-update_repo <- FALSE
+update_repo <- TRUE
 
 # Render markdown file with dashboard code and save with today's date
 rmarkdown::render(here::here("MSH Admin Dose Summary.Rmd"), 

### 2022-04-14 Vaccine Admin by Week Export.R

@@ -1,0 +1,333 @@
+# Code for exporting vaccines administered by week for Jen Paez
+
+#Install and load necessary packages --------------------
+#install.packages("readraw_dfl")
+#install.packages("writeraw_dfl")
+#install.packages("ggplot2")
+#install.packages("lubridate")
+#install.packages("dplyr")
+#install.packages("reshape2")
+#install.packages("svDialogs")
+#install.packages("stringr")
+#install.packages("formattable")
+#install.packages("ggpubr")
+#install.packages("zipcodeR")
+#install.packages("tidyr")
+#install.packages("janitor")
+#install.packages("knitr")
+#install.packages("rmarkdown")
+#install.packages("kableExtra")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(janitor)
+library(knitr)
+library(rmarkdown)
+library(kableExtra)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Weekly Dashboard Doses Administered",
+  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))
+
+dept_mappings <- dept_mappings %>%
+  select(-`New Site`, -Notes) %>%
+  rename(Site = `Site (Historical)`)
+
+
+# Store today's date
+today <- Sys.Date()
+yesterday <- today - 1
+
+# Site order
+all_sites <- c("MSB",
+               "MSBI",
[…]

### 2022-04-18 MSH Admin Dose Summary.Rmd
Simplify logic for determining adult vs pediatric vaccine.

@@
     # Determine appointment day of week
-    DOW = weekdays(ApptDate),
-    # # Determine if patient's zip code is in NYS
-    # NYZip = substr(`ZIP Code`, 1, 5) %in% ny_zips$zipcode,
-    # Determine if patient is a MSHS employee based on response to question
-    # MSHSEmployee =
-    #   # First see if patient responded "YES" to question about MSHS employee
-    #   str_detect(
-    #     str_replace_na(IsPtEmployee, ""),
-    #     regex("yes", ignore_case = TRUE)) |
-    #   # Next, see if there is a MSHS site listed for patients who were vaccinated
-    #   # prior to the addition of the MSHS employee field
-    #   str_detect(
-    #     str_replace_na(`MOUNT SINAI HEALTH SYSTEM`, " "),
-    #     regex("[a-z]", ignore_case = TRUE))
+    DOW = weekdays(ApptDate)
     )
@@
       `Vaccine Age Group` %in% "Peds" |
+        # MSBI Peds POD
+        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
+                                       "DOSE 2 PEDIATRIC [1324685]") |
+        # Practics that administer adult and pediatric vaccines
         (`Vaccine Age Group` %in% "Both" &
-           # Determine if provider/resource at MSBI is peds
-           (`Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
-                                       "DOSE 2 PEDIATRIC [1324685]") |
-              (`Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
-                 Age_Numeric < 12))),
+              `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
+                 Age_Numeric < 12),
       "Peds", "Adult"),

### 2022-07-11 MSH Admin Dose Summary.Rmd
Create script to process and validate new Epic report based on vaccines administered instead of appointments scheduled.

@@
                                         tz = "", format = "%Y-%m-%d %H:%M %p"),
-               `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)))})
+               `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
+               `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
+                 `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
+      }
+    )
 

### 2022-07-11 Render MSHS Doses Admin To Date.R

@@ -16,10 +16,10 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-update_repo <- TRUE
+update_repo <- FALSE
 
 # Render markdown file with dashboard code and save with today's date
-rmarkdown::render(here::here("MSH Admin Dose Summary.Rmd"), 
+rmarkdown::render(here::here("MSH_Admin_Dose_Summary.Rmd"), 
                   output_file = paste0(
                     user_directory,
                     "/Weekly Dashboard Doses Administered",

### 2022-07-11 Validate New Epic Administered Vaccine Report.R

@@ -1,0 +1,96 @@
+# Clear environment
+rm(list = ls())
+
+# Load libraries
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+library(janitor)
+library(DT)
+
+# Determine directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+update_repo <- FALSE
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# # Determine whether or not to update an existing repo
+# update_repo <- FALSE
+
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Weekly Dashboard Doses Administered",
+  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))
+
+dept_mappings <- dept_mappings %>%
+  select(-`Site (Historical)`, -Notes)
+
+# Store today's date
+today <- Sys.Date()
+
+# Site order
+all_sites <- c("MSB",
+               "MSBI",
+               "MSH",
+               "MSM",
+               "MSQ",
+               "MSW",
+               "MSVD",
+               "Network LI")
+
+# Vaccine types
+vax_types <- c("Adult", "Peds")
+
+# Dept grouper
+dept_group <- c("Hospital POD", "MSHS Practice")
+
+
+epic_df <- read_excel(path = paste0(user_directory,
+                                    "/Epic Vaccines Administered Report",
+                                    "/Sample Report 2022-07-11.xls"))
+
+epic_df <- epic_df %>%
[…]

### 2022-07-12 Validate New Epic Administered Vaccine Report.R
Continue working on Epic administered vaccine report validation by comparing to data from schedule repository.

@@ -94,3 +94,207 @@ epic_df <- left_join(epic_df,
 epic_df_summary <- epic_df %>%
   group_by(Existing_Dept, `New Site`, DEPARTMENT_NAME, ImmunizationDate) %>%
   summarize(Count = n())
+
+existing_sites_summary <- epic_df_summary %>%
+  filter(Existing_Dept) %>%
+  group_by(`New Site`) %>%
+  summarize(Count = sum(Count, na.rm = TRUE))
+
+# Import schedule repo --------------------------
+sched_repo_file <- choose.files(default = paste0(user_directory,
+                                                 "/R_Sched_AM_Repo/*.*"))
+
+sched_repo <- readRDS(sched_repo_file)
+
+sched_to_date <- sched_repo
+
+sched_to_date <- sched_to_date %>%
+  # rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
+  mutate(
+    # Update timezones to EST if imported as UTC
+    `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
+    # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
+    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
+                  ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
+                         ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
+                                "Dose 3/Boosters", NA))),
+    # Determine appointment date, year, month, etc.
+    ApptDate = date(Date),
+    ApptYear = year(Date),
+    ApptMonth = month(Date),
+    ApptDay = day(Date),
+    ApptWeek = week(Date),
+    # Clean up department if it is duplicated in that column
+    Department = ifelse(str_detect(Department, ","),
+                        substr(Department, 1,
+                               str_locate(Department, ",") - 1),
+                        Department),
+    # Group arrived, completed, and checked out appts as arrived
+    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
+                    "Arr", `Appt Status`),
+    # Update appointment status: classify any appts from prior days that are
+    # still in scheduled as No Shows
+    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
+                     # Correct any appts erroneously marked as arrived early
+                     ifelse(ApptDate >= today & Status == "Arr", "Sch",
+                            Status)),
+    # # Determine whether the vaccine is an adult or pediatric dose
[…]

### 2022-07-18 Create 2020 to 2021 Schedule Summary.R
Create a script that summarizes all schedule data by date, department, site, dose, etc. for 2020 and 2021. This will be combined with vaccine administration data for future reporting.

@@ -1,0 +1,205 @@
+# Clear environment
+rm(list = ls())
+
+# Load libraries
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+library(janitor)
+library(DT)
+
+# Determine directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+update_repo <- FALSE
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# # Determine whether or not to update an existing repo
+# update_repo <- FALSE
+
+# Import static file for 
+
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Weekly Dashboard Doses Administered",
+  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))
+
+dept_mappings <- dept_mappings %>%
+  select(-`Site (Historical)`, -Notes)
+
+# Store today's date
+today <- Sys.Date()
+
+# Site order
+all_sites <- c("MSB",
+               "MSBI",
+               "MSH",
+               "MSM",
+               "MSQ",
+               "MSW",
+               "MSVD",
+               "Network LI")
+
+# Vaccine types
+vax_types <- c("Adult (12yo+)", "Peds (5-11yo)")
+
+# Dept grouper
+dept_group <- c("Hospital POD", "MSHS Practice")
+
+# Import schedule repo --------------------------
+sched_repo_file <- paste0(user_directory,
+                          "/R_Sched_AM_Repo",
+                          "/Auto Epic Report Sched 121520 to 062922 on 061422 0930.rds")
+
+sched_repo <- readRDS(sched_repo_file)
+
[…]

### 2022-07-18 Create 2020 to 2021 Schedule Summary.R
Add sections and comments.

@@ -1,3 +1,6 @@
+# Script to summarize arrived COVID-19 vaccine appointments for 2020-2021
+
+# Clear environment and load libraries ---------------
 # Clear environment
 rm(list = ls())
 
@@ -23,6 +26,7 @@ library(purrr)
 library(janitor)
 library(DT)
 
+# Reference data -----------------------
 # Determine directory
 if ("Presidents" %in% list.files("J://")) {
   user_directory <- paste0("J:/Presidents/HSPI-PM/",
@@ -39,11 +43,6 @@ update_repo <- FALSE
 # Set path for file selection
 user_path <- paste0(user_directory, "\\*.*")
 
-# # Determine whether or not to update an existing repo
-# update_repo <- FALSE
-
-# Import static file for 
-
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
@@ -56,22 +55,6 @@ dept_mappings <- dept_mappings %>%
 # Store today's date
 today <- Sys.Date()
 
-# Site order
-all_sites <- c("MSB",
-               "MSBI",
-               "MSH",
-               "MSM",
-               "MSQ",
-               "MSW",
-               "MSVD",
-               "Network LI")
-
-# Vaccine types
-vax_types <- c("Adult (12yo+)", "Peds (5-11yo)")
-
-# Dept grouper
-dept_group <- c("Hospital POD", "MSHS Practice")
-
 # Import schedule repo --------------------------
 sched_repo_file <- paste0(user_directory,
                           "/R_Sched_AM_Repo",
@@ -79,6 +62,7 @@ sched_repo_file <- paste0(user_directory,
 
 sched_repo <- readRDS(sched_repo_file)
 
+# Process and format schedule repository for standard reporting ---------------
 sched_to_date <- sched_repo
 
 sched_to_date <- sched_to_date %>%
@@ -199,6 +183,7 @@ sched_repo_summary <- sched_to_date %>%
   rename(Date = ApptDate,
          Setting_Type = `Setting Grouper`)
 
+# Save standardized, static schedule repository as .RDS for use in future reporting --------------------------
 saveRDS(sched_repo_summary,
         paste0(user_directory,
                "/Hybrid Repo Sched & Admin Data",

### 2022-07-18 Create 2020 to 2021 Schedule Summary.R
Ungroup summary dataframe before saving as .rds. Change .rds name to be dependent on current date.

@@ -38,11 +38,6 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-update_repo <- FALSE
-
-# Set path for file selection
-user_path <- paste0(user_directory, "\\*.*")
-
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
@@ -181,10 +176,13 @@ sched_repo_summary <- sched_to_date %>%
            VaxType, Dose, Mfg) %>%
   summarize(Count = n()) %>%
   rename(Date = ApptDate,
-         Setting_Type = `Setting Grouper`)
+         Setting = `Setting Grouper`) %>%
+  ungroup()
 
 # Save standardized, static schedule repository as .RDS for use in future reporting --------------------------
 saveRDS(sched_repo_summary,
         paste0(user_directory,
                "/Hybrid Repo Sched & Admin Data",
-               "/Sched Repo Summary 2020-2021 2022-07-18.RDS"))
+               "/Sched Repo Summary 2020-2021 ",
+               format(today),
+               ".RDS"))

### 2022-07-18 Create Jan-Jun2022 Vaccine Admin Summary.R
Create a script to summarize vaccines administered from Jan to Jun 2022 in a standard format that can be added to schedule repository.

@@ -1,0 +1,93 @@
+# Script to summarize administered COVID-19 vaccine appointments from 1/1/22-6/30/22
+
+# Clear environment and load libraries ---------------
+# Clear environment
+rm(list = ls())
+
+# Load libraries
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+library(janitor)
+library(DT)
+
+# Reference data -----------------------
+# Determine directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Hybrid Repo Sched & Admin Data",
+  "/Vaccines Administered Dept Mappings 2022-07-18.xlsx"))
+
+# Store today's date
+today <- Sys.Date()
+
+# Import historical data for vaccines administered ----------------------
+hist_vax_admin <- read_excel(paste0(
+  user_directory,
+  "/Epic Vaccines Administered Report",
+  "/Sample Report 2022-07-11.xls"
+))
+
+vax_admin_to_date <- hist_vax_admin
+
+vax_admin_to_date <- left_join(vax_admin_to_date,
+                               dept_mappings,
+                               by = c("DEPARTMENT_NAME" = "Department"))
+
+vax_admin_to_date <- vax_admin_to_date %>%
+  select(-DOSE) %>%
+  mutate(Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
+                      ifelse(str_detect(IMMUNE_NAME, "MODERNA"), "Moderna",
+                             ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
+                                    NA))),
[…]

### 2022-07-18 MSH Vaccines Administered Hybrid Data Model.Rmd
Create new markdown file for rendering vaccines administered dashboard using hybrid data approach.

--- 2022-07-11 MSH Admin Dose Summary.Rmd
@@
 ```{r Set directory, import reference data, and repository, include = FALSE}
-# # Set working directory and select raw data ----------------------------
-# rm(list = ls())
-# 
-# # Determine path for working directory
-# if ("Presidents" %in% list.files("J://")) {
-#   user_directory <- paste0("J:/Presidents/HSPI-PM/",
-#                            "Operations Analytics and Optimization/Projects/",
-#                            "System Operations/COVID Vaccine")
-# } else {
-#   user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
-#                            "Operations Analytics and Optimization/Projects/",
-#                            "System Operations/COVID Vaccine")
-# }
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
 
@@
 # # Determine whether or not to update an existing repo
-# update_repo <- FALSE
+update_repo <- FALSE
 
 # Import reference data for site and pod mappings
-dept_mappings <- read_excel(paste0(
+sched_repo_dept_mappings <- read_excel(paste0(
   user_directory,
@@
 
-dept_mappings <- dept_mappings %>%
+sched_repo_dept_mappings <- sched_repo_dept_mappings %>%
   select(-`Site (Historical)`, -Notes)
+
+vaccine_admin_dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Hybrid Repo Sched & Admin Data",
+  "/Vaccines Administered Dept Mappings 2022-07-18.xlsx"))
 
@@
 # Vaccine types
-vax_types <- c("Adult", "Peds")
+vax_types <- c("Adult (12 yo +)", "Peds (5-11 yo)", "Peds (6 mo - 4 yo)")
 
 # Dept grouper
-dept_group <- c("Hospital POD", "MSHS Practice")
+dept_group <- c("Hospital POD", "MSHS Practice", "MSHS Inpatient & ED")
 ```
@@
 # Import schedule repository and determine last date it was updated
-sched_repo_file <- choose.files(default = paste0(user_directory,
-                                                 "/R_Sched_AM_Repo/*.*"))
+sched_repo_summary <- readRDS(paste0(user_directory,
+                                  "/Hybrid Repo Sched & Admin Data",
+                                  "/Sched Repo Summary 2020-2021 2022-07-18.RDS")
+)
 
-sched_repo <- readRDS(sched_repo_file)
-sched_repo_update_date <- date(file.info(sched_repo_file)$ctime)
+vax_admin_repo_summary <- readRDS(paste0(user_directory,
+                                  "/Hybrid Repo Sched & Admin Data",
+                                  "/Vaccines Admin Summary Jan-Jun2022 2022-07-18.RDS")
+)
+
+hybrid_repo <- rbind(sched_repo_summary,
+                     vax_admin_repo_summary)
+
+# sched_repo_update_date <- date(file.info(sched_repo_file)$ctime)
 
@@
 
-  sched_repo <- sched_repo
+  hybrid_repo <- hybrid_repo
 
@@
 ```{r Format and process schedule data}
-# Format and analyze schedule to date for dashboards ---------------------------
-sched_to_date <- sched_repo
-
-sched_to_date <- sched_to_date %>%
-  # rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
-  mutate(
-    # Update timezones to EST if imported as UTC
-    `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
-    # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
-    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
-                  ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
-                         ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
-                                "Dose 3/Boosters", NA))),
-    # Determine appointment date, year, month, etc.
-    ApptDate = date(Date),
-    ApptYear = year(Date),
-    ApptMonth = month(Date),
-    ApptDay = day(Date),
-    ApptWeek = week(Date),
-    # Clean up department if it is duplicated in that column
-    Department = ifelse(str_detect(Department, ","),
-                        substr(Department, 1,
-                               str_locate(Department, ",") - 1),
-                        Department),
-    # Group arrived, completed, and checked out appts as arrived
-    Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
-                    "Arr", `Appt Status`),
-    # Update appointment status: classify any appts from prior days that are
-    # still in scheduled as No Shows
-    Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
-                     # Correct any appts erroneously marked as arrived early
-                     ifelse(ApptDate >= today & Status == "Arr", "Sch",
-                            Status)),
-    # # Determine whether the vaccine is an adult or pediatric dose
-    # VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
-    #                                    "1468 MADISON HOSP PEDS GEN") |
+# # Format and analyze schedule to date for dashboards ---------------------------
+# sched_to_date <- sched_repo
+# 
+# sched_to_date <- sched_to_date %>%
+#   # rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
+#   mutate(
+#     # Update timezones to EST if imported as UTC
+#     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
+#     # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
+#     Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
+#                   ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
+#                          ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
+#                                 "Dose 3/Boosters", NA))),
+#     # Determine appointment date, year, month, etc.
+#     ApptDate = date(Date),
+#     ApptYear = year(Date),
+#     ApptMonth = month(Date),
+#     ApptDay = day(Date),
+#     ApptWeek = week(Date),
+#     # Clean up department if it is duplicated in that column
+#     Department = ifelse(str_detect(Department, ","),
+#                         substr(Department, 1,
+#                                str_locate(Department, ",") - 1),
+#                         Department),
+#     # Group arrived, completed, and checked out appts as arrived
+#     Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
+#                     "Arr", `Appt Status`),
+#     # Update appointment status: classify any appts from prior days that are
+#     # still in scheduled as No Shows
+#     Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
+#                      # Correct any appts erroneously marked as arrived early
+#                      ifelse(ApptDate >= today & Status == "Arr", "Sch",
+#                             Status)),
+#     # # Determine whether the vaccine is an adult or pediatric dose
+#     # VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
+#     #                                    "1468 MADISON HOSP PEDS GEN") |
+#     #                    `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
+#     #                                               "DOSE 2 PEDIATRIC [1324685]") |
+#     #                    Department %in% peds_school_practice_dept,
+#     #                  "Peds", "Adult"),
+#     # # Determine manufacturer based on immunization field and vaccine type fields
+#     # Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
+#     #   ifelse(Status2 != "Arr", NA,
+#     #          # Any blank immunizations and any peds assumed to be Pfizer
+#     #          ifelse(is.na(Immunizations) |
+#     #                   VaxType %in% c("Peds"), "Pfizer",
+#     #                 # Any immunizations with Moderna in text classified as Moderna
+#     #                 ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
+#     #                        # Any visiting docs or Johnson and Johnson
+#     #                        # immunizations classified as J&J
+#     #                        ifelse(str_detect(Department, "VISITING DOCS") |
+#     #                                 str_detect(Immunizations,
+#     #                                            "Johnson and Johnson"),
+#     #                               "J&J", "Pfizer")))),
+#     # Determine week number of year
+#     WeekNum = format(ApptDate, "%U"),
+#     # Determine appointment day of week
+#     DOW = weekdays(ApptDate)
+#   )
+# 
+# # Crosswalk sites and department grouper
+# sched_to_date <- left_join(sched_to_date, dept_mappings,
+#                            by = c("Department" = "Department"))
+# 
+# sched_to_date <- sched_to_date %>%
+#   rename(Site = `New Site`)
+# 
+# # Determine if there are any missing departments and notify user
+# unmapped_dept <- sched_to_date %>%
+#   filter(is.na(Site)) %>%
+#   select(Department) %>%
+#   distinct()
+# 
+# if(nrow(unmapped_dept) > 0) {
+#   stop(paste0("Check department mappings. Missing departments include ",
+#               paste(as.vector(unmapped_dept$Department), collapse = ", "),
+#               "."))
+# }
+# 
+# # Determine vaccine type (adult vs peds) administered based on department, provider, and age, as appropriate
+# sched_to_date <- sched_to_date %>%
+#   mutate(
+#     # Create a column for age grouper
+#     Age_Grouper = ifelse(str_detect(Age, "\\ y.o."), "years",
+#                          ifelse(str_detect(Age, "\\ m.o."), "months",
+#                                 ifelse(str_detect(Age, "\\ days"), "days",
+#                                        "unknown"))),
+#     # Convert string with age to numeric
+#     Age_Numeric = 
+#       ifelse(Age_Grouper == "years",
+#              as.numeric(str_extract(Age,
+#                                     # pattern = "(?<=Deceased\\ \\().+(?=\\ y.o.)")),
+#                                     paste("(?<=Deceased\\ \\()[0-9]+(?=\\ y.o.)",
+#                                           "[0-9]+(?=\\ y.o.)",
+#                                           sep = "|"))),
+#              ifelse(Age_Grouper == "months",
+#                     as.numeric(str_extract(Age, "[0-9]+(?=\\ m.o.)")) / 12,
+#                     ifelse(Age_Grouper == "days",
+#                            as.numeric(
+#                              str_extract(Age, "[0-9]+(?=\\ days)")) / 365,
+#                            ifelse(Age_Grouper == "unknown", 10000,
+#                                   NA_integer_)))),
+#     # Determine vaccine type based on department, provider/resource, and age if necessary
+#     VaxType = ifelse(
+#       `Vaccine Age Group` %in% "Peds" |
+#         # MSBI Peds POD
 #         `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
 #                                    "DOSE 2 PEDIATRIC [1324685]") |
-    #                    Department %in% peds_school_practice_dept,
+#         # Practics that administer adult and pediatric vaccines
+#         (`Vaccine Age Group` %in% "Both" &
+#            `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
+#            Age_Numeric < 12),
 #       "Peds", "Adult"),
@@
 #                                   "J&J", "Pfizer")))),
-    # Determine week number of year
-    WeekNum = format(ApptDate, "%U"),
-    # Determine appointment day of week
-    DOW = weekdays(ApptDate)
-    )
-
-# Crosswalk sites and department grouper
-sched_to_date <- left_join(sched_to_date, dept_mappings,
-                           by = c("Department" = "Department"))
-
-sched_to_date <- sched_to_date %>%
-  rename(Site = `New Site`)
-
-# Determine if there are any missing departments and notify user
-unmapped_dept <- sched_to_date %>%
-  filter(is.na(Site)) %>%
-  select(Department) %>%
-  distinct()
-
-if(nrow(unmapped_dept) > 0) {
-  stop(paste0("Check department mappings. Missing departments include ",
-             paste(as.vector(unmapped_dept$Department), collapse = ", "),
-             "."))
-}
-
-# Determine vaccine type (adult vs peds) administered based on department, provider, and age, as appropriate
-sched_to_date <- sched_to_date %>%
-  mutate(
-    # Create a column for age grouper
-    Age_Grouper = ifelse(str_detect(Age, "\\ y.o."), "years",
-                        ifelse(str_detect(Age, "\\ m.o."), "months",
-                               ifelse(str_detect(Age, "\\ days"), "days",
-                                      "unknown"))),
-    # Convert string with age to numeric
-    Age_Numeric = 
-      ifelse(Age_Grouper == "years",
-                    as.numeric(str_extract(Age,
-                                 # pattern = "(?<=Deceased\\ \\().+(?=\\ y.o.)")),
-                                 paste("(?<=Deceased\\ \\()[0-9]+(?=\\ y.o.)",
-                                       "[0-9]+(?=\\ y.o.)",
-                                       sep = "|"))),
-                    ifelse(Age_Grouper == "months",
-                           as.numeric(str_extract(Age, "[0-9]+(?=\\ m.o.)")) / 12,
-                           ifelse(Age_Grouper == "days",
-                                  as.numeric(
-                                    str_extract(Age, "[0-9]+(?=\\ days)")) / 365,
-                                  ifelse(Age_Grouper == "unknown", 10000,
-                                         NA_integer_)))),
-    # Determine vaccine type based on department, provider/resource, and age if necessary
-    VaxType = ifelse(
-      `Vaccine Age Group` %in% "Peds" |
-        # MSBI Peds POD
-        `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
-                                       "DOSE 2 PEDIATRIC [1324685]") |
-        # Practics that administer adult and pediatric vaccines
-        (`Vaccine Age Group` %in% "Both" &
-              `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
-                 Age_Numeric < 12),
-      "Peds", "Adult"),
-    # Determine manufacturer based on immunization field and vaccine type fields
-    Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
-      ifelse(Status2 != "Arr", NA,
-             # Any blank immunizations and any peds assumed to be Pfizer
-             ifelse(is.na(Immunizations) |
-                      VaxType %in% c("Peds"), "Pfizer",
-                    # Any immunizations with Moderna in text classified as Moderna
-                    ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
-                           # Any visiting docs or Johnson and Johnson
-                           # immunizations classified as J&J
-                           ifelse(str_detect(Department, "VISITING DOCS") |
-                                    str_detect(Immunizations,
-                                               "Johnson and Johnson"),
-                                  "J&J", "Pfizer")))),
-    Site =
-      # Roll up any Moderna administered at MSB for YWCA to MSH
-      ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
-             # Manually classify school practices as peds or adolescent for schools administering both
-             ifelse(`Setting Grouper` %in% "School Based Practice" &
-                      VaxType %in% "Peds", "Peds School Based Practice",
-                    ifelse(`Setting Grouper` %in% "School Based Practice" &
-                             VaxType %in% "Adult",
-                           "Adolescent School Based Practice",
-                           Site))),
-    # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
-    Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c("Dose 2"), "Dose 1", Dose),
-    `Setting Grouper` = ifelse(`Setting Grouper` %in% "School Based Practice",
-                               "MSHS Practice", `Setting Grouper`))
-
-vax_admin_start_date <- min(sched_to_date$ApptDate[
-  which(sched_to_date$Status2 %in% "Arr")])
-
-vax_admin_end_date <- max(sched_to_date$ApptDate[
-  which(sched_to_date$Status2 %in% "Arr")])
+#     Site =
+#       # Roll up any Moderna administered at MSB for YWCA to MSH
+#       ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
+#              # Manually classify school practices as peds or adolescent for schools administering both
+#              ifelse(`Setting Grouper` %in% "School Based Practice" &
+#                       VaxType %in% "Peds", "Peds School Based Practice",
+#                     ifelse(`Setting Grouper` %in% "School Based Practice" &
+#                              VaxType %in% "Adult",
+#                            "Adolescent School Based Practice",
+#                            Site))),
+#     # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
+#     Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c("Dose 2"), "Dose 1", Dose),
+#     `Setting Grouper` = ifelse(`Setting Grouper` %in% "School Based Practice",
+#                                "MSHS Practice", `Setting Grouper`))
+# 
+# vax_admin_start_date <- min(sched_to_date$ApptDate[
+#   which(sched_to_date$Status2 %in% "Arr")])
+# 
+# vax_admin_end_date <- max(sched_to_date$ApptDate[
+#   which(sched_to_date$Status2 %in% "Arr")])
 
@@
 # Summarize data for dashboard visualizations
-summary_all_doses <- sched_to_date %>%
-  filter(Status2 %in% "Arr") %>%
-  group_by(`Setting Grouper`, Site, VaxType) %>%
-  summarize(Count = n()) %>%
-  rename(Setting = `Setting Grouper`) %>%
+summary_all_doses <- hybrid_repo %>%
+  group_by(Setting, Site, VaxType) %>%
+  summarize(Count = sum(Count, na.rm = TRUE)) %>%
   arrange(Setting, VaxType, -Count) %>%

### 2022-08-12 Create FY2020-2021 Sched Arr Visits Summary.R
Create daily summaries of arrived visits for 2020 and 2021 and vaccines administered for Jan-Jun2022.

@@ -51,15 +51,6 @@ sched_data_mappings <- dept_mappings %>%
 # Store today's date
 today <- Sys.Date()
 
-# Vaccine types
-vax_types <- c("Adult", "Peds")
-
-# Dept grouper
-dept_group <- c("Hospital POD",
-                "MSHS Practice",
-                "School Based Practice",
-                "MSHS Inpatient & ED")
-
 # Import schedule repo --------------------------
 sched_repo_file <- choose.files(default = paste0(user_directory,
                                                  "/R_Sched_AM_Repo/*.*"))
@@ -142,13 +133,13 @@ sched_to_date <- sched_to_date %>%
         (`Vaccine Age Group` %in% "Both" &
            `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
            Age_Numeric < 12),
-      "Peds", "Adult"),
+      "Peds (5-11 yo)", "Adult (12 yo +)"),
     # Determine manufacturer based on immunization field and vaccine type fields
     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
       ifelse(Status2 != "Arr", NA,
              # Any blank immunizations and any peds assumed to be Pfizer
              ifelse(is.na(Immunizations) |
-                      VaxType %in% c("Peds"), "Pfizer",
+                      VaxType %in% c("Peds (5-11 yo)"), "Pfizer",
                     # Any immunizations with Moderna in text classified as Moderna
                     ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                            # Any visiting docs or Johnson and Johnson
@@ -172,10 +163,28 @@ sched_to_date <- sched_to_date %>%
     `Setting Grouper` = ifelse(`Setting Grouper` %in% "School Based Practice",
                                "MSHS Practice", `Setting Grouper`))
 
+sched_arr_visits_daily_summary <- sched_to_date %>%
+  group_by(ApptDate, Department, `Setting Grouper`,
+           Site, `Hospital Roll Up`,
+           VaxType, Dose, Mfg) %>%
+  summarize(Count = n()) %>%
+  ungroup() %>%
+  rename(Date = ApptDate)
+
 # Save 2020 and 2021 data as it's own RDS for future reporting
+# Save patient level data
 saveRDS(sched_to_date,
         file = paste0(user_directory,
                       "/Hybrid Repo Sched & Admin Data",
                       "/Sched Arr Visits 2020-2021 Summary ",
[…]

### 2022-08-12 Create Jan-Jun2022 Vaccine Admin Summary.R

@@ -39,17 +39,15 @@ if ("Presidents" %in% list.files("J://")) {
 }
 
 # Import reference data for site and pod mappings
-dept_mappings_name <- read_excel(paste0(
+dept_mappings <- read_excel(paste0(
   user_directory,
   "/Hybrid Repo Sched & Admin Data",
-  "/Vaccines Administered Dept Mappings 2022-08-02.xlsx"),
-  sheet = "Dept Mappings by Name")
+  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
+  sheet = "Hybrid Dept Mapping")
 
-dept_mappings_epic_id <- read_excel(paste0(
-  user_directory,
-  "/Hybrid Repo Sched & Admin Data",
-  "/Vaccines Administered Dept Mappings 2022-08-02.xlsx"),
-  sheet = "Dept Mappings by Epic ID")
+vax_admin_data_mappings <- dept_mappings %>%
+  select(-Department) %>%
+  unique()
 
 # Store today's date
 today <- Sys.Date()
@@ -61,21 +59,12 @@ hist_vax_admin <- read_excel(paste0(
   "/Version4-Jan-June2022.xls"
 ))
 
-vax_admin_to_date <- hist_vax_admin
-
-# Map on department name
-vax_admin_to_date <- left_join(vax_admin_to_date,
-                               dept_mappings_name,
-                               by = c("DEPARTMENT_NAME" = "Department"))
+vax_admin_to_date <- unique(hist_vax_admin)
 
 # Map on Epic ID
 vax_admin_to_date <- left_join(vax_admin_to_date,
-                               dept_mappings_epic_id %>%
-                                 select(-Vaccine_Type),
-                               by = c("EPICDEPID" = "Epic_ID"))
-
-vax_admin_to_date <- vax_admin_to_date %>%
-  mutate(CompareSite = Site.x == Site.y)
+                               vax_admin_data_mappings,
+                               by = c("EPICDEPID" = "EpicID"))
 
 vax_admin_to_date <- vax_admin_to_date %>%
   select(-DOSE) %>%
@@ -89,7 +78,14 @@ vax_admin_to_date <- vax_admin_to_date %>%
                                             "(\\(6 MONTHS - 4 YEARS\\))"),
                                  "Peds (6 mo - 4 yo)", 
                           "Adult (12 yo +)")),
-         Dose = "Dose 1", # Fix this later
[…]

### 2022-08-12 MSH Vaccines Administered Hybrid Data Model.Rmd
Update weekly dashboard to use hybrid data model. Currently only includes data through June 2022 until we get more data from Epic team.

@@
 
-# # Determine whether or not to update an existing repo
+# Determine whether or not to update an existing repo
 update_repo <- FALSE
@@
 # Import reference data for site and pod mappings
-sched_repo_dept_mappings <- read_excel(paste0(
-  user_directory,
-  "/Weekly Dashboard Doses Administered",
-  "/MSHS COVID-19 Vaccine Department Mappings 2022-04-11.xlsx"))
-
-sched_repo_dept_mappings <- sched_repo_dept_mappings %>%
-  select(-`Site (Historical)`, -Notes)
-
-vaccine_admin_dept_mappings <- read_excel(paste0(
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
   user_directory,
   "/Hybrid Repo Sched & Admin Data",
-  "/Vaccines Administered Dept Mappings 2022-07-18.xlsx"))
+  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
+  sheet = "Hybrid Dept Mapping")
+
+vax_admin_data_mappings <- dept_mappings %>%
+  select(-Department) %>%
+  unique()
 
@@
                "MSVD",
-               "Network LI")
+               "Network")
 
@@
 ```{r Import existing repo and append as needed}
-# Import schedule repository and determine last date it was updated
-sched_repo_summary <- readRDS(paste0(user_directory,
+# Import schedule repository daily summary for 2020 and 2021
+sched_repo_summary <- readRDS(
+  paste0(user_directory,
          "/Hybrid Repo Sched & Admin Data",
-                                  "/Sched Repo Summary 2020-2021 2022-07-18.RDS")
-)
+         "/Sched Arr Visits 2020-2021 Daily Summary 2022-08-12.RDS"))
 
-vax_admin_repo_summary <- readRDS(paste0(user_directory,
+# Import vaccine administration repository daily summary for Jan-Jun 2022
+vax_admin_repo_summary <- readRDS(
+  paste0(user_directory,
          "/Hybrid Repo Sched & Admin Data",
-                                  "/Vaccines Admin Summary Jan-Jun2022 2022-07-18.RDS")
-)
+         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-12.RDS"))
 
@@
 
-# sched_repo_update_date <- date(file.info(sched_repo_file)$ctime)
-
-if (update_repo) {
-
-  # Determine date range of reports to add to repository
-  if (sched_repo_update_date == today - 1) {
-    new_report_dates <- today - 1
-  } else {
-    new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
-  }
-
-  new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")
-
-  # Find list of reports
-  file_list_vacc_sched <- list.files(
-    path = paste0(user_directory,
-                  "/Epic Auto Report Sched All Status"),
-    pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
-                     new_report_dates_pattern,
-                     ".*.csv",
-                     collapse = "|"))
-
-  # Import reports and add a column with report name and report date
-  import_new_reports <- map_df(
-    file_list_vacc_sched,
-    .f = function(x){
-      sched_data <- read.csv(
-        paste0(user_directory,
-               "/Epic Auto Report Sched All Status/",
-               x),
-        stringsAsFactors = FALSE,
-        check.names = FALSE) %>%
-        mutate(Filename = x,
-               ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
-                                    "%Y%m%d"),
-               DOB = as.Date(DOB, format = "%m/%d/%Y"),
-               `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
-               Date = as.Date(Date, "%m/%d/%Y"),
-               `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
-                                        tz = "", format = "%Y-%m-%d %H:%M %p"),
-               `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
-               `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
-                 `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
-    }
-  )
-
-  # Filter schedule data from new reports to only keep appointments in latest reports
-  sched_data_new_reports <- import_new_reports %>%
-    group_by(Date) %>%
-    slice_max(ReportDate) %>%
-    mutate(Filename = NULL,
-           ReportDate = NULL) %>%
-    ungroup()
-
-  new_reports_dates <- sort(unique(sched_data_new_reports$Date))
-
-  # Remove vaccine appoints from any overlapping dates in repository and new reports
-  sched_repo <- sched_repo %>%
-    filter(!(Date >= new_reports_dates[1]))
-
-  # Bind schedule repository and schedule from new reports
-  sched_repo <- rbind(sched_repo, sched_data_new_reports)
-
-  # Save new repository
-  saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
-                             "Auto Epic Report Sched ",
-                             format(min(sched_repo$Date), "%m%d%y"), " to ",
-                             format(max(sched_repo$Date), "%m%d%y"),
-                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
-
-} else {
-
-  hybrid_repo <- hybrid_repo
-
-}
+# # Needs to be updated once we start receiving weekly reports
+# if (update_repo) {
+# 
+#   # Determine date range of reports to add to repository
+#   if (sched_repo_update_date == today - 1) {
+#     new_report_dates <- today - 1
+#   } else {
+#     new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
+#   }
+# 
+#   new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")
+# 
+#   # Find list of reports
+#   file_list_vacc_sched <- list.files(
+#     path = paste0(user_directory,
+#                   "/Epic Auto Report Sched All Status"),
+#     pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
+#                      new_report_dates_pattern,
+#                      ".*.csv",
+#                      collapse = "|"))
+# 
+#   # Import reports and add a column with report name and report date
+#   import_new_reports <- map_df(
+#     file_list_vacc_sched,
+#     .f = function(x){
+#       sched_data <- read.csv(
+#         paste0(user_directory,
+#                "/Epic Auto Report Sched All Status/",
+#                x),
+#         stringsAsFactors = FALSE,
+#         check.names = FALSE) %>%
+#         mutate(Filename = x,
+#                ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
+#                                     "%Y%m%d"),
+#                DOB = as.Date(DOB, format = "%m/%d/%Y"),
+#                `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
+#                Date = as.Date(Date, "%m/%d/%Y"),
+#                `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
+#                                         tz = "", format = "%Y-%m-%d %H:%M %p"),
+#                `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
+#                `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
+#                  `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
+#     }
+#   )
+# 
+#   # Filter schedule data from new reports to only keep appointments in latest reports
+#   sched_data_new_reports <- import_new_reports %>%
+#     group_by(Date) %>%
+#     slice_max(ReportDate) %>%
+#     mutate(Filename = NULL,
+#            ReportDate = NULL) %>%
+#     ungroup()
+# 
+#   new_reports_dates <- sort(unique(sched_data_new_reports$Date))
+# 
+#   # Remove vaccine appoints from any overlapping dates in repository and new reports
+#   sched_repo <- sched_repo %>%
+#     filter(!(Date >= new_reports_dates[1]))
+# 
+#   # Bind schedule repository and schedule from new reports
+#   sched_repo <- rbind(sched_repo, sched_data_new_reports)
+# 
+#   # Save new repository
+#   saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
+#                              "Auto Epic Report Sched ",
+#                              format(min(sched_repo$Date), "%m%d%y"), " to ",
+#                              format(max(sched_repo$Date), "%m%d%y"),
+#                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
+# 
+# } else {
+# 
+# }
 ```
 
-```{r Format and process schedule data}
-# # Format and analyze schedule to date for dashboards ---------------------------
-# sched_to_date <- sched_repo
+```{r Format and process new immunization data}
+# new_immune_data <- unique(data)
 # 
-# sched_to_date <- sched_to_date %>%
-#   # rename(IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
-#   mutate(
-#     # Update timezones to EST if imported as UTC
-#     `Appt Time` = with_tz(`Appt Time`, tzone = "EST"),
-#     # Determine whether appointment is for dose 1, 2, or 3 based on scheduled visit type
-#     Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
-#                   ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
-#                          ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
-#                                 "Dose 3/Boosters", NA))),
-#     # Determine appointment date, year, month, etc.
-#     ApptDate = date(Date),
-#     ApptYear = year(Date),
-#     ApptMonth = month(Date),
-#     ApptDay = day(Date),
-#     ApptWeek = week(Date),
-#     # Clean up department if it is duplicated in that column
-#     Department = ifelse(str_detect(Department, ","),
-#                         substr(Department, 1,
-#                                str_locate(Department, ",") - 1),
-#                         Department),
-#     # Group arrived, completed, and checked out appts as arrived
-#     Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
-#                     "Arr", `Appt Status`),
-#     # Update appointment status: classify any appts from prior days that are
-#     # still in scheduled as No Shows
-#     Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
-#                      # Correct any appts erroneously marked as arrived early
-#                      ifelse(ApptDate >= today & Status == "Arr", "Sch",
-#                             Status)),
-#     # # Determine whether the vaccine is an adult or pediatric dose
-#     # VaxType = ifelse(Department %in% c("1468 MADISON PEDIATRIC VACCINE POD",
-#     #                                    "1468 MADISON HOSP PEDS GEN") |
-#     #                    `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
-#     #                                               "DOSE 2 PEDIATRIC [1324685]") |
-#     #                    Department %in% peds_school_practice_dept,
-#     #                  "Peds", "Adult"),
-#     # # Determine manufacturer based on immunization field and vaccine type fields
-#     # Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
-#     #   ifelse(Status2 != "Arr", NA,
-#     #          # Any blank immunizations and any peds assumed to be Pfizer
-#     #          ifelse(is.na(Immunizations) |
-#     #                   VaxType %in% c("Peds"), "Pfizer",
-#     #                 # Any immunizations with Moderna in text classified as Moderna
-#     #                 ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
-#     #                        # Any visiting docs or Johnson and Johnson
-#     #                        # immunizations classified as J&J
-#     #                        ifelse(str_detect(Department, "VISITING DOCS") |
-#     #                                 str_detect(Immunizations,
-#     #                                            "Johnson and Johnson"),
-#     #                               "J&J", "Pfizer")))),
-#     # Determine week number of year
-#     WeekNum = format(ApptDate, "%U"),
-#     # Determine appointment day of week
-#     DOW = weekdays(ApptDate)
-#   )
+# new_immune_data <- left_join(new_immune_data,
+#                              vax_admin_data_mappings,
+#                              by = c("EPICDEPID" = "EpicID"))
 # 
-# # Crosswalk sites and department grouper
-# sched_to_date <- left_join(sched_to_date, dept_mappings,
-#                            by = c("Department" = "Department"))
+# # Add in logic to check for unmapped departments that need to be added to mapping file
+# # Note: This is different than immunizations without a department listed
 # 
-# sched_to_date <- sched_to_date %>%
-#   rename(Site = `New Site`)
+# new_immune_data <- new_immune_data %>%
+#   select(-DOSE) %>%
+#   mutate(Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
+#                       ifelse(str_detect(IMMUNE_NAME, "MODERNA"), "Moderna",
+#                              ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
+#                                     NA))),
+#          VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
+#                           "Peds (5-11 yo)",
+#                           ifelse(str_detect(IMMUNE_NAME,
+#                                             "(\\(6 MONTHS - 4 YEARS\\))"),
+#                                  "Peds (6 mo - 4 yo)", 
+#                           "Adult (12 yo +)")),
+#          Dose = ifelse(str_detect(replace_na(PRC_NAME, ""), "DOSE 1"),
+#                        "Dose 1",
+#                        ifelse(str_detect(replace_na(PRC_NAME, ""),
+#                                          "DOSE 2"), "Dose 2",
+#                               ifelse(str_detect(replace_na(PRC_NAME, ""),
+#                                                 "(DOSE 3)|(BOOSTER)"),
+#                                      "Dose 3/Booster", "Dose 3/Booster"
+#                               ))),
+#          Date = as.Date(str_extract(IMMUNE_DATE,
+#                                     "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
+#                         format = "%d-%b-%Y")
+#          ) %>%
+#   rename(Department = DEPARTMENT_NAME)
 # 
-# # Determine if there are any missing departments and notify user
-# unmapped_dept <- sched_to_date %>%
-#   filter(is.na(Site)) %>%
-#   select(Department) %>%
-#   distinct()
+# new_immune_data_daily_summary <- new_immune_data %>%
+#   filter(!is.na(Department)) %>%
+#   group_by(Date, Department, `Setting Grouper`, 
+#            Site, `Hospital Roll Up`, 
+#            VaxType, Dose, Mfg) %>%
+#   summarize(Count = n()) %>%
+#   ungroup()
 # 
-# if(nrow(unmapped_dept) > 0) {
-#   stop(paste0("Check department mappings. Missing departments include ",
-#               paste(as.vector(unmapped_dept$Department), collapse = ", "),
-#               "."))
-# }
-# 
-# # Determine vaccine type (adult vs peds) administered based on department, provider, and age, as appropriate
-# sched_to_date <- sched_to_date %>%
-#   mutate(
-#     # Create a column for age grouper
-#     Age_Grouper = ifelse(str_detect(Age, "\\ y.o."), "years",
-#                          ifelse(str_detect(Age, "\\ m.o."), "months",
-#                                 ifelse(str_detect(Age, "\\ days"), "days",
-#                                        "unknown"))),
-#     # Convert string with age to numeric
-#     Age_Numeric = 
-#       ifelse(Age_Grouper == "years",
-#              as.numeric(str_extract(Age,
-#                                     # pattern = "(?<=Deceased\\ \\().+(?=\\ y.o.)")),
-#                                     paste("(?<=Deceased\\ \\()[0-9]+(?=\\ y.o.)",
-#                                           "[0-9]+(?=\\ y.o.)",
-#                                           sep = "|"))),
-#              ifelse(Age_Grouper == "months",
-#                     as.numeric(str_extract(Age, "[0-9]+(?=\\ m.o.)")) / 12,
-#                     ifelse(Age_Grouper == "days",
-#                            as.numeric(
-#                              str_extract(Age, "[0-9]+(?=\\ days)")) / 365,
-#                            ifelse(Age_Grouper == "unknown", 10000,
-#                                   NA_integer_)))),
-#     # Determine vaccine type based on department, provider/resource, and age if necessary
-#     VaxType = ifelse(
-#       `Vaccine Age Group` %in% "Peds" |
-#         # MSBI Peds POD
-#         `Provider/Resource` %in% c("DOSE 1 PEDIATRIC [1324684]",
-#                                    "DOSE 2 PEDIATRIC [1324685]") |
-#         # Practics that administer adult and pediatric vaccines
-#         (`Vaccine Age Group` %in% "Both" &
-#            `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
-#            Age_Numeric < 12),
-#       "Peds", "Adult"),
-#     # Determine manufacturer based on immunization field and vaccine type fields
-#     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
-#       ifelse(Status2 != "Arr", NA,
-#              # Any blank immunizations and any peds assumed to be Pfizer
-#              ifelse(is.na(Immunizations) |
-#                       VaxType %in% c("Peds"), "Pfizer",
-#                     # Any immunizations with Moderna in text classified as Moderna
-#                     ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
-#                            # Any visiting docs or Johnson and Johnson
-#                            # immunizations classified as J&J
-#                            ifelse(str_detect(Department, "VISITING DOCS") |
-#                                     str_detect(Immunizations,
-#                                                "Johnson and Johnson"),
-#                                   "J&J", "Pfizer")))),
-#     Site =
-#       # Roll up any Moderna administered at MSB for YWCA to MSH
-#       ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH",
-#              # Manually classify school practices as peds or adolescent for schools administering both
-#              ifelse(`Setting Grouper` %in% "School Based Practice" &
-#                       VaxType %in% "Peds", "Peds School Based Practice",
-#                     ifelse(`Setting Grouper` %in% "School Based Practice" &
-#                              VaxType %in% "Adult",
-#                            "Adolescent School Based Practice",
-#                            Site))),
-#     # Manually correct any J&J doses erroneously documented as dose 2 and change to dose 1
-#     Dose = ifelse(Mfg %in% c("J&J") & Dose %in% c("Dose 2"), "Dose 1", Dose),
-#     `Setting Grouper` = ifelse(`Setting Grouper` %in% "School Based Practice",
-#                                "MSHS Practice", `Setting Grouper`))
-# 
-# vax_admin_start_date <- min(sched_to_date$ApptDate[
-#   which(sched_to_date$Status2 %in% "Arr")])
-# 
-# vax_admin_end_date <- max(sched_to_date$ApptDate[
-#   which(sched_to_date$Status2 %in% "Arr")])
+# # Add to existing summary
+# hybrid_repo <- rbind(hybrid_repo,
+#                      new_immune_data_daily_summary)
+
+vax_admin_start_date <- min(hybrid_repo$Date)
+vax_admin_end_date <- max(hybrid_repo$Date)
 
@@
 summary_all_doses <- hybrid_repo %>%
-  group_by(Setting, Site, VaxType) %>%
+  mutate(`Setting Grouper` = ifelse(str_detect(Site, "School Practice"),
+                                    "MSHS Practice", `Setting Grouper`)) %>%
+  group_by(`Setting Grouper`, Site, VaxType) %>%
   summarize(Count = sum(Count, na.rm = TRUE)) %>%
-  arrange(Setting, VaxType, -Count) %>%
+  arrange(`Setting Grouper`, VaxType, -Count) %>%
   pivot_wider(names_from = VaxType,
@@
   ungroup() %>%
-  arrange(Setting, Site) %>%
-  group_split(Setting) %>%
+  arrange(`Setting Grouper`, Site) %>%
+  group_split(`Setting Grouper`) %>%
   # split(.$Setting) %>%
@@
     adorn_totals(x, where = "row",
-                 name = unique(x$Setting),
+                 name = unique(x$`Setting Grouper`),
                  fill = "MSHS Total")})
@@
 
-  if(!(setting %in% unique(sched_to_date$`Setting Grouper`)) |
-     (!(vax_type %in% unique(sched_to_date$VaxType)))) {
+  if(!(setting %in% unique(hybrid_repo$`Setting Grouper`)) |
+     (!(vax_type %in% unique(hybrid_repo$VaxType)))) {
     stop(paste0("Check your setting and vaccine type."))
@@
 
-  subset_data <- sched_to_date %>%
-    filter(Status2 %in% "Arr",
-           `Setting Grouper` %in% setting,
-           VaxType %in% vax_type) %>%
+  subset_data <- hybrid_repo %>%
+    mutate(`Setting Grouper` = ifelse(str_detect(Site, "School Practice"),
+                                    "MSHS Practice", `Setting Grouper`)) %>%
+    filter(`Setting Grouper` %in% setting,
+           VaxType %in% vax_type)
+
+  if(nrow(subset_data) > 0) {
+
+    subset_data <- subset_data %>%
       group_by(Site, Dose) %>%
@@
           caption = paste(setting, vax_type,
-                        "Vaccine Doses Administered"))%>%
+                          "Vaccine Doses Administered")) %>%
       kable_styling(bootstrap_options = "hover", 
@@
 
+}
+
 ```
@@
 setting_kable(setting = "Hospital POD",
-              vax_type = "Adult")
+              vax_type = "Adult (12 yo +)")
 
 setting_kable(setting = "Hospital POD",
-              vax_type = "Peds")
+              vax_type = "Peds (5-11 yo)")
+
+setting_kable(setting = "Hospital POD",
+              vax_type = "Peds (6 mo - 4 yo)")
 
@@
 setting_kable(setting = "MSHS Practice",
-              vax_type = "Adult")
+              vax_type = "Adult (12 yo +)")
 
 setting_kable(setting = "MSHS Practice",
-              vax_type = "Peds")
+              vax_type = "Peds (5-11 yo)")
+
+setting_kable(setting = "MSHS Practice",
+              vax_type = "Peds (6 mo - 4 yo)")
+
+```
+
+### MSHS Hospitals Inpatient & ED
+```{r Create tables for Inpatient and ED vaccine summary}
+
+setting_kable(setting = "MSHS Inpatient & ED",
+              vax_type = "Adult (12 yo +)")
+
+setting_kable(setting = "MSHS Inpatient & ED",
+              vax_type = "Peds (5-11 yo)")
+
+setting_kable(setting = "MSHS Inpatient & ED",
+              vax_type = "Peds (6 mo - 4 yo)")
 
@@
 
-**Data Source**
+**Data Sources**
 
-  Analysis based on Epic schedule data.
+*2020 and 2021:*
+Data based on arrived visits from Epic schedule data.
+
+*2022:*
+Based on vaccines administered across health system using completed immunization orders.
+
+*Epic Immunization Data Considerations:*
+
+*   Immunizations with no associated Department/Epic ID excluded from analysis.
+*   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
+*   Vaccine dose based on Procedure Name field in Epic. Immunizations with ambiguous visit types are categorized as Dose 3/Booster.
 
@@
 dept_mappings_dt <- dept_mappings %>%
-  # relocate(`Setting Grouper`) %>%
-  relocate(Department, .after = `New Site`) %>%
-  relocate(`Vaccine Age Group`, .after = Department) %>%
-  rename(Site = `New Site`,
-         Setting = `Setting Grouper`,
+  select(-`Hospital Roll Up`) %>%
+  relocate(`Setting Grouper`) %>%
+  relocate(Site, .after = `Setting Grouper`) %>%
+  relocate(`Vaccine Age Group`, .after = EpicID) %>%
+  rename(Setting = `Setting Grouper`,
+         `Epic ID` = EpicID,
          `Vaccine Administered` = `Vaccine Age Group`) %>%
@@
 ```
-
-<!-- ### School Based Practices -->
-<!-- ```{r Create tables for school based practice vaccine summary} -->
-
-<!-- setting_kable(setting = "School Based Practice", -->
-                       <!--               vax_type = "Adult") -->
-
-<!-- setting_kable(setting = "School Based Practice", -->
-                       <!--               vax_type = "Peds") -->
-
-<!-- ``` -->

### 2022-08-12 Create FY2020-2021 Sched Arr Visits Summary.R

@@ -68,7 +68,7 @@ sched_to_date <- sched_to_date %>%
     Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
                   ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
                          ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"),
-                                "Dose 3/Boosters", NA))),
+                                "Dose 3/Booster", NA))),
     # Determine appointment date, year, month, etc.
     ApptDate = date(Date),
     ApptYear = year(Date),

### 2022-09-14 MSH Vaccines Administered Hybrid Data Model.Rmd
Change tab name from Reference to Data Sources & Reference
Update code for 2022 vaccine administration summary to include additional departments and logic for Moderna <6yo vaccine.

@@
          "/Hybrid Repo Sched & Admin Data",
-         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-12.RDS"))
+         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-19.RDS"))
 
@@
       group_by(Site, Dose) %>%
-      summarize(Count = n()) %>%
+      summarize(Count = sum(Count, na.rm = TRUE)) %>%
       pivot_wider(names_from = Dose,
@@
 
-### Reference
+### Data Sources & Reference
 
@@
 *   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
-*   Vaccine dose based on Procedure Name field in Epic. Immunizations with ambiguous visit types are categorized as Dose 3/Booster.
+*   Vaccine dose based on the following logic:
+    1. PRC_NAME field in Epic for clearly defined visits.
+    2. RESPONSE_LIST field completed during vaccination noting the dose in the series for ambiguously defined visits (ie, well visits, follow ups, etc.)
 

### 2022-09-14 Create Jan-Jun2022 Vaccine Admin Summary.R

@@ -1,126 +1,0 @@
-# Script to summarize administered COVID-19 vaccine appointments from 1/1/22-6/30/22
-
-# Clear environment and load libraries ---------------
-# Clear environment
-rm(list = ls())
-
-# Load libraries
-library(readxl)
-library(writexl)
-library(ggplot2)
-library(lubridate)
-library(dplyr)
-library(reshape2)
-library(svDialogs)
-library(stringr)
-library(formattable)
-library(scales)
-library(ggpubr)
-library(reshape2)
-library(knitr)
-library(kableExtra)
-library(rmarkdown)
-library(zipcodeR)
-library(tidyr)
-library(purrr)
-library(janitor)
-library(DT)
-
-# Reference data -----------------------
-# Determine directory
-if ("Presidents" %in% list.files("J://")) {
-  user_directory <- paste0("J:/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-} else {
-  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-}
-
-# Import reference data for site and pod mappings
-dept_mappings <- read_excel(paste0(
-  user_directory,
-  "/Hybrid Repo Sched & Admin Data",
-  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
-  sheet = "Hybrid Dept Mapping")
-
-vax_admin_data_mappings <- dept_mappings %>%
-  select(-Department) %>%
-  unique()
-
-# Store today's date
-today <- Sys.Date()
-
-# Import historical data for vaccines administered ----------------------
-hist_vax_admin <- read_excel(paste0(
-  user_directory,
-  "/Epic Vaccines Administered Report",
-  "/COVID-8.19.2022.xls"
-))
-
-vax_admin_to_date <- unique(hist_vax_admin)
-
-# Map on Epic ID
-vax_admin_to_date <- left_join(vax_admin_to_date,
-                               vax_admin_data_mappings,
-                               by = c("EPICDEPID" = "EpicID"))
-
-vax_admin_to_date <- vax_admin_to_date %>%
-  select(-DOSE) %>%
-  mutate(Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
[…]

### 2022-09-14 Render MSHS Doses Admin To Date.R

@@ -16,7 +16,7 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-update_repo <- TRUE
+update_repo <- FALSE
 
 # Render markdown file with dashboard code and save with today's date
 rmarkdown::render(here::here("MSH_Admin_Dose_Summary.Rmd"), 

### 2022-09-14 Validate New Epic Administered Vaccine Report.R

@@ -46,7 +46,7 @@ user_path <- paste0(user_directory, "\\*.*")
 dept_mappings <- read_excel(paste0(
   user_directory,
   "/Hybrid Repo Sched & Admin Data",
-  "/Hybrid Reporting Dept Mapping 2022-08-03.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
 sched_data_mappings <- dept_mappings %>%
@@ -72,7 +72,7 @@ dept_group <- c("Hospital POD",
 
 epic_df <- read_excel(path = paste0(user_directory,
                                     "/Epic Vaccines Administered Report",
-                                    "/Version4-Jan-June2022.xls"))
+                                    "/COVID-8.19.2022.xls"))
 
 # epic_df <- epic_df %>%
 #   mutate(Existing_Dept = DEPARTMENT_NAME %in% dept_mappings$Department,
@@ -273,8 +273,8 @@ sched_data_depts <- unique(sched_to_date_validate$Department)
 epic_df_validate <- epic_df_validate %>%
   mutate(Dept_in_Sched = DEPARTMENT_NAME %in% sched_data_depts,
          Month = floor_date(ImmunizationDate, "months"),
-         MRN_VaxDate = paste(MRN, ImmunizationDate)) %>%
-  rename(Site = `New Site`)
+         MRN_VaxDate = paste(MRN, ImmunizationDate)) #%>%
+  # rename(Site = `New Site`)
 
 sched_to_date_validate <- sched_to_date_validate %>%
   mutate(Month = floor_date(Date, "months"),

### 2022-09-14 Create 2022 Vaccine Admin Summary.R
Add script for 2022 summary

@@ -1,0 +1,156 @@
+# Script to summarize administered COVID-19 vaccine appointments from 1/1/22-6/30/22
+
+# Clear environment and load libraries ---------------
+# Clear environment
+rm(list = ls())
+
+# Load libraries
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(purrr)
+library(janitor)
+library(DT)
+
+# Reference data -----------------------
+# Determine directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Hybrid Repo Sched & Admin Data",
+  "/Hybrid Reporting Dept Mapping 2022-09-13.xlsx"),
+  sheet = "Hybrid Dept Mapping")
+
+vax_admin_data_mappings <- dept_mappings %>%
+  select(-Department) %>%
+  unique()
+
+# Store today's date
+today <- Sys.Date()
+
+# Import historical data for vaccines administered ----------------------
+hist_vax_admin <- read_excel(paste0(
+  user_directory,
+  "/Epic Vaccines Administered Report",
+  "/Vaccines Administered 01012022 to 09102022.xls"
+))
+
+vax_admin_to_date <- unique(hist_vax_admin)
+
+# Map on Epic ID
+vax_admin_to_date <- left_join(vax_admin_to_date,
+                               vax_admin_data_mappings,
+                               by = c("EPICDEPID" = "EpicID"))
+
+# Determine if there are any missing departments and notify user
+unmapped_dept <- vax_admin_to_date %>%
+  select(DEPARTMENT_NAME, EPICDEPID, Site) %>%
+  distinct() %>%
[…]

### 2022-09-15 MSHS Vaccines Administered Hybrid Data Model.Rmd
Add scripts used to create and render hybrid data model dashboard to repository.

--- 2022-09-14 MSH Vaccines Administered Hybrid Data Model.Rmd
@@
 
-# Determine whether or not to update an existing repo
-update_repo <- FALSE
-
 # Import reference data for site and pod mappings
@@
   "/Hybrid Repo Sched & Admin Data",
-  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2022-09-13.xlsx"),
   sheet = "Hybrid Dept Mapping")
@@
 # Vaccine types
-vax_types <- c("Adult (12 yo +)", "Peds (5-11 yo)", "Peds (6 mo - 4 yo)")
+vax_types <- c("Adult (12yo+)", "Peds (5-11yo)", "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")
 
@@
          "/Hybrid Repo Sched & Admin Data",
-         "/Sched Arr Visits 2020-2021 Daily Summary 2022-08-12.RDS"))
+         "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))
 
@@
          "/Hybrid Repo Sched & Admin Data",
-         "/Admin Immune Jan-Jun2022 Daily Summary 2022-08-19.RDS"))
+         "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-09-14.RDS"))
 
@@
 
-# # Needs to be updated once we start receiving weekly reports
-# if (update_repo) {
-# 
-#   # Determine date range of reports to add to repository
-#   if (sched_repo_update_date == today - 1) {
-#     new_report_dates <- today - 1
-#   } else {
-#     new_report_dates <- seq.Date(sched_repo_update_date, today - 1, by = 1)
-#   }
-# 
-#   new_report_dates_pattern <- format(new_report_dates, "%Y%m%d")
-# 
-#   # Find list of reports
-#   file_list_vacc_sched <- list.files(
-#     path = paste0(user_directory,
-#                   "/Epic Auto Report Sched All Status"),
-#     pattern = paste0("^(Covid_vaccine_all_status_ZipCode_)",
-#                      new_report_dates_pattern,
-#                      ".*.csv",
-#                      collapse = "|"))
-# 
-#   # Import reports and add a column with report name and report date
-#   import_new_reports <- map_df(
-#     file_list_vacc_sched,
-#     .f = function(x){
-#       sched_data <- read.csv(
-#         paste0(user_directory,
-#                "/Epic Auto Report Sched All Status/",
-#                x),
-#         stringsAsFactors = FALSE,
-#         check.names = FALSE) %>%
-#         mutate(Filename = x,
-#                ReportDate = as.Date(str_extract(x, "[0-9]{8}"),
-#                                     "%Y%m%d"),
-#                DOB = as.Date(DOB, format = "%m/%d/%Y"),
-#                `Made Date` = as.Date(`Made Date`, format = "%m/%d/%y"),
-#                Date = as.Date(Date, "%m/%d/%Y"),
-#                `Appt Time` = as.POSIXct(paste("1899-12-31 ", `Appt Time`),
-#                                         tz = "", format = "%Y-%m-%d %H:%M %p"),
-#                `ZIP Code` = substr(`ZIP Code`, 2, nchar(`ZIP Code`)),
-#                `PATIENTS LIFE NUMBER OR ORACLE NUMBER` = as.character(
-#                  `PATIENTS LIFE NUMBER OR ORACLE NUMBER`))
-#     }
-#   )
-# 
-#   # Filter schedule data from new reports to only keep appointments in latest reports
-#   sched_data_new_reports <- import_new_reports %>%
-#     group_by(Date) %>%
-#     slice_max(ReportDate) %>%
-#     mutate(Filename = NULL,
-#            ReportDate = NULL) %>%
-#     ungroup()
-# 
-#   new_reports_dates <- sort(unique(sched_data_new_reports$Date))
-# 
-#   # Remove vaccine appoints from any overlapping dates in repository and new reports
-#   sched_repo <- sched_repo %>%
-#     filter(!(Date >= new_reports_dates[1]))
-# 
-#   # Bind schedule repository and schedule from new reports
-#   sched_repo <- rbind(sched_repo, sched_data_new_reports)
-# 
-#   # Save new repository
-#   saveRDS(sched_repo, paste0(user_directory, "/R_Sched_AM_Repo/",
-#                              "Auto Epic Report Sched ",
-#                              format(min(sched_repo$Date), "%m%d%y"), " to ",
-#                              format(max(sched_repo$Date), "%m%d%y"),
-#                              " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
-# 
-# } else {
-# 
-# }
-```
+# Needs to be updated once we start receiving weekly reports
+if (update_repo) {
 
-```{r Format and process new immunization data}
-# new_immune_data <- unique(data)
-# 
-# new_immune_data <- left_join(new_immune_data,
-#                              vax_admin_data_mappings,
-#                              by = c("EPICDEPID" = "EpicID"))
-# 
-# # Add in logic to check for unmapped departments that need to be added to mapping file
-# # Note: This is different than immunizations without a department listed
-# 
-# new_immune_data <- new_immune_data %>%
-#   select(-DOSE) %>%
-#   mutate(Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
-#                       ifelse(str_detect(IMMUNE_NAME, "MODERNA"), "Moderna",
-#                              ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
-#                                     NA))),
-#          VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
-#                           "Peds (5-11 yo)",
-#                           ifelse(str_detect(IMMUNE_NAME,
-#                                             "(\\(6 MONTHS - 4 YEARS\\))"),
-#                                  "Peds (6 mo - 4 yo)", 
-#                           "Adult (12 yo +)")),
-#          Dose = ifelse(str_detect(replace_na(PRC_NAME, ""), "DOSE 1"),
-#                        "Dose 1",
-#                        ifelse(str_detect(replace_na(PRC_NAME, ""),
-#                                          "DOSE 2"), "Dose 2",
-#                               ifelse(str_detect(replace_na(PRC_NAME, ""),
-#                                                 "(DOSE 3)|(BOOSTER)"),
-#                                      "Dose 3/Booster", "Dose 3/Booster"
-#                               ))),
-#          Date = as.Date(str_extract(IMMUNE_DATE,
-#                                     "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
-#                         format = "%d-%b-%Y")
-#          ) %>%
-#   rename(Department = DEPARTMENT_NAME)
-# 
-# new_immune_data_daily_summary <- new_immune_data %>%
-#   filter(!is.na(Department)) %>%
-#   group_by(Date, Department, `Setting Grouper`, 
-#            Site, `Hospital Roll Up`, 
-#            VaxType, Dose, Mfg) %>%
-#   summarize(Count = n()) %>%
-#   ungroup()
-# 
-# # Add to existing summary
-# hybrid_repo <- rbind(hybrid_repo,
-#                      new_immune_data_daily_summary)
+  # Select most recent weekly file
+  weekly_vax_admin <- choose.files(
+    default = 
+      paste0(user_directory,
+             "/Epic Vaccines Administered Report/*.*"))
+
+  weekly_vax_admin <- read.csv(weekly_vax_admin)
+
+  weekly_vax_admin <- unique(weekly_vax_admin)
+
+  weekly_vax_admin <- left_join(weekly_vax_admin,
+                                vax_admin_data_mappings,
+                                by = c("EPICDEPID" = "EpicID"))
+
+  unmapped_dept <- weekly_vax_admin %>%
+    select(DEPARTMENT_NAME, EPICDEPID, Site) %>%
+    distinct() %>%
+    filter(!is.na(DEPARTMENT_NAME) & is.na(Site))
+
+  if(nrow(unmapped_dept) > 0) {
+    stop(paste0("Check department mappings. Missing departments include ",
+                paste(as.vector(unmapped_dept$DEPARTMENT_NAME), collapse = ", "),
+                "."))
+  }
+
+  weekly_vax_admin <- weekly_vax_admin %>%
+    select(-DOSE) %>%
+    mutate(VaxType = ifelse(str_detect(IMMUNE_NAME, "(\\(5-11 YEARS)\\)"),
+                            "Peds (Pfizer 5-11yo)",
+                            ifelse(str_detect(IMMUNE_NAME,
+                                              "(\\(6 MONTHS - 4 YEARS\\))") |
+                                     str_detect(IMMUNE_NAME,
+                                                "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
+                                   "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)", 
+                                   "Adult (12yo+)")),
+           Mfg = ifelse(str_detect(IMMUNE_NAME, "PFIZER"), "Pfizer",
+                        ifelse(str_detect(IMMUNE_NAME, "MODERNA") |
+                                 str_detect(
+                                   IMMUNE_NAME,
+                                   "COVID-19, MRNA, LNP-S, PF, PEDIATRIC 25 MCG/0.25 ML DOSE"),
+                               "Moderna",
+                               ifelse(str_detect(IMMUNE_NAME, "JOHNSON"), "J&J",
+                                      NA))),
+           Dose = ifelse(
+             str_detect(replace_na(PRC_NAME, ""), "DOSE 1"), "Dose 1",
+             ifelse(
+               str_detect(replace_na(PRC_NAME, ""), "DOSE 2"), "Dose 2",
+               ifelse(
+                 str_detect(replace_na(PRC_NAME, ""), "(DOSE 3)|(BOOSTER)"),
+                 "Dose 3/Booster",
+                 ifelse(
+                   str_detect(replace_na(RESPONSE_LIST, ""), "First Dose"),
+                   "Dose 1",
+                   ifelse(
+                     str_detect(replace_na(RESPONSE_LIST, ""), "Second Dose"),
+                     "Dose 2",
+                     ifelse(
+                       str_detect(replace_na(RESPONSE_LIST, ""),
+                                  "(Third Dose) | (Booster Dose)"),
+                       "Dose 3/Booster",
+                       ifelse(VaxType %in% "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)",
+                              "Dose 1", "Dose 3/Booster"))))))),
+           Date = as.Date(str_extract(IMMUNE_DATE,
+                                      "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
+                          format = "%d-%b-%Y")
+           ) %>%
+    rename(Department = DEPARTMENT_NAME)
+
+  weekly_admin_summary <- weekly_vax_admin %>%
+    filter(!is.na(Department)) %>%
+    group_by(Date, Department, `Setting Grouper`, 
+             Site, `Hospital Roll Up`, 
+             VaxType, Dose, Mfg) %>%  
+    summarize(Count = n()) %>%
+    ungroup()
+
+  # Bind hybrid repository repository and most recent week's vaccine administration data
+  hybrid_repo <- rbind(hybrid_repo, weekly_admin_summary)
+
+  # Save new repository
+  saveRDS(sched_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
+                             "Hybrid Vaccine Admin Data ",
+                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
+                             format(max(hybrid_repo$Date), "%m%d%y"),
+                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
+
+} else {
+
+}
 
@@
 setting_kable(setting = "Hospital POD",
-              vax_type = "Adult (12 yo +)")
+              vax_type = "Adult (12yo+)")
 
 setting_kable(setting = "Hospital POD",
-              vax_type = "Peds (5-11 yo)")
+              vax_type = "Peds (Pfizer 5-11yo)")
 
 setting_kable(setting = "Hospital POD",
-              vax_type = "Peds (6 mo - 4 yo)")
+              vax_type = "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")
 
@@
 setting_kable(setting = "MSHS Practice",
-              vax_type = "Adult (12 yo +)")
+              vax_type = "Adult (12yo+)")
 
 setting_kable(setting = "MSHS Practice",
-              vax_type = "Peds (5-11 yo)")
+              vax_type = "Peds (Pfizer 5-11yo)")
 
 setting_kable(setting = "MSHS Practice",
-              vax_type = "Peds (6 mo - 4 yo)")
+              vax_type = "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")
 
@@
 setting_kable(setting = "MSHS Inpatient & ED",
-              vax_type = "Adult (12 yo +)")
+              vax_type = "Adult (12yo+)")
 
 setting_kable(setting = "MSHS Inpatient & ED",
-              vax_type = "Peds (5-11 yo)")
+              vax_type = "Peds (Pfizer 5-11yo)")
 
 setting_kable(setting = "MSHS Inpatient & ED",
-              vax_type = "Peds (6 mo - 4 yo)")
+              vax_type = "Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)")
 
@@
 *   Immunizations with no associated Department/Epic ID excluded from analysis.
-*   Vaccine type (Adult (12 yo +), Peds (5 - 11 yo), Peds (6 mo - 4 yo)) based on Immunization Name in Epic.
+*   Vaccine type (Adult (12yo+), Peds (5-11yo), Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo)) based on Immunization Name in Epic.
 *   Vaccine dose based on the following logic:
@@
     2. RESPONSE_LIST field completed during vaccination noting the dose in the series for ambiguously defined visits (ie, well visits, follow ups, etc.)
+    3. If both of these are empty, the dose is assumed to be Dose 1 for Peds (Pfizer 6mo-4yo, Moderna 6mo-6yo) or Dose 3/Booster for Peds (5-11yo) and Adults (12+).
 

### 2022-09-15 Create 2022 Vaccine Admin Summary.R

@@ -134,17 +134,17 @@ vax_admin_repo_summary <- vax_admin_to_date %>%
 start_date <- format(min(vax_admin_repo_summary$Date), "%m%d%Y")
 end_date <- format(max(vax_admin_repo_summary$Date), "%m%d%Y")
 
-saveRDS(vax_admin_repo_summary,
-        paste0(user_directory,
-               "/Hybrid Repo Sched & Admin Data",
-               "/Vaccine Administration Daily Summary ",
-               start_date,
-               " to ",
-               end_date,
-               " as of ",
-               format(today, "%Y-%m-%d"),
-               ".rds"))
-
+# saveRDS(vax_admin_repo_summary,
+#         paste0(user_directory,
+#                "/Hybrid Repo Sched & Admin Data",
+#                "/Vaccine Administration Daily Summary ",
+#                start_date,
+#                " to ",
+#                end_date,
+#                " as of ",
+#                format(today, "%Y-%m-%d"),
+#                ".rds"))
+# 
 
 
 # # Save standardized, static vaccines administered repository as .RDS for use in future reporting ----------

### 2022-09-15 Create FY2020-2021 Sched Arr Visits Summary.R

@@ -133,13 +133,13 @@ sched_to_date <- sched_to_date %>%
         (`Vaccine Age Group` %in% "Both" &
            `Setting Grouper` %in% c("School Based Practice", "MSHS Practice") &
            Age_Numeric < 12),
-      "Peds (5-11 yo)", "Adult (12 yo +)"),
+      "Peds (Pfizer 5-11yo)", "Adult (12yo+)"),
     # Determine manufacturer based on immunization field and vaccine type fields
     Mfg = #Keep manufacturer as NA if the appointment hasn't been arrived
       ifelse(Status2 != "Arr", NA,
              # Any blank immunizations and any peds assumed to be Pfizer
              ifelse(is.na(Immunizations) |
-                      VaxType %in% c("Peds (5-11 yo)"), "Pfizer",
+                      VaxType %in% c("Peds (Pfizer 5-11yo)"), "Pfizer",
                     # Any immunizations with Moderna in text classified as Moderna
                     ifelse(str_detect(Immunizations, "Moderna"), "Moderna",
                            # Any visiting docs or Johnson and Johnson
@@ -173,12 +173,12 @@ sched_arr_visits_daily_summary <- sched_to_date %>%
 
 # Save 2020 and 2021 data as it's own RDS for future reporting
 # Save patient level data
-saveRDS(sched_to_date,
-        file = paste0(user_directory,
-                      "/Hybrid Repo Sched & Admin Data",
-                      "/Sched Arr Visits 2020-2021 Summary ",
-                      format(today, "%Y-%m-%d"),
-                      ".rds"))
+# saveRDS(sched_to_date,
+#         file = paste0(user_directory,
+#                       "/Hybrid Repo Sched & Admin Data",
+#                       "/Sched Arr Visits 2020-2021 Summary ",
+#                       format(today, "%Y-%m-%d"),
+#                       ".rds"))
 
 # Save daily summary of arrived visits
 saveRDS(sched_arr_visits_daily_summary,

### 2022-09-15 Render Hybrid Doses Admin Model.R

@@ -1,0 +1,27 @@
+# This code renders the COVID-19 Vaccine Administration data for the health system
+# This dashboard looks at historical doses administered by setting type (hospital POD vs practices)
+# and is less focused on scheduled appointments in the coming weeks.
+
+# Clear environment
+rm(list = ls())
+
+# Determine directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+update_repo <- FALSE
+
+# Render markdown file with dashboard code and save with today's date
+rmarkdown::render(here::here("MSHS Vaccines Administered Hybrid Data Model.Rmd"), 
+                  output_file = paste0(
+                    user_directory,
+                    "/Hybrid Repo Sched & Admin Data",
+                    "/MSHS COVID-19 Vaccines Administered ",     
+                    format(Sys.Date(), "%m-%d-%y")))

### 2022-09-27 MSHS Vaccines Administered Hybrid Data Model.Rmd
Update analysis reference file. Update code for hybrid dashboard to create new repo each week.

@@
 ```{r Set directory, import reference data, and repository, include = FALSE}
-# Set working directory and select raw data ----------------------------
-rm(list = ls())
-
-# Determine path for working directory
-if ("Presidents" %in% list.files("J://")) {
-  user_directory <- paste0("J:/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-} else {
-  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-}
+# # Determine path for working directory
+# if ("Presidents" %in% list.files("J://")) {
+#   user_directory <- paste0("J:/Presidents/HSPI-PM/",
+#                            "Operations Analytics and Optimization/Projects/",
+#                            "System Operations/COVID Vaccine")
+# } else {
+#   user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+#                            "Operations Analytics and Optimization/Projects/",
+#                            "System Operations/COVID Vaccine")
+# }
 
@@
   "/Hybrid Repo Sched & Admin Data",
-  "/Hybrid Reporting Dept Mapping 2022-09-13.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
@@
 ```{r Import existing repo and append as needed}
+if (initial_run) {
+
   # Import schedule repository daily summary for 2020 and 2021
@@
 
+  # Save new repository
+  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
+                             "Hybrid Vaccine Admin Data ",
+                             format(min(hybrid_repo$Date), "%m%d%y"), " to ",
+                             format(max(hybrid_repo$Date), "%m%d%y"),
+                             " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
+} else {
+
+  # Select repository
+  repo_file <- choose.files(
+    default = 
+      paste0(user_directory,
+             "/Epic Vaccines Administered Report",
+             "/*.*"),
+    caption = "Select hybrid vaccine administration repository.")
+
+  hybrid_repo <- readRDS(repo_file)
+
+}
+
 # Needs to be updated once we start receiving weekly reports
@@
       paste0(user_directory,
-             "/Epic Vaccines Administered Report/*.*"))
+             "/Epic Vaccines Administered Report",
+             "/Weekly Automated Reports/*.*"),
+    caption = "Select weekly vaccine administration data.")
 
-  weekly_vax_admin <- read.csv(weekly_vax_admin)
+  weekly_vax_admin <- read_excel(weekly_vax_admin)
 
@@
                               "Dose 1", "Dose 3/Booster"))))))),
-           Date = as.Date(str_extract(IMMUNE_DATE,
-                                      "[0-9]{2}\\-[A-Za-z]{3}\\-[0-9]{4}"),
-                          format = "%d-%b-%Y")
-           ) %>%
+           Date = as.Date(IMMUNE_DATE)) %>%
     rename(Department = DEPARTMENT_NAME)
@@
   # Save new repository
-  saveRDS(sched_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
+  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
                              "Hybrid Vaccine Admin Data ",

### 2022-09-27 Render Hybrid Doses Admin Model.R

@@ -16,7 +16,8 @@ if ("Presidents" %in% list.files("J://")) {
                            "System Operations/COVID Vaccine")
 }
 
-update_repo <- FALSE
+initial_run <- FALSE
+update_repo <- TRUE
 
 # Render markdown file with dashboard code and save with today's date
 rmarkdown::render(here::here("MSHS Vaccines Administered Hybrid Data Model.Rmd"), 

### 2022-09-28 Vaccine Admin by Week Export.R
Start updating Vaccine Admin by Week Export for Justin using hybrid repo data structure.

@@ -61,13 +61,13 @@ user_path <- paste0(user_directory, "\\*.*")
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
-  "/Weekly Dashboard Doses Administered",
-  "/MSHS COVID-19 Vaccine Department Mappings 2022-08-25.xlsx"))
+  "/Hybrid Repo Sched & Admin Data",
+  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
+  sheet = "Hybrid Dept Mapping")
 
-dept_mappings <- dept_mappings %>%
-  select(-`New Site`, -Notes) %>%
-  rename(Site = `Site (Historical)`)
-
+vax_admin_data_mappings <- dept_mappings %>%
+  select(-Department) %>%
+  unique()
 
 # Store today's date
 today <- Sys.Date()
@@ -153,22 +153,26 @@ all_dates <- all_dates %>%
   arrange(VaxType, Date)
 
 
-# Import Epic schedule repository
-sched_repo <- readRDS(
-  choose.files(default = paste0(user_directory,
-                                  "/R_Sched_AM_Repo/*.*"),
-                 caption = "Select this morning's schedule repository"))
+# Import hybrid schedule and administration data repository
+repo_file <- choose.files(
+  default = 
+    paste0(user_directory,
+           "/Epic Vaccines Administered Report",
+           "/*.*"),
+  caption = "Select hybrid vaccine administration repository.")
+
+hybrid_repo <- readRDS(repo_file)
 
 # Format and analyze Epic schedule to date for dashboards ---------------------
-sched_to_date <- sched_repo
+admin_to_date <- hybrid_repo
 
-sched_to_date <- sched_to_date %>%
+admin_to_date <- admin_to_date %>%
   mutate(
-    # Determine whether appointment is for dose 1 or dose 2
-    Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
-                  ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
-                         ifelse(str_detect(Type, "(DOSE 3)|(BOOSTER)"), 
-                                "Dose 3/Booster", NA))),
+    # # Determine whether appointment is for dose 1 or dose 2
+    # Dose = ifelse(str_detect(Type, "DOSE 1"), "Dose 1",
+    #               ifelse(str_detect(Type, "DOSE 2"), "Dose 2",
[…]

### 2022-10-04 MSHS Vaccines Administered Hybrid Data Model.Rmd
Update code to reflect updated shared drive folder structure.

@@
   user_directory,
-  "/Hybrid Repo Sched & Admin Data",
+  "/Hybrid Sched & Admin Reporting",
   "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
@@
     paste0(user_directory,
-           "/Hybrid Repo Sched & Admin Data",
+           "/Hybrid Sched & Admin Reporting",
+           "/Hybrid Model Repo",
            "/Sched Arr Visits 2020-2021 Daily Summary 2022-09-14.RDS"))
@@
     paste0(user_directory,
-           "/Hybrid Repo Sched & Admin Data",
-           "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-09-14.RDS"))
+           "/Hybrid Sched & Admin Reporting",
+           "/Hybrid Model Repo",
+           "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-10-04.RDS"))
 
@@
   # Save new repository
-  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
-                             "Hybrid Vaccine Admin Data ",
+  saveRDS(hybrid_repo, paste0(user_directory, 
+                              "/Hybrid Sched & Admin Reporting",
+                              "/Hybrid Model Repo",
+                              "/Hybrid Vaccine Admin Data ",
                               format(min(hybrid_repo$Date), "%m%d%y"), " to ",
@@
       paste0(user_directory,
-             "/Epic Vaccines Administered Report",
+             "/Hybrid Sched & Admin Reporting",
+             "/Hybrid Model Repo",
              "/*.*"),
@@
       paste0(user_directory,
-             "/Epic Vaccines Administered Report",
-             "/Weekly Automated Reports/*.*"),
+             "/Hybrid Sched & Admin Reporting",
+             "/Vaccine Admin Reports/*.*"),
     caption = "Select weekly vaccine administration data.")
@@
   # Save new repository
-  saveRDS(hybrid_repo, paste0(user_directory, "/Epic Vaccines Administered Report/",
-                             "Hybrid Vaccine Admin Data ",
+  saveRDS(hybrid_repo, paste0(user_directory,
+                              "/Hybrid Sched & Admin Reporting",
+                              "/Hybrid Model Repo",
+                              "/Hybrid Vaccine Admin Data ",
                               format(min(hybrid_repo$Date), "%m%d%y"), " to ",

### 2022-10-04 Combine All Epic Dept Names and ID.R

@@ -49,7 +49,7 @@ sched_repo_dept_names_id <- sched_repo %>%
 # Import vaccine administration data
 hist_vax_admin <- read_excel(paste0(
   user_directory,
-  "/Epic Vaccines Administered Report",
+  "/Epic Vaccines Administered Report Validation",
   "/Version4-Jan-June2022.xls"
 ))
 
@@ -70,5 +70,5 @@ hybrid_data_dept_list <- hybrid_data_dept_list %>%
 
 write_xlsx(hybrid_data_dept_list,
            path = paste0(user_directory,
-                         "/Hybrid Repo Sched & Admin Data",
+                         "/Hybrid Sched & Admin Reporting",
                          "/Epic Department Names and IDs 2022-08-03.xlsx"))

### 2022-10-04 Create 2020 to 2021 Schedule Summary.R

@@ -182,7 +182,7 @@ sched_repo_summary <- sched_to_date %>%
 # Save standardized, static schedule repository as .RDS for use in future reporting --------------------------
 saveRDS(sched_repo_summary,
         paste0(user_directory,
-               "/Hybrid Repo Sched & Admin Data",
+               "/Hybrid Sched & Admin Reporting",
                "/Sched Repo Summary 2020-2021 ",
                format(today),
                ".RDS"))

### 2022-10-04 Create 2022 Vaccine Admin Summary.R

@@ -41,8 +41,8 @@ if ("Presidents" %in% list.files("J://")) {
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
-  "/Hybrid Repo Sched & Admin Data",
-  "/Hybrid Reporting Dept Mapping 2022-09-13.xlsx"),
+  "/Hybrid Sched & Admin Reporting",
+  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
 vax_admin_data_mappings <- dept_mappings %>%
@@ -55,7 +55,8 @@ today <- Sys.Date()
 # Import historical data for vaccines administered ----------------------
 hist_vax_admin <- read_excel(paste0(
   user_directory,
-  "/Epic Vaccines Administered Report",
+  "/Hybrid Sched & Admin Reporting",
+  "/Vaccine Admin Reports",
   "/Vaccines Administered 01012022 to 09102022.xls"
 ))
 
@@ -134,23 +135,24 @@ vax_admin_repo_summary <- vax_admin_to_date %>%
 start_date <- format(min(vax_admin_repo_summary$Date), "%m%d%Y")
 end_date <- format(max(vax_admin_repo_summary$Date), "%m%d%Y")
 
-# saveRDS(vax_admin_repo_summary,
-#         paste0(user_directory,
-#                "/Hybrid Repo Sched & Admin Data",
-#                "/Vaccine Administration Daily Summary ",
-#                start_date,
-#                " to ",
-#                end_date,
-#                " as of ",
-#                format(today, "%Y-%m-%d"),
-#                ".rds"))
-# 
+saveRDS(vax_admin_repo_summary,
+        paste0(user_directory,
+               "/Hybrid Sched & Admin Reporting",
+               "/Hybrid Model Repo",
+               "/Vaccine Administration Daily Summary ",
+               start_date,
+               " to ",
+               end_date,
+               " as of ",
+               format(today, "%Y-%m-%d"),
+               ".rds"))
+
 
 
 # # Save standardized, static vaccines administered repository as .RDS for use in future reporting ----------
 # saveRDS(vax_admin_repo_summary,
 #         paste0(user_directory,
-#                "/Hybrid Repo Sched & Admin Data",
+#                "/Hybrid Sched & Admin Reporting",
 #                "/Vaccines Admin Summary Jan-Jun2022 ",
 #                format(today),
 #                ".RDS"))

### 2022-10-04 Create FY2020-2021 Sched Arr Visits Summary.R

@@ -40,8 +40,8 @@ if ("Presidents" %in% list.files("J://")) {
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
-  "/Hybrid Repo Sched & Admin Data",
-  "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
+  "/Hybrid Sched & Admin Reporting",
+  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
 sched_data_mappings <- dept_mappings %>%
@@ -175,7 +175,7 @@ sched_arr_visits_daily_summary <- sched_to_date %>%
 # Save patient level data
 # saveRDS(sched_to_date,
 #         file = paste0(user_directory,
-#                       "/Hybrid Repo Sched & Admin Data",
+#                       "/Hybrid Sched & Admin Reporting",
 #                       "/Sched Arr Visits 2020-2021 Summary ",
 #                       format(today, "%Y-%m-%d"),
 #                       ".rds"))
@@ -183,7 +183,7 @@ sched_arr_visits_daily_summary <- sched_to_date %>%
 # Save daily summary of arrived visits
 saveRDS(sched_arr_visits_daily_summary,
         file = paste0(user_directory,
-                      "/Hybrid Repo Sched & Admin Data",
+                      "/Hybrid Sched & Admin Reporting",
                       "/Sched Arr Visits 2020-2021 Daily Summary ",
                       format(today, "%Y-%m-%d"),
                       ".rds"))

### 2022-10-04 Render Hybrid Doses Admin Model.R

@@ -23,6 +23,7 @@ update_repo <- TRUE
 rmarkdown::render(here::here("MSHS Vaccines Administered Hybrid Data Model.Rmd"), 
                   output_file = paste0(
                     user_directory,
-                    "/Hybrid Repo Sched & Admin Data",
+                    "/Hybrid Sched & Admin Reporting",
+                    "/Hybrid Model Dashboard",
                     "/MSHS COVID-19 Vaccines Administered ",     
                     format(Sys.Date(), "%m-%d-%y")))

### 2022-10-04 Vaccine Admin by Week Export.R

@@ -61,7 +61,7 @@ user_path <- paste0(user_directory, "\\*.*")
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
-  "/Hybrid Repo Sched & Admin Data",
+  "/Hybrid Sched & Admin Reporting",
   "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
@@ -157,7 +157,8 @@ all_dates <- all_dates %>%
 repo_file <- choose.files(
   default = 
     paste0(user_directory,
-           "/Epic Vaccines Administered Report",
+           "/Hybrid Sched & Admin Reporting",
+           "/Hybrid Model Repo",
            "/*.*"),
   caption = "Select hybrid vaccine administration repository.")
 

### 2022-10-04 Validate New Epic Administered Vaccine Report.R

@@ -45,7 +45,7 @@ user_path <- paste0(user_directory, "\\*.*")
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
-  "/Hybrid Repo Sched & Admin Data",
+  "/Hybrid Sched & Admin Reporting",
   "/Hybrid Reporting Dept Mapping 2022-08-08.xlsx"),
   sheet = "Hybrid Dept Mapping")
 

### 2022-10-12 Yearly Vaccine Summary.R
Create script for summarizing vaccines administered by year.

@@ -1,0 +1,145 @@
+# Code to summarize doses by year
+
+#Install and load necessary packages --------------------
+#install.packages("readraw_dfl")
+#install.packages("writeraw_dfl")
+#install.packages("ggplot2")
+#install.packages("lubridate")
+#install.packages("dplyr")
+#install.packages("reshape2")
+#install.packages("svDialogs")
+#install.packages("stringr")
+#install.packages("formattable")
+#install.packages("ggpubr")
+#install.packages("zipcodeR")
+#install.packages("tidyr")
+#install.packages("janitor")
+#install.packages("knitr")
+#install.packages("rmarkdown")
+#install.packages("kableExtra")
+
+#Analysis for weekend discharge tracking
+library(readxl)
+library(writexl)
+library(ggplot2)
+library(lubridate)
+library(dplyr)
+library(reshape2)
+library(svDialogs)
+library(stringr)
+library(formattable)
+library(scales)
+library(ggpubr)
+library(reshape2)
+library(knitr)
+library(kableExtra)
+library(rmarkdown)
+library(zipcodeR)
+library(tidyr)
+library(janitor)
+library(knitr)
+library(rmarkdown)
+library(kableExtra)
+
+# Set working directory and select raw data ----------------------------
+rm(list = ls())
+
+# Determine path for working directory
+if ("Presidents" %in% list.files("J://")) {
+  user_directory <- paste0("J:/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+} else {
+  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
+                           "Operations Analytics and Optimization/Projects/",
+                           "System Operations/COVID Vaccine")
+}
+
+# Set path for file selection
+user_path <- paste0(user_directory, "\\*.*")
+
+# Import reference data for site and pod mappings
+dept_mappings <- read_excel(paste0(
+  user_directory,
+  "/Hybrid Sched & Admin Reporting",
+  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
+  sheet = "Hybrid Dept Mapping")
+
+vax_admin_data_mappings <- dept_mappings %>%
+  select(-Department) %>%
+  unique()
+
+# Store today's date
+today <- Sys.Date()
+yesterday <- today - 1
+
+# Site order
+all_sites <- c("MSB",
[…]

### 2022-10-27 MSHS Vaccines Administered Hybrid Data Model.Rmd
Add code to remove any repeated rows before binding hybrid repo.
Update analysis reference file.

@@
   "/Hybrid Sched & Admin Reporting",
-  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2022-10-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
@@
                  ifelse(
-                   str_detect(replace_na(RESPONSE_LIST, ""), "First Dose"),
+                   str_detect(replace_na(RESPONSE_LIST, ""), "First"),
                    "Dose 1",
                    ifelse(
-                     str_detect(replace_na(RESPONSE_LIST, ""), "Second Dose"),
+                     str_detect(replace_na(RESPONSE_LIST, ""), "Second"),
                      "Dose 2",
@@
                        str_detect(replace_na(RESPONSE_LIST, ""),
-                                  "(Third Dose) | (Booster Dose)"),
+                                  "(Third) | (Booster)"),
                        "Dose 3/Booster",
@@
     ungroup()
+
+  # Remove any duplicate dates, departments, etc.
+  hybrid_repo <- anti_join(hybrid_repo,
+                           weekly_admin_summary,
+                           by = c("Date",
+                                  "Department"))
 

### 2022-10-27 Vaccine Admin by Week Export.R

@@ -62,7 +62,7 @@ user_path <- paste0(user_directory, "\\*.*")
 dept_mappings <- read_excel(paste0(
   user_directory,
   "/Hybrid Sched & Admin Reporting",
-  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2022-10-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
 vax_admin_data_mappings <- dept_mappings %>%

### 2022-10-27 Yearly Vaccine Summary.R

@@ -62,7 +62,7 @@ user_path <- paste0(user_directory, "\\*.*")
 dept_mappings <- read_excel(paste0(
   user_directory,
   "/Hybrid Sched & Admin Reporting",
-  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2022-10-27.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
 vax_admin_data_mappings <- dept_mappings %>%
@@ -136,10 +136,10 @@ yearly_summary <- admin_to_date %>%
 
 export_list <- list("Annual Summary" = yearly_summary)
 
-write_xlsx(export_list,
-           path = paste0(user_directory,
-                         "/AdHoc",
-                         "/Vaccines Administered by Year as of ",
-                         format(Sys.Date(), "%Y-%m-%d"),
-                         ".xlsx"))
+# write_xlsx(export_list,
+#            path = paste0(user_directory,
+#                          "/AdHoc",
+#                          "/Vaccines Administered by Year as of ",
+#                          format(Sys.Date(), "%Y-%m-%d"),
+#                          ".xlsx"))
 

### 2023-07-24 MSHS Vaccines Administered Hybrid Data Model.Rmd
Clean up if-else statement when repo is not updated.
Update repository and associated codes to use latest data pull from Epic for all vaccines administered from 01-2022 to 06-2023 with all relevant immunization names.

@@
   user_directory,
+  "HSPI-PM/Operations Analytics and Optimization/",
+  "Projects/System Operations/COVID Vaccine",
   "/Hybrid Sched & Admin Reporting",
-  "/Hybrid Reporting Dept Mapping 2022-10-27.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2023-07-24.xlsx"),
   sheet = "Hybrid Dept Mapping")
@@
     paste0(user_directory,
+           "HSPI-PM/Operations Analytics and Optimization",
+           "/Projects/System Operations/COVID Vaccine",
            "/Hybrid Sched & Admin Reporting",
@@
     paste0(user_directory,
+           "HSPI-PM/Operations Analytics and Optimization",
+           "/Projects/System Operations/COVID Vaccine",
            "/Hybrid Sched & Admin Reporting",
            "/Hybrid Model Repo",
-           "/Vaccine Administration Daily Summary 01012022 to 09102022 as of 2022-10-04.RDS"))
+           "/Vaccine Administration Daily Summary 01012022 to 06302023 as of 2023-07-24.RDS"))
 
@@
   saveRDS(hybrid_repo, paste0(user_directory, 
+                              "HSPI-PM/Operations Analytics and Optimization",
+                              "/Projects/System Operations/COVID Vaccine",
                               "/Hybrid Sched & Admin Reporting",
@@
                               " on ", format(Sys.time(), "%m%d%y %H%M"), ".rds"))
-
-} else {
 

### 2023-07-24 Create 2022 Vaccine Admin Summary.R

@@ -28,21 +28,39 @@ library(DT)
 
 # Reference data -----------------------
 # Determine directory
-if ("Presidents" %in% list.files("J://")) {
-  user_directory <- paste0("J:/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-} else {
-  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
+define_root_path <- function(){
+  #Check if directory is from R Workbench; starts with '/home'
+  if(grepl("^/home", dirname(getwd()))){
+    #Check if mapped Sharedrvie starts at folder Presidents or deans
+    ifelse(list.files("/SharedDrive/") == "Presidents",
+           #Define prefix of path to share drive with R Workbench format
+           output <- "/SharedDrive/Presidents/", 
+           output <- "/SharedDrive/deans/Presidents/")
+  }#Check if directory is from R Studio; starts with an uppercase letter than ':'
+  else if(grepl("^[[:upper:]]+:", dirname(getwd()))){
+    #Determine which drive is mapped to Sharedrive (x)
+    for(i in LETTERS){
+      if(any(grepl("deans|Presidents", list.files(paste0(i, "://"))))){x <- i}
+    }
+    #Check if mapped Sharedrvie starts at folder Presidents or deans
+    ifelse(list.files(paste0(x, "://")) == "Presidents",
+           #Define prefix of path to share drive with R Studio format
+           output <- paste0(x, ":/Presidents/"),
+           output <- paste0(x, ":/deans/Presidents/"))
+    
+  }
+  return(output)
 }
+
+user_directory <- define_root_path()
 
 # Import reference data for site and pod mappings
 dept_mappings <- read_excel(paste0(
   user_directory,
+  "HSPI-PM/Operations Analytics and Optimization/",
+  "Projects/System Operations/COVID Vaccine",
   "/Hybrid Sched & Admin Reporting",
-  "/Hybrid Reporting Dept Mapping 2022-09-27.xlsx"),
+  "/Hybrid Reporting Dept Mapping 2023-07-24.xlsx"),
   sheet = "Hybrid Dept Mapping")
 
[…]

### 2023-07-24 Render Hybrid Doses Admin Model.R

@@ -6,18 +6,36 @@
 rm(list = ls())
 
 # Determine directory
-if ("Presidents" %in% list.files("J://")) {
-  user_directory <- paste0("J:/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
-} else {
-  user_directory <- paste0("J:/deans/Presidents/HSPI-PM/",
-                           "Operations Analytics and Optimization/Projects/",
-                           "System Operations/COVID Vaccine")
+#Function to determine path to share drive on R Workbench or R Studio
+
+define_root_path <- function(){
+  #Check if directory is from R Workbench; starts with '/home'
+  if(grepl("^/home", dirname(getwd()))){
+    #Check if mapped Sharedrvie starts at folder Presidents or deans
+    ifelse(list.files("/SharedDrive/") == "Presidents",
+           #Define prefix of path to share drive with R Workbench format
+           output <- "/SharedDrive/Presidents/", 
+           output <- "/SharedDrive/deans/Presidents/")
+  }#Check if directory is from R Studio; starts with an uppercase letter than ':'
+  else if(grepl("^[[:upper:]]+:", dirname(getwd()))){
+    #Determine which drive is mapped to Sharedrive (x)
+    for(i in LETTERS){
+      if(any(grepl("deans|Presidents", list.files(paste0(i, "://"))))){x <- i}
+    }
+    #Check if mapped Sharedrvie starts at folder Presidents or deans
+    ifelse(list.files(paste0(x, "://")) == "Presidents",
+           #Define prefix of path to share drive with R Studio format
+           output <- paste0(x, ":/Presidents/"),
+           output <- paste0(x, ":/deans/Presidents/"))
+    
+  }
+  return(output)
 }
 
-initial_run <- FALSE
-update_repo <- TRUE
+user_directory <- define_root_path()
+
+initial_run <- TRUE
+update_repo <- FALSE
 
 # Render markdown file with dashboard code and save with today's date
 rmarkdown::render(here::here("MSHS Vaccines Administered Hybrid Data Model.Rmd"), 
